### 2015-02-22 draft.tex
First drafts of paper.

\documentclass[letterpaper, 10pt, conference]{ieeeconf/ieeeconf} % Change font size to 9pt

\IEEEoverridecommandlockouts
\overrideIEEEmargins

\usepackage{graphics}
\usepackage{epsfig}
% \usepackage{mathptmx}
% \usepackage{times}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cite}
\usepackage{lpic}

\newtheorem{thm}{Lemma}[section]
\newtheorem{rem}[thm]{Remark}
\newtheorem{defn}[thm]{Definition}
\newtheorem{assn}{Assumption}
\newtheorem{algo}[thm]{Algorithm}

\providecommand{\norm}[1]{\left\|#1\right\|}
\providecommand{\abs}[1]{\left|#1\right|}
\providecommand{\conv}{\text{conv}}

\usepackage{xcolor}
\def\edit{\textcolor{blue}}
\allowdisplaybreaks[4]

\DeclareFontFamily{U}{mathx}{\hyphenchar\font45}
\DeclareFontShape{U}{mathx}{m}{n}{
      <5> <6> <7> <8> <9> <10> gen * mathx
      <10.95> mathx10 <12> <14.4> <17.28> <20.74> <24.88> mathx12
      }{}
\DeclareSymbolFont{mathx}{U}{mathx}{m}{n}
\DeclareFontSubstitution{U}{mathx}{m}{n}
\DeclareMathSymbol{\temp}{\mathbin}{mathx}{'341}
\newcommand{\bigominus}{\raisebox{10pt}{$\temp$}}

\graphicspath{{./Pix/}}

\begin{document}
  \title{Advances in Robust Positive Invariant Sets Computation}

\author{Rainer M. Schaich\textsuperscript{\dag} %
         and Mark Cannon\textsuperscript{\dag,\ddag}%
\thanks{\textsuperscript{\dag} Department of Engineering Science, University of Oxford, OX1 3PJ.}%
\thanks{\textsuperscript{\ddag} Corresponding author, 
        \texttt{mark.cannon@eng.ox.ac.uk}.}
}

\maketitle

\begin{abstract}

\end{abstract}

\begin{keywords}
\vskip-\baselineskip
\end{keywords}

\section{Introduction}
\begin{equation}\label{eq:system:equation}
	x^+ = \Psi x + v
\end{equation}
\begin{equation}\label{eq:definition:mrpi:set:state:dependent}
	\mathcal X^\infty = \{x:\Psi x + v\in\mathcal X^\infty\; \forall v\in\mathcal V(x)\}
\end{equation}
\begin{equation}\label{eq:PWA:distrubance:set}
	\mathcal V(x) = \left\{v: Gv\leq\max\{{\bf{1}},H^x x\}\right\}
\end{equation}
\section{Parametrically convex set operations}
In this section we discuss sets that depend on a state-like parameter (so called point-to-set maps, 
see~\cite{Hogan:1973}), and extend the existing set algebra~\cite{blanchini:2007} to 
accommodate such sets. We present the general case first, then derive the computation of
the case with piece-wise affine sets.

%First we introduce
    \begin{defn}[Parametric Convexity]\label{def:parametric:convexity}
      Let $X\subseteq\mathbb R^n$ and $Y\subseteq\mathbb R^m$ and $T:X\rightarrow Y$, $X\ni s\mapsto T(s)\subset Y$ be a 
      continuous point-to-set map. The map $T$ is called \emph{parametrically convex} if it satisfies
      \begin{equation}\label{eq:pconvexdef}
        T(\lambda s_1 + (1-\lambda)s_2)\subseteq\lambda T(s_1) \oplus (1-\lambda) T(s_2)
      \end{equation}
      for all $s_1,s_2\in X$ and $\lambda\in[0,1]$.
    \end{defn}

In (\ref{eq:pconvexdef}), $\oplus$ denotes the Minkowski set addition
      \begin{equation}
        \mathcal A\oplus\mathcal B = \{c : c = a + b\; \forall\,a\in\mathcal A,\, b\in\mathcal B\}.
      \end{equation}
%      see~\cite{blanchini:2007}.
%    Note also that Definition~\ref{def:parametric:convexity} does not require $X$ and $Y$ to be of equal dimensions.
    In the following we will need to be able to compute differences of sets
    analogous to the Pontryagin difference in~\cite{Kolmanovsky:1998} but using parametrised 
    sets, this is defined as follows:

    \begin{defn}[Parametric Pontryagin Difference]\label{def:parametric:pontryagin:difference}
Let $S\subseteq X$ and let $T:X\to X$ be a continuous point-to-set map,
%      Let $T$ be a continuous point-to-set map from $X$ to $X$, and let $S\subseteq X$, 
then the \emph{parametric Pontryagin difference} $S\ominus T(S)$ is 
      \begin{equation}
        S\ominus T(S) = \left\{x\in X: \{x\} \oplus T(x)\subseteq S\right\},
      \end{equation}
      where $T(S)$ denotes the image of $S$ under the map $T$.
    \end{defn}

    For parametric Pontryagin differences of convex sets and parametrically convex maps we have the following result.

    \begin{thm}\label{thm:convexity:of:pontryagin:difference}
      Let $S\subseteq X$ be a convex set and let $T:X\rightarrow X$ be a parametrically convex point-to-set
      map, then $S\ominus T(S)$ is convex. 
    \end{thm}
    \begin{proof}
      Define $ Z =  S\ominus T( S)$ and let $z_1,z_2\in Z$, then
      by definition of the parametric Pontryagin difference, we have
      \begin{equation}
        \{z_i\} \oplus T(z_i) \subseteq S,\; i=1,2.
      \end{equation}
      To see that $ Z$ is convex we show that line segments between
      all possible $z_1$ and $z_2$ are subsets of $ Z$, i.e.~for all $\lambda \in [0,1]$,
%      \begin{equation}\label{eq:proof:of:parametric:convexity}
      \[\begin{aligned}
        \{ \lambda z_1 + (1-&\lambda)z_2
        \}\oplus T\left( \lambda z_1 + (1-\lambda)z_2\right)\\
        \subseteq&\left\{ \lambda z_1 + (1-\lambda)z_2
        \right\}\oplus \lambda T(z_1) \oplus (1-\lambda)
         T(z_2)\\
        \subseteq &\lambda\underbrace{(\{z_1\}\oplus T(z_1))}_{\subseteq S}\oplus
        (1-\lambda)\underbrace{(\{z_2\}\oplus T(z_2))}_{\subseteq S}\\
        \subseteq& Z
        \end{aligned}\]
%      \end{equation}
      where the last inclusion follows from the convexity of $\mathcal S$.
    \end{proof}

    In the given setup we consider a point-to-set map defined by
    \begin{equation}\label{eq:definition:disturbance:set}
      \mathcal V(x) = \{v:\,G v \leq H(x)\}
    \end{equation}
    where $H$ is elementwise convex in $x$, so that 
    $H_i(\lambda x_1+(1-\lambda)x_2)\leq \lambda H_i(x_1)+(1-\lambda)H_i(x_2)$ for 
    $\lambda\in[0,1]$.  For such sets we have the following result.
    \begin{thm}\label{thm:convex:parametric:set}
      $\mathcal V (x)$ defined in~\eqref{eq:definition:disturbance:set} is parametrically convex.
    \end{thm}
    \begin{proof}
      To show that $\mathcal V(\lambda x_1 + (1-\lambda)x_2)\subseteq 
      \lambda\mathcal V(x_1) \oplus(1-\lambda)\mathcal V(x_2)$ for all $\lambda \in [0,1]$ we note that
        \begin{align*}
        \mathcal V&(\lambda x_1 + (1-\lambda)x_2)\\
        =& \{v:\; G v \leq H(\lambda x_1 + (1-\lambda)x_2)\}\\
        \subseteq& \{v:\;Gv\leq\lambda H(x_1)+(1-\lambda) H(x_2)\}\\
        =&\{v:\;Gv\leq\lambda H(x_1)\}\oplus\{v
        :\;Gv\leq(1-\lambda)H(x_2)\}\\
        =&\lambda\mathcal V(x_1)\oplus(1-\lambda)\mathcal V(x_2).
        \end{align*}
\vskip-1.5\baselineskip
    \end{proof} 
\def\genmat{\Xi} \def\genvec{\xi}Lemmas~\ref{thm:convexity:of:pontryagin:difference} 
and~\ref{thm:convex:parametric:set} imply that the difference of a convex set and 
$\mathcal V(x)$ is a convex set.
Furthermore, we will see that if $\mathcal X$ is polyhedral and $\mathcal 
V(x)$ is as defined in~\eqref{eq:PWA:distrubance:set}, then $\mathcal X\ominus\mathcal V(\mathcal X)$ is 
again a polytopic set. This will become more clear in the next section when we describe 
the computation of the mRPI set~\eqref{eq:definition:mrpi:set:state:dependent}.

\section{Maximal Robust Positive Invariant Sets for State Dependent Disturbance}
In this section we describe an iterative algorithm to compute the mRPI 
set~\eqref{eq:definition:mrpi:set:state:dependent} for a linear system~\eqref{eq:system:equation}.
For this notice that the set $\mathcal V(x)$ can be represented as the convex hull of its vertices 
$\mathcal V(x) = \conv\{v_i(x)\}$. Since ${\mathcal{V}}(x)$
has a piece-wise affine dependence on $x$ the vertices $v_i(x)$ are also piece-wise affine in $x$.
The set $\mathcal X^\infty$ as defined in~\eqref{eq:definition:mrpi:set:state:dependent} 
requires to satisfy $\Psi x + v\in\mathcal X^\infty$ for all
$x\in\mathcal X^\infty$ and $v\in\mathcal V(x)$, to compute the mRPI set we start from a given set
$\mathcal X_0 = \{x:\;\genmat_{0,i}x\leq \genvec_{0,i}\,\forall i\in\mathcal I_0\}$, e.g.
the system constraints, and 
\emph{cut off} all points that do not satisfy the invariance condition in one step, two steps, 
etc. until only points satisfying the conditions are left. I.e. we iteratively introduce 
constraints that cut off all points for which the successor state can lie outside 
$\mathcal X_0$. So for the first iteration we need to enforce the constraint:
\begin{equation}\begin{split}
	&\genmat_{0,i}(\Psi x + v)\overset{!}{\leq}\genvec_{0,i}\;\forall v\in\conv\{v_i(x)\}\\
	&\genmat_{0,i}\Psi x + \max_{v\in\mathcal V(x)} \genmat_{0,i} v \leq \genvec_{0,i}\\
	&\genmat_{0,i}\Psi x + \underbrace{\max_{j} \genmat_{0,i} v_j(x)}_{v_{0,i}^\ast(x)} \leq \genvec_{0,i}.
\end{split}\end{equation}
to each inequality.
Notice that $v_{0,i}^\ast(x)$ is not necessarily given by one unique maximiser, 
but is the solution of a multiparametric linear program and hence will be given 
by a vertex $v_i(x)$ of $\mathcal V(x)$ for each $x$ on that facet.
Since each vertex is a piece-wise affine function of $x$ the maximum $v_{0,i}^\ast(x)$ will also
be piece-wise affine
and therefore the set $\mathcal X_1=\mathcal X_0 \cap \{x:\genmat_{0,i}\Psi x + v_{0,i}^\ast(x) \leq 
\genvec_{0,i}\forall i\in\mathcal I_0\}$
has the representation $\mathcal X_1 = \{x:\genmat_{1,i}x\leq\genvec_{1,i}\,\forall i\in\mathcal I_1\}$.
The next iterate is defined by
\begin{multline}
	\mathcal X_2 = \mathcal X_1 \cap \\ \{x:\genmat_{0,i}\Psi(\Psi x + v) + v_{0,i}^\ast(x)\leq\genvec_{0,i}\,
	\forall i\in\mathcal I_0,v\in\mathcal V(x)\}\\
	= \mathcal X_1 \cap \{x: \genmat_{0,i}\Psi^2 x + v_{1,i}^\ast(x) + v_{0,i}^\ast(x)\leq\genvec_{0,i}\,\forall 
	i\in\mathcal I_0\}.
\end{multline}
And we analogously define
\begin{equation}
	\mathcal X_{k+1} = \mathcal X_k\cap \{x:\genmat_{0,i}\Psi^k x + \sum_{l=0}^{k-1}v_{l,i}^\ast(x)
	\leq\genvec_{0,i}\,\forall i\in\mathcal I_0\},
\end{equation}
where we have 
\begin{multline}
	v_{l,i}^\ast(x)=\begin{split}\max& \genmat_{0,i}\Psi^{l-1}v_j(x)\\ j&\end{split}
	 = \begin{split}&\max \genmat_{0,i}\Psi^{l-1}v \\ &v\in\mathcal V(x)\end{split}\\
	= \begin{split}&\max \genmat_{0,i}\tilde v\\ &\tilde v\in \Psi^{l-1}\mathcal V(x) \end{split}
\end{multline}
In a closed form the iterates can be expressed as
\begin{equation}\label{eq:set:iteration:state:dependent:constraints}
\begin{split}
	\mathcal X_{k+1} =& \mathcal X_k\cap\left(\Psi^{-1}\mathcal X_k \ominus \Psi^{k-1}\mathcal V(\mathcal X_k)\right)
	=\mathcal X_k\cap D_k \\
	=& \bigcap_{l\leq k+1}\left( \Psi^{-l} \mathcal X_0 \underset{i\leq l-1}{\bigominus} \Psi^i \mathcal V(\mathcal X_{l-1})\right).
\end{split}\end{equation}
We will use~\eqref{eq:set:iteration:state:dependent:constraints} to prove the finite determinability of
$\mathcal X^\infty$, i.e. that there exists a finite number $N$ such that $x\in\mathcal X_N$ implies
$\Psi x + v \in\mathcal X_N$ for all $v\in\mathcal V(x)$ and the set therefore is robustly positive invariant.
\begin{thm}
Let the system constraints be contained in a band $\mathcal X_0\subseteq B=\{x:\Gamma x\leq{\bf{1}}\wedge 
-\Gamma x\leq{\bf{1}}\}$, let the pair $(\Psi,\Gamma)$ be observable and let $\mathcal V(\mathcal X_0)$ be bounded, 
then $\mathcal X_N\subseteq \mathcal X_{N+1}$ for a finite $N$. Hence the mRPI set $\mathcal X^\infty 
=\mathcal X_N$ is a finite polytope.
\end{thm}
\begin{proof}
The proof has two main steps: First we will prove that $\mathcal X_p$ is compact for $p\leq n$
where $n$ is the state dimension. The second step is to prove that in~\eqref{eq:set:iteration:state:dependent:constraints}
the set $D_k$ grows exponentially, i.e. that for any given compact set $\mathcal C$ there exists
a $\tilde N$ such that $\mathcal C\subseteq D_{\tilde N}$. The proof is concluded by setting 
$\mathcal C = \mathcal X_p$ and using $N = \tilde N$. For the first step, notice that the observability of
$(\Psi,\Gamma)$ is equivalent to the observability matrix $\Omega$ having full rank, i.e.
\[
\Omega = \left(\begin{array}{c}
\Gamma\\ \vdots \\ \Gamma\Psi^{n-1}
\end{array}\right)
\]
having a trivial kernel. But this then implies that the set $\mathcal P_{n+1} = \{x: 
\Omega x\leq{\bf{1}}\wedge-\Omega x\leq{\bf{1}}\} = \bigcap_{l\leq n+1} \Psi^{-l} B$ is bounded.
Notice that the containment $\mathcal X_k\subseteq \mathcal P_k$ holds for all $k$ and hence
the set $\mathcal X_{n+1}$ is also bounded. The case that $\tilde N<n$ occurs when $\Gamma$
has more than rank one. To see that $D_k$ grows exponentially we use that $\mathcal V(\mathcal X_0)$
is bounded, let $K_1$ denote the smallest ball that contains $\mathcal V(\mathcal X_0)$ and let
$\bar\lambda$ denote the magnitude of the largest eigenvalue of $\Psi$. Furthermore, let $K_1$
be the biggest ball that is contained in $\mathcal X_{0}$. $D_k$ has the representation
\begin{equation}
D_k = \underbrace{\Psi^{-k}\mathcal X_0}_{(\ast)} \ominus \underbrace{\left(\bigoplus_{i\leq k-1} 
\Psi^i\mathcal V(\mathcal X_k)\right)}_{(\ast\ast)}.
\end{equation}
Since $\Psi$ is asymptotically stable we know that $\bar\lambda<1$ and so we have 
$\bar\lambda^{-l}K_1\subseteq\Psi^{-l} K_1 \subseteq \Psi^{-l}\mathcal X_0 = (\ast)$
which implies exponential growth of $D_k$ as long as $(\ast\ast)$ is bounded.
To bound $(\ast\ast)$ we use $(\ast\ast)\subseteq \oplus_{i\leq k-1} \bar\lambda^i K_2 \subseteq
\frac{1}{1-\bar\lambda} K_2$. This concludes the proof: We proved that $D_k$ grows exponentially,
that it contains an exponentially growing ball. We proved that the subtrahend is bounded inside a ball of
finite radius, and hence we conclude that after a finite number of iterations $N$ intersecting with $D_{N+1}$
will no longer change $\mathcal X_N$.
\end{proof}
We have seen that we can compute a the maximal robust positive invariant set $\mathcal X^\infty$ for linear 
systems with state dependent constraints. In the next section we will illustrate the concept with an 
example.
\section{Example}
In this section we discuss the calculation of the mRPI set for a simplified model of the levitating
ball system depict in figure~\ref{fig:levitating:ball}. The system dynamics for the ball are given
by $m \ddot y = m g - c\frac{i^2}{y^2}$, where $m,g,c,i$ and $y$ denote the mass of the ball, the gravitational
constant, a constant factor, the current and the distance between the coil and the centre of the ball respectively.
For illustration purposes we neglect inductive dynamics and use the current $u=i$ as an input and the position
$y$ and its first derivative $\dot y$ as the states, i.e. $x = (y,\dot y)^T$. We find that an equilibrium
is present when $x_2=0$ and $u=\sqrt{\frac{gm}{c}}x_1$ for any positive position $x_1>0$.
Linearising the nonlinear differential equation $\dot x = f(x,u)$ around $\hat x, \hat u$ we obtain
\begin{equation}
	\Delta \dot x = \underbrace{\left(\begin{array}{cc}
	0 & 1 \\ \frac{2c\hat u^2}{m\hat x_1^3} & 0
	\end{array}\right)}_{\frac{\partial f}{\partial x}(\hat x,\hat u)}\Delta x + \underbrace{\left(\begin{array}{c}
	0 \\ - \frac{2c\hat u}{m\hat x_1^2}
	\end{array}\right)}_{\frac{\partial f}{\partial u}(\hat x,\hat u)}\Delta u.
\end{equation}
We derive discrete time system dynamics using the explicit Euler formula $x^+=x+T_s f(x,u) =:\tilde f(x,u)$,
with the sampling rate $T_s$. We hence define the system matrix $A = (I+T_s\frac{\partial f}{\partial x}(\hat x,\hat u))$
and the input matrix $B = T_s \frac{\partial f}{\partial u}(\hat x,\hat u)$. In order to obtain a 
representation of additive disturbances depending on the state and input like~\eqref{eq:definition:disturbance:set}
we use the mean-value theorem for vector valued functions:
\begin{thm}
Let $\mathcal X\subset\mathbb R^n$ be open, $f : \mathcal X \rightarrow\mathbb R^m$ continuously differentiable, 
and $x \in\mathcal X, h \in\mathbb R^n$ vectors such that the 
whole line segment $x + th$ remains in $\mathcal X$ for $0 \leq t \leq 1$. Then
\begin{equation}
	f(x+th) = f(x) + \left(\int_0^1 \frac{\partial f}{\partial x}(x+th)dt\right)\cdot h.
\end{equation}
\end{thm}
\begin{figure}
\centering
\begin{lpic}{levitatingBall}
\lbl[tr]{25,3; $m g$}
\lbl[br]{25,25; $c\frac{i^2}{x^2}$}
\lbl[bl]{49,17; $y$}
\lbl[bl]{56,55; $i$}
\end{lpic}
\caption{Levitating ball system.}
\label{fig:levitating:ball}
\end{figure}
\section{Maximal Robust Positive Invariant Sets for Parametrised Disturbance}
\section{Example}

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,MyLib}

\end{document}

### 2015-03-02 draft.tex
Initial draft.

@@
 \usepackage{lpic}
+% \usepackage{blkarray}
+\usepackage{mathrsfs}
 
@@
 \begin{document}
-  \title{Advances in Robust Positive Invariant Sets Computation}
+  \title{Advances in Robust Positive Invariant Set Computation}
 
@@
 \section{Introduction}
+Ever since the introduction of disturbance invariant sets in~\cite{Glover:1971}, the analytic
+properties of these sets have been fairly well studied, see~\cite{blanchini:2007}. Here by disturbance
+invariant sets we mean set $\mathscr X$ containing initial conditions for the perturbed linear system
 \begin{equation}\label{eq:system:equation}
-	x^+ = \Psi x + v
+	x^+ = \Psi x + v,
 \end{equation}
+where $\Psi$ is Hurwitz, $x,x^+\in\mathbb R^n$ the state and the successor state, and where 
+$v\in\mathscr V$ denotes the perturbation, such that the successor state is contained in the 
+disturbance invariant $x^+\in\mathscr X$ set for all possible realisations of the 
+perturbation $v\in\mathscr V$. That is summarised in the implicit definition
 \begin{equation}\label{eq:definition:mrpi:set:state:dependent}
-	\mathcal X^\infty = \{x:\Psi x + v\in\mathcal X^\infty\; \forall v\in\mathcal V(x)\}
+	\mathscr X = \{x:\Psi x + v\in\mathscr X\; \forall v\in\mathscr V\}.
 \end{equation}
+These sets are known as robust positive invariant (RPI) sets, for obvious reasons we are interested 
+the largest such set, i.e. the set containing all other RPI sets $\mathscr X\subseteq\mathcal X^\infty$,
+this set is called the maximal robust positive invariant (mRPI) set. Even though analytical properties
+of these sets were derived early after their introduction, it took more than two decades until algorithms
+were introduced to numerically compute mRPI sets~\cite{DeSantis:1994,Kolmanovsky:1995,Blanchini:1994}. Earlier algorithms
+did not guarantee finite determinability of $\mathcal X^\infty$, see e.g.~\cite{Blanchini:1990}, or 
+did not guarantee to produce the maximal RPI set, e.g.~\cite{Blanchini:1991}. 
+%
+In the afore mentioned algorithms the perturbation was considered to belong to a fixed compact set, in this paper
+we consider sets that vary with parameters. First we consider the set of disturbances to be state dependent, i.e.
 \begin{equation}\label{eq:PWA:distrubance:set}
-	\mathcal V(x) = \left\{v: Gv\leq\max\{{\bf{1}},H^x x\}\right\}
+	\mathcal V(x) = \left\{v: Gv\leq\max\{{\bf{1}},H^x x\}\right\},
 \end{equation}
-\section{Parametrically convex set operations}
+where the maximum is understood to be element-wise. This means that in the first part of the paper
+we will discuss the computation of $\mathcal X^\infty$ for the case where $\mathscr V=\mathcal V(x)$.
+The case where the disturbance depends on the state has been studied analytically before but not 
+extensively, see~\cite{Kuntsevich:1995}.
+
+The second case we consider is the case of a scaled set of disturbance, i.e.
+\begin{equation}
+  \mathcal V(\theta) = \{v:Gv\leq(1+\theta){\bf{1}}\},
+\end{equation}
+with $\theta>-1$. To distinguish the resulting sets from regular mRPI sets we use $\mathcal Z^\infty$
+to emphasise that $\mathcal Z^\infty$ itself is not an mRPI set, however by fixing $\theta=\hat\theta$ the
+set $\mathcal Z^\infty\vert_{\hat\theta}$ is an mRPI set. To our best knowledge, this setup has not been 
+presented in the literature.
+
+The remainder of this paper is structured: In section~\ref{sec:parametrically:convex:set:operations} we
+introduce the notion of \emph{parametric convexity} and of its general implications, this is necessary 
+for the convexity of the mRPI set. The algorithm to compute the mRPI set for state dependent disturbance
+constraints is presented in section~\ref{sec:state:dep:mrpi}, we also prove its finite determinability.
+In section~\ref{sec:first:example} we demonstrate the algorithm using a numerical exemplary system, a
+levitating ball setup. The case of scaled disturbance constraints is discussed in section~\ref{sec:mRPI:parametrised}
+where the algorithm for the parametrised mRPI set as well as the proof for its finite determinability
+are also presented. Section~\ref{sec:second:example} illustrates the use of parametrised mRPI sets using
+again the levitating ball example and illustrating some of possible robustness analyses of the parametrised
+mRPI sets with a numerical example. The paper is concluded in section~\ref{sec:conclusions}.
+%
+%
+%
+\section{Parametrically convex set operations}\label{sec:parametrically:convex:set:operations}
 In this section we discuss sets that depend on a state-like parameter (so called point-to-set maps, 
@@
 the case with piece-wise affine sets.
-
-%First we introduce
+%
+%
     \begin{defn}[Parametric Convexity]\label{def:parametric:convexity}
@@
     \end{defn}
-
+%
 In (\ref{eq:pconvexdef}), $\oplus$ denotes the Minkowski set addition
@@
       \end{equation}
-%      see~\cite{blanchini:2007}.
-%    Note also that Definition~\ref{def:parametric:convexity} does not require $X$ and $Y$ to be of equal dimensions.
+%
     In the following we will need to be able to compute differences of sets
@@
     sets, this is defined as follows:
-
+%
     \begin{defn}[Parametric Pontryagin Difference]\label{def:parametric:pontryagin:difference}
 Let $S\subseteq X$ and let $T:X\to X$ be a continuous point-to-set map,
-%      Let $T$ be a continuous point-to-set map from $X$ to $X$, and let $S\subseteq X$, 
 then the \emph{parametric Pontryagin difference} $S\ominus T(S)$ is 
@@
     \end{defn}
-
+%
     For parametric Pontryagin differences of convex sets and parametrically convex maps we have the following result.
-
+%
     \begin{thm}\label{thm:convexity:of:pontryagin:difference}
@@
     \end{thm}
+%
     \begin{proof}
@@
       all possible $z_1$ and $z_2$ are subsets of $ Z$, i.e.~for all $\lambda \in [0,1]$,
-%      \begin{equation}\label{eq:proof:of:parametric:convexity}
       \[\begin{aligned}
@@
         \end{aligned}\]
-%      \end{equation}
       where the last inclusion follows from the convexity of $\mathcal S$.
     \end{proof}
-
+%
+%
     In the given setup we consider a point-to-set map defined by
@@
     \end{proof} 
+%
+%
 \def\genmat{\Xi} \def\genvec{\xi}Lemmas~\ref{thm:convexity:of:pontryagin:difference} 
@@
 the computation of the mRPI set~\eqref{eq:definition:mrpi:set:state:dependent}.
-
-\section{Maximal Robust Positive Invariant Sets for State Dependent Disturbance}
+%
+%
+%
+%
+\section{Maximal Robust Positive Invariant Sets for State Dependent Disturbance}\label{sec:state:dep:mrpi}
 In this section we describe an iterative algorithm to compute the mRPI 
@@
 $\mathcal X_0$. So for the first iteration we need to enforce the constraint:
+%
 \begin{equation}\begin{split}
@@
 \end{split}\end{equation}
+%
 to each inequality.
@@
 The next iterate is defined by
+%
 \begin{multline}
@@
 \end{multline}
+%
 And we analogously define
+%
 \begin{equation}
@@
 \end{equation}
+%
 where we have 
+%
 \begin{multline}
@@
 \end{multline}
+%
 In a closed form the iterates can be expressed as
+%
 \begin{equation}\label{eq:set:iteration:state:dependent:constraints}
@@
 \end{split}\end{equation}
+%
 We will use~\eqref{eq:set:iteration:state:dependent:constraints} to prove the finite determinability of
@@
 $\Psi x + v \in\mathcal X_N$ for all $v\in\mathcal V(x)$ and the set therefore is robustly positive invariant.
-\begin{thm}
+%
+\begin{thm}\label{thm:finite:mRPI:set:state:dependable}
 Let the system constraints be contained in a band $\mathcal X_0\subseteq B=\{x:\Gamma x\leq{\bf{1}}\wedge 
@@
 \end{thm}
+%
 \begin{proof}
@@
 \end{proof}
+%
 We have seen that we can compute a the maximal robust positive invariant set $\mathcal X^\infty$ for linear 
@@
 example.
-\section{Example}
-In this section we discuss the calculation of the mRPI set for a simplified model of the levitating
-ball system depict in figure~\ref{fig:levitating:ball}. The system dynamics for the ball are given
-by $m \ddot y = m g - c\frac{i^2}{y^2}$, where $m,g,c,i$ and $y$ denote the mass of the ball, the gravitational
-constant, a constant factor, the current and the distance between the coil and the centre of the ball respectively.
-For illustration purposes we neglect inductive dynamics and use the current $u=i$ as an input and the position
-$y$ and its first derivative $\dot y$ as the states, i.e. $x = (y,\dot y)^T$. We find that an equilibrium
-is present when $x_2=0$ and $u=\sqrt{\frac{gm}{c}}x_1$ for any positive position $x_1>0$.
-Linearising the nonlinear differential equation $\dot x = f(x,u)$ around $\hat x, \hat u$ we obtain
-\begin{equation}
-	\Delta \dot x = \underbrace{\left(\begin{array}{cc}
-	0 & 1 \\ \frac{2c\hat u^2}{m\hat x_1^3} & 0
-	\end{array}\right)}_{\frac{\partial f}{\partial x}(\hat x,\hat u)}\Delta x + \underbrace{\left(\begin{array}{c}
-	0 \\ - \frac{2c\hat u}{m\hat x_1^2}
-	\end{array}\right)}_{\frac{\partial f}{\partial u}(\hat x,\hat u)}\Delta u.
-\end{equation}
-We derive discrete time system dynamics using the explicit Euler formula $x^+=x+T_s f(x,u) =:\tilde f(x,u)$,
-with the sampling rate $T_s$. We hence define the system matrix $A = (I+T_s\frac{\partial f}{\partial x}(\hat x,\hat u))$
-and the input matrix $B = T_s \frac{\partial f}{\partial u}(\hat x,\hat u)$. In order to obtain a 
-representation of additive disturbances depending on the state and input like~\eqref{eq:definition:disturbance:set}
-we use the mean-value theorem for vector valued functions:
-\begin{thm}
-Let $\mathcal X\subset\mathbb R^n$ be open, $f : \mathcal X \rightarrow\mathbb R^m$ continuously differentiable, 
-and $x \in\mathcal X, h \in\mathbb R^n$ vectors such that the 
-whole line segment $x + th$ remains in $\mathcal X$ for $0 \leq t \leq 1$. Then
-\begin{equation}
-	f(x+th) = f(x) + \left(\int_0^1 \frac{\partial f}{\partial x}(x+th)dt\right)\cdot h.
-\end{equation}
-\end{thm}
+%
+%
+%
+\section{Example}\label{sec:first:example}
+%
+%
 \begin{figure}
@@
 \end{figure}
-\section{Maximal Robust Positive Invariant Sets for Parametrised Disturbance}
-\section{Example}
+%
+%
+%
+In this section we discuss the calculation of the mRPI set for a simplified model of the levitating
+ball system depict in figure~\ref{fig:levitating:ball}. The system dynamics for the ball are given
+by $m \ddot y = m g - c\frac{i^2}{y^2}$, where $m,g,c,i$ and $y$ denote the mass of the ball, the gravitational
+constant, a constant factor, the current and the distance between the coil and the centre of the ball respectively.
+For illustration purposes we neglect inductive dynamics and use the current $u=i$ as an input and the position
+$y$ and its first derivative $\dot y$ as the states, i.e. $x = (y,\dot y)^T$. We find that an equilibrium
+is present when $x_2=0$ and $u=\sqrt{\frac{gm}{c}}x_1$ for any positive position $x_1>0$.
+Linearising the nonlinear differential equation $\dot x = f(x,u)$ around $\hat x, \hat u$ we obtain
+%
+\begin{equation}
+	\Delta \dot x = \underbrace{\left(\begin{array}{cc}
+	0 & 1 \\ \frac{2c\hat u^2}{m\hat x_1^3} & 0
+	\end{array}\right)}_{\frac{\partial f}{\partial x}(\hat x,\hat u)}\Delta x + \underbrace{\left(\begin{array}{c}
+	0 \\ - \frac{2c\hat u}{m\hat x_1^2}
+	\end{array}\right)}_{\frac{\partial f}{\partial u}(\hat x,\hat u)}\Delta u.
+\end{equation}
+%
+We derive discrete time system dynamics using the explicit Euler formula $x^+=x+T_s f(x,u) =:\tilde f(x,u)$,
+with the sampling rate $T_s$. We hence define the system matrix $A = (I+T_s\frac{\partial f}{\partial x}(\hat x,\hat u))$
+and the input matrix $B = T_s \frac{\partial f}{\partial u}(\hat x,\hat u)$. In order to obtain a 
+representation of additive disturbances depending on the state and input like~\eqref{eq:definition:disturbance:set}
+we use the mean-value theorem for vector valued functions:
+%
+%
+\begin{thm}\label{thm:mean:value:theorem}
+Let $\mathcal X\subset\mathbb R^n$ be open, $g : \mathcal X \rightarrow\mathbb R^m$ continuously differentiable, 
+and $x \in\mathcal X, h \in\mathbb R^n$ vectors such that the 
+whole line segment $x + th$ remains in $\mathcal X$ for $0 \leq t \leq 1$. Then
+\begin{equation}
+	g(x+h) = g(x) + \left(\int_0^1 \frac{\partial g}{\partial x}(x+th)dt\right)\cdot h.
+\end{equation}
+\end{thm}
+%
+%
+Using the mean value theorem~\ref{thm:mean:value:theorem}
+and the linearisation for $\Delta x = \hat x + \tilde x$ and $\Delta u = \hat u + \tilde u$ we
+get the successor state:
+%
+\begin{equation}
+	\begin{split}
+	\Delta x^+ = \underbrace{\tilde f(\hat x, \hat u)}_{\hat x} + \int_0^1\frac{\partial\tilde 
+	f}{\partial x}(\hat x + t\tilde x
+	,\hat u + t\tilde u)dt\cdot \tilde x +\\
+	 \int_0^1\frac{\partial\tilde f}{\partial u}(\hat x + t\tilde x
+	,\hat u + t\tilde u)dt\cdot \tilde u + A \tilde x + B \tilde u - A \tilde x - B\tilde u\\
+	\Leftrightarrow \tilde x^+ = A\tilde x + B \tilde x +\left(
+	\int_0^1\frac{\partial\tilde f}{\partial x}(\hat x + t\tilde x,\hat u + t\tilde u)dt - A
+	\right)\tilde x + \\ \left(
+	\int_0^1\frac{\partial\tilde f}{\partial u}(\hat x + t\tilde x,\hat u + t\tilde u)dt - B
+	\right)\tilde u
+	\end{split}
+\end{equation}
+%
+This implies that for any linearised state $\tilde x$ we obtain the expression
+$\tilde x^+ = A\tilde x+B\tilde u + H^x\tilde x + H^u \tilde u$, however the computation
+of $H^x$ and $H^u$ requires solving a nonlinear integral. Assume that inside given compact system
+constraints $\mathcal X$ and $\mathcal U$ we had extremal values of $H^x$ and $H^u$, i.e.
+$H^x\tilde x+H^u\tilde u\in\conv_k\{H^x_k\tilde x + H^u_k\tilde u\}$ for all $(\tilde x,\tilde u)\in\mathcal X\times \mathcal U$.
+Clearly, we can then introduce the element wise bound disturbance 
+%
+\begin{equation}\label{eq:definition:element:wise:constraints:on:nonlinearities}
+\begin{split}
+\mathcal V(x,u)=\left\{v:\min_k\{
+H^x_{k,i}x+H^u_{k,i}u\}\leq v_i\,\wedge\right. \\ \left.v_i \leq \max_k\{H^x_{k,i}x+H^u_{k,i}u\}\, i =1,\dots,n\right\}.
+\end{split}
+\end{equation}
+%
+With this set we can
+guarantee that $\tilde x^+ = A\tilde x + B\tilde u + v$ accounts for all nonlinearities within $\mathcal X
+\times\mathcal U$ if we constraint $v\in\mathcal V(\tilde x,\tilde u)$. For general nonlinear systems
+finding the extremal values of $(H^x,H^u)$ can not be done easily, so for the example of the 
+levitating ball we use the parameters: $Ts=30ms, C=1, m=100g, \hat x_1 = 50mm$ and $\mathcal X=\{x:
+\abs{\hat x_1-x_1}\leq 1mm\wedge \abs{x_2}\leq 105\frac{mm}{s}\}$, $\mathcal U=\{u:\abs{\hat u-u}\leq10mA\}$.
+Using 25 samples of $(H^x,H^u)$ we obtain the invariant set shown in figure~\ref{fig:mrpi:set:levitating:ball},
+which is less conservative than using fixed bounds on the nonlinearities as we will see in the next example.
+%
+%
+\begin{figure}
+\centering
+\begin{lpic}{invariantSetStateDependant(.65,)}
+{\tiny
+\lbl[r]{9,94; $0.1$}
+\lbl[r]{9,86; $0.08$}
+\lbl[r]{9,78; $0.06$}
+\lbl[r]{9,70; $0.04$}
+\lbl[r]{9,63; $0.02$}
+\lbl[r]{9,55; $0$}
+\lbl[r]{9,47; $-0.02$}
+\lbl[r]{9,39; $-0.04$}
+\lbl[r]{9,32; $-0.06$}
+\lbl[r]{9,24; $-0.08$}
+\lbl[r]{9,16; $-0.1$}
+\lbl[t]{11,9; $-6$}
+\lbl[t]{30,9; $-4$}
+\lbl[t]{48,9; $-2$}
+\lbl[t]{67.5,9; $0$}
+\lbl[t]{86,9; $2$}
+\lbl[t]{104,9; $4$}
+\lbl[t]{123,9; $6$}
+\lbl{120,3; $\times10^{-3}$}
+}
+{\small
+\lbl{68,3; $\tilde x_1$}
+\lbl{0,55,90; $\tilde x_2$}
+}
+\end{lpic}
+\caption{The maximal robust positive invariant set for the levitating ball system.}
+\label{fig:mrpi:set:levitating:ball}
+\end{figure}
+%
+%
+%
+%
+%
+\section{Maximal Robust Positive Invariant Sets for Parametrised Disturbance}\label{sec:mRPI:parametrised}
+%
+%
+In this section we describe the computation of the mRPI set for~\eqref{eq:system:equation}
+but using a disturbance set that is parametrised for scaling, i.e. $\mathcal V(\theta) = \{v: Gv\leq(1+\theta){\bf{1}}\} 
+= (1+\theta)\mathcal V(0)$, for $\theta>-1$. We will be able to combine the uniform scaling of 
+the disturbance set $\mathcal V(\theta)$ with non-uniform scaling of the input constraint set
+$\mathcal U({\bf{\alpha}}) = \{u: Fu\leq\left(I+\text{diag}(\alpha_1,\dots,\alpha_p)\right){\bf{1}}\}$, 
+this can be used to study closed loop systems subject to a given feedback controller.
+%
+\begin{rem}
+The set $\mathcal V(\theta)$ is nonempty and contains the origin for all $\theta>-1$ and hence the 
+maximum
+%
+\[
+0<\begin{array}{rl}
+\max & c^T v\\
+\text{s.t.}& Gv \leq (1+\theta){\bf{1}}\\
+&\theta>-1
+\end{array}
+\]
+%
+is positive for any nonzero $c$.
+\end{rem}
+%
+In the following we describe an algorithm to compute the mRPI set $\mathcal Z^\infty$ contained in 
+$\mathcal Z = \{(x,\theta):\mathcal F_i x+\mathcal G_i\theta \leq 1,\forall\, i\leq m\}$.
+As in the state dependent case we iteratively introduce constraints \emph{cutting off} points
+for which the successor state can lie outside the previous set, i.e. starting from $Z_0 = \mathcal Z$
+we determine the first iterate by enforcing all individual constraints onto all possible successor states:
+$Z_1=Z_0\cap D_0$ where $D_0$ is defined by
+%
+\begin{equation}\small
+\begin{split}
+	D_0 =& \{\mathcal F_i(\Psi x+v) + \mathcal G_i\theta \leq 1 \forall\, v\in\mathcal V(\theta), i\leq m\}\\
+	=&\left\{\mathcal F_i\Psi x + \begin{array}{rl}\max& F_i v \\ \text{s.t.}& Gv \leq 
+	(1+\theta){\bf{1}} \\ &\theta>-1\end{array}
+	 + \mathcal G_i \theta \leq 1 \forall\, i\leq m\right\}\\
+	=&\left\{\mathcal F_i\Psi x + (1+\theta)\underbrace{\begin{array}{rl}\max& F_i v \\ 
+	\text{s.t.}& Gv \leq {\bf{1}}\end{array}}_{v_{0,i}^\ast}
+	 + \mathcal G_i \theta \leq 1 \forall\, i\leq m\right\}\\
+	=&\{\mathcal F_i\Psi x + (\mathcal G_i + v_{0,i}^\ast)\theta \leq 1 - v_{0,1}^\ast \forall i\leq m
+	\}
+\end{split}\end{equation}
+%
+Using the same principle we define $Z_{k+1}=Z_k\cap D_k$ with $D_k$ given by
+%
+\begin{equation}\label{eq:parametrised:Dk}\small
+	D_k = \{\mathcal F_i\Psi^{k+1}x+ \left(\mathcal G_i +\sum_{0\leq l\leq k} v_{l,i}^\ast\right)\theta \leq 1 
+	- \sum_{0\leq l\leq k} v_{l,i}^\ast\, i\leq m\}
+\end{equation}
+%
+where we use 
+%
+\begin{equation}\label{eq:definition:v:ast}
+v_{l,i}^\ast = \begin{array}{rl}\max & \mathcal F_i \Psi^{l} v \\ \text{s.t.}& Gv\leq{\bf{1}}
+\end{array}
+\end{equation}
+%
+Notice that~\eqref{eq:definition:v:ast} can be represented in various ways:
+%
+\[
+\begin{array}{rl}
+\max&\mathcal F_i \Psi^l v \\ \text{s.t.}&v\in\bar{\mathcal{V}}
+\end{array} = 
+\begin{array}{rl}
+\max&\mathcal F_i \tilde  v \\ \text{s.t.}&\Psi^{-l} \tilde v\in\bar{\mathcal{V}}
+\end{array} = 
+\begin{array}{rl}
+\max&\mathcal F_i v \\ \text{s.t.}& \tilde v\in\Psi^l\bar{\mathcal{V}}
+\end{array}
+\]
+%
+$\bar{\mathcal{V}}=\mathcal V(0)$ for notational convenience. So that for any fixed $\hat\theta>-1$
+we have the closed form description
+%
+\begin{equation}\label{eq:closed:form:parametrised:iterates}
+\begin{split}
+	Z_{k+1}\vert_{\hat\theta} &= Z_{k}\vert_{\hat\theta}\cap\left(
+	\Psi^{-1}Z_k\vert_{\hat\theta}\ominus\Psi^{k-1}\mathcal V(\hat\theta)\right)\\
+	&=\bigcap_{l\leq k}\left(\Psi^{-l}\mathcal Z\vert_{\hat\theta}\underset{i\leq l-1}{\bigominus} 
+	\Psi^i \mathcal V(\hat\theta)
+	\right).
+\end{split}
+\end{equation}
+%
+The iteration terminates when $Z_k\subseteq Z_{k+1}$. Like in section~\ref{sec:state:dep:mrpi}
+we will require $\mathcal Z\vert_{\hat\theta}$ to be contained in an observable band, i.e. that 
+the set $\{x:\mathcal Fx \leq {\bf{1}}-\mathcal G\hat\theta\}=\mathcal Z\vert_{\hat\theta}\subseteq
+\mathcal B=\{x:\Gamma x\leq {\bf{1}}\wedge -\Gamma x\leq {\bf{1}}\}$ for all $\hat\theta>-1$. We have the
+%
+\begin{thm}
+Let the system constraints be contained in a band $\mathcal Z\vert_{\hat\theta}\subseteq\mathcal 
+B=\{x:\Gamma x\leq {\bf{1}}\wedge -\Gamma x\leq {\bf{1}}\}$ for any fixed $\hat\theta$, let the
+pair $(\Psi,\Gamma)$ be observable and let $\mathcal V(0)$ be bounded, then $Z_N\subseteq Z_{N+1}$
+for a finite $N$. Hence the mRPI set $\mathcal Z^\infty = Z_N$ is a finite polyhedron.
+\end{thm}
+%
+\begin{proof}
+The argumentation in this completely analogue to the one in Lemma~\ref{thm:finite:mRPI:set:state:dependable}.
+First we argue that for each fixed $\hat\theta$ the set $Z_k\vert_{\hat\theta}$ becomes compact using the same
+observability argument as in Lemma~\ref{thm:finite:mRPI:set:state:dependable}.
+We then use the representation~\eqref{eq:closed:form:parametrised:iterates} to argue that $D_k$ as
+in~\eqref{eq:parametrised:Dk} grows exponentially and therefore contains any compact set after a finite number
+of iterations. The fact that $\theta$ was fixed to $\hat\theta$ does not change anything since
+our argument is constructed for a fixed matrix $\Gamma$ where the rows had to be scaled by 
+$\frac{1}{1-\mathcal G_i\hat\theta}$ and we could rescale them to accommodate any other choice of $\hat\theta>-1$.
+\end{proof}
+We now have a way to scale the the disturbance set uniformly, as mentioned earlier we can extend the algorithm
+to accommodate non uniformly parametrised input constraints to accommodate more degrees of freedom for 
+system analysis by simply using $\mathcal Z = \{(x,\theta,\alpha): \mathcal F x + \mathcal G\theta + 
+\mathcal H \alpha \leq {\bf{1}}\}$. This does not affect the algorithm since at each step of the iteration 
+the elements of $\mathcal H$ remain unchanged. In the next section we will illustrate the algorithm.
+%
+%
+%
+%
+%
+%
+\section{Example}\label{sec:second:example}
+%
+%
+In this section we compute the mRPI set for the levitating ball exemplary system presented in 
+section~\ref{sec:first:example} as well as for a direct torque fed pendulum to illustrate both
+the effectiveness of the afore presented algorithm for state dependent disturbances as well as
+the system analysis tool that is the parametrised mRPI set. First we present the parametrised mRPI
+set for the levitating ball, notice that in order to obtain comparable results we need to get fixed bounds
+on the effect of nonlinearities on each state, i.e. a constant version 
+of~\eqref{eq:definition:element:wise:constraints:on:nonlinearities}. Using the same constraint set 
+$\mathcal X \times \mathcal U$ to determine the maximal and minimal values for nonlinear effects
+we obtain a constant set which is non symmetric around the origin due to nonlinearity. We also introduce
+a scaling parameter $\alpha$ such that $\mathcal U(0)=\mathcal U$. For this setup we obtain the mRPI
+set $\mathcal Z^\infty=\{(x,\theta,\alpha): \Lambda_i^x x + \Lambda_i^\theta \theta + \Lambda_i^\alpha \alpha\leq
+\lambda_i\,\forall i\leq m_\infty\}$. Notice that since $\alpha$ was introduced as a scaling parameter
+for $\mathcal U(\alpha)=\{u: Fu\leq (1+\alpha){\bf{1}}\}$ all entries in $\mathcal H$ are non positive and
+remain unchanged throughout the computation of $\mathcal Z^\infty$ so that $\Lambda^\alpha$ has only non
+positive entries, i.e. increasing $\alpha$ will enlarge the parametrised mRPI set $\mathcal Z^\infty\vert_{\alpha_1}
+\subseteq\mathcal Z^\infty\vert_{\alpha_2}$ for $\alpha_1\leq\alpha_2$.
 
+First we want to compare the mRPI set $\mathcal X^\infty$ obtained with state dependent disturbance 
+constraints with the parametrised one $\mathcal Z^\infty$. To do this we compute the scaling parameter 
+$\alpha_{\min}$ such that $\mathcal X^\infty\subseteq\mathcal Z^\infty\vert_{(0,\alpha_{\min})}$.
+We can do this by solving $m_\infty$ linear programs
+%
+%
+\[
+	\gamma_i^\ast = \left\{\begin{split}
+	\max& \;\Lambda_i^x x\\
+	\text{s.t.}& \;x\in\mathcal X^\infty
+	\end{split}
+	\right.
+\]
+%
+%
+The minimal value for $\alpha_{\min}$ is then given by the maximal $\alpha$ satisfying $\gamma_i^\ast + 
+\Lambda_i^\theta\cdot 0 + \Lambda_i^\alpha \alpha \leq \lambda_i$. Solving this we obtain the 
+minimal value $\alpha_{\min} = 1.7555$ and the mRPI sets shown in Figure~\ref{fig:minimal:scaling:comparison:mRPIs}.
+Caution is advised when interpreting $\alpha>0$, since the system is nonlinear extrapolations bare very
+little insight, the only information we can safely extract is that the current set of inputs $\mathcal U(0)=\mathcal U$ 
+is not large enough to cope with the perturbation set containing given by upper bounds of the nonlinear effects.
+%
+%
+\begin{figure}
+\begin{lpic}{minimalAlphaForConstantDisturbance(.65,)}
+{\tiny
+\lbl[r]{7,87;$1.5$}
+\lbl[r]{7,69;$1$}
+\lbl[r]{7,51;$0.5$}
+\lbl[r]{7,34;$0$}
+\lbl[r]{7,16;$-0.5$}
+\lbl[t]{15,2;$-0.06$}
+\lbl[t]{27,2;$-0.05$}
+\lbl[t]{39,2;$-0.04$}
+\lbl[t]{51,2;$-0.03$}
+\lbl[t]{63,2;$-0.02$}
+\lbl[t]{75,2;$-0.01$}
+\lbl[t]{89,2;$0$}
+\lbl[t]{100,2;$0.01$}
+\lbl[t]{113,2;$0.02$}
+}
+{\footnotesize
+\lbl[r]{5,45,90;$\tilde x_2$}
+\lbl[t]{121,3;$\tilde x_1$}
+}
+\lbl[l]{93,32;$\longleftarrow\mathcal X^\infty$}
+\lbl[r]{68,43;$\mathcal Z^\infty\vert_{(\alpha_{\min},0)}\longrightarrow$}
+\end{lpic}
+\caption{Minimal scaling for mRPI set computed for constant disturbance which contains
+ mRPI set for piecewise affine disturbances is $\alpha=1.7555$. Note that since the nonlinearities of the system
+ dynamics are not symmetrical around the equilibrium the mRPI set with fixed constraints on the perturbation
+ is non-symmetric.}
+ \label{fig:minimal:scaling:comparison:mRPIs}
+\end{figure}
+
+In the second example we compute the parametrised mRPI set for the system
+$$
+x^+ = \underbrace{\left(\begin{array}{cc}1 & 2 \\ 0 & 1\end{array}\right)}_Ax + 
+\underbrace{\left(\begin{array}{cc} 1 & 1 \\ 1 & -1\end{array}\right)}_B u + 
+\underbrace{\left(\begin{array}{cc} 1 & 2 \\ 2 & 1 \end{array}\right)}_D w
+$$
+We use the constraint sets $\mathcal U(\alpha) = \{u: Fu\leq(I+\text{diag}(\alpha)){\bf{1}} \wedge
+-Fu\leq (I+\text{diag}(\alpha)){\bf{1}}\}$ and $\mathcal V(\theta) = D\mathcal W(\theta)$ where $\mathcal W(\theta) = \{w:
+\abs{w_1}\leq 0.1(1+\theta)\wedge \abs{w_2}\leq 0.15(1+\theta)\}$. The constraint matrix $F$ is given by
+$$
+	F = \left(\begin{array}{cc} 2 & 2 \\ 4 & 0 \\ 2 & -2 \end{array}\right).
+$$
+We can now analyse the effect of changing individual constraints on the input by changing $\alpha$ as well as the
+effect of perturbations. To initialise the iteration we use
+$\mathcal Z(x,\theta,\alpha) = \left\{(x,\theta,\alpha): Kx\in\mathcal U(\alpha)\wedge K_w x\in\mathcal W
+(\theta)\wedge \alpha,\theta>-{\bf{1}}\right\}$, with $K$ and $K_w$ being the solution to the semidefinite program
+$x^TPx - ((A+BK)x+Dw)^TP((A+BK)x+Dw)\geq x^T(Q+K^TRK)x -\gamma^2 w^Tw$, i.e. $K_w = (\gamma^2-D^TPD)D^TP(A+BK)$.
+We use $Q = \text{diag}(2,1)$ and $R = I$. Using these numerical values we determine the mRPI set 
+$\mathcal Z^\infty$ after 22 iterations, it has 61 facets. Notice that in addition to the sign of 
+the sensitivity of the mRPI set on $\alpha$ we know that since we introduced each facet of $\mathcal Z$
+to depend only on one $\alpha_i$, since the algorithm does not change the elements corresponding to $\alpha$
+and due to orthogonality two facets depending on different elements of $\alpha$ can not be reduced to 
+one facet depending on both. I.e. $\Lambda^\alpha$ has no more than one entry per row. We can therefore 
+compute which $\alpha_i$ will change the mRPI set the most. This can be done by element wise calculating
+$$
+	\max_i  \frac{-\Lambda_i^\alpha}{\norm{\Lambda_i^x}_2}.
+$$
+In our example the greatest sensitivity corresponds to $\alpha_3$ with a numerical value of $2.6458\times 10^9$, 
+i.e. the third input constraint.
+Analogue to the first example we might want to know how much disturbance the closed loop system can 
+take such that a given set is contained in the mRPI set $\mathcal C\subseteq\mathcal Z^\infty\vert_{(\theta,0)}$.
+We used the non-positivity of $\mathcal H$ to argue the non-positivity of $\Lambda^\alpha$, however we
+can not use a similar argument for $\Lambda^\theta$, in fact it is easy to see that both signs are likely to be 
+present in $\Lambda^\theta$. The condition $\theta>-1$ implies that $\Lambda^\theta$ has at least one negative
+element, on the other hand the elements of $\Lambda^\theta$ are given by $\mathcal G_i + \sum_{l\leq k}v_{l,i}^\ast$.
+We know $\mathcal G$ and hence we know that most entries are zero, so that $\Lambda^\theta$ has positive entries.
+Let $(\Lambda^1,\lambda^1)$ and $(\Lambda^2,\lambda^2)$ denote all rows such that $\Lambda^{1,\theta}>0$ and
+$\Lambda^{2,\theta}\leq0$. This implies that for any fixed $\hat\alpha$ the set $\mathcal Z^\infty\vert_{\hat\alpha}$
+is compact, since $\mathcal Z^\infty\vert_{(\hat\alpha,\hat\theta)}$ is compact and there exists a maximal $\theta_{\max}$
+such that $\Lambda^{1,x}x+\Lambda^{1,\alpha}\hat\alpha+\Lambda^{1,\theta}\theta\leq\lambda^1$ can be satisfied
+analogue there is a minimal $\theta_{\min}$. We can solve the optimisation programs
+$$
+	\gamma_i = \left\{\begin{array}{rl}
+	\max& \Lambda^{1,x}x\\
+	\text{s.t.}& x\in\mathcal C
+	\end{array}
+	\right.\;
+	\delta_i = \left\{\begin{array}{rl}
+	\max& \Lambda^{2,x}x\\
+	\text{s.t.}& x\in\mathcal C
+	\end{array}
+	\right. .
+$$
+The extremal values for which $\mathcal C$ is contained in the mRPI set are given by
+the smallest $\theta_{\max}$ satisfying $\gamma_i+\Lambda^{1,\alpha}_i\hat\alpha+
+\Lambda^{1,\theta}_i\theta_{\max}\leq\lambda_i^1$ and the largest $\theta_{\min}$ 
+satisfying $\delta_i+\Lambda^{2,\alpha}_i\hat\alpha+\Lambda^{2,\theta}_i\theta_{\min}\leq\lambda_i^2$
+The numerical values for the example are given by $[\theta_{\min},\theta_{\max}]=[-0.9999,6.2582]$.
+A two and three dimensional illustration of the parametrised mRPI set is given in Figure~\ref{fig:two:dim:example}
+and~\ref{fig:three:dim:example} respectively.
+%
+%
+%
+\begin{figure}
+\includegraphics[width=\columnwidth]{twoDimensional}
+\caption{The extremal mRPI sets $\mathcal Z^\infty\vert_{({\bf{0}},\theta_{min})}$ and $\mathcal Z^\infty
+\vert_{({\bf{0}},\theta_{\max})}$ containing the unit box.}
+\label{fig:two:dim:example}
+\end{figure}
+\begin{figure}
+\includegraphics[width=\columnwidth]{threeDimensional}
+\caption{The parametrised mRPI set for $\alpha={\bf{0}}$. Containing the unit box in the 
+interior between $\theta_{\min}$ and $\theta_{\max}$.}
+\label{fig:three:dim:example}
+\end{figure}
+%
+%
+%
+\section{Conclusions}\label{sec:conclusions}
+%
+In this paper we discussed extensions to existing computational methods to determine mRPI sets
+for linear systems subject to additive disturbance in two cases. The case of state dependent case
+which can be applied to determine approximations to mRPI sets for linearised nonlinear systems as was shown
+for the example of a levitating ball system. We also introduced the computation of mRPI sets using 
+scaling parameters which allows various system analyses using uniform scaling for the disturbance sets
+and non-uniform scaling for the input constraints. The effectiveness of state dependent disturbance
+sets was demonstrated by comparing the two mRPI methods.
 \bibliographystyle{IEEEtran}
 \bibliography{IEEEabrv,MyLib}
-
+%
 \end{document}

### 2015-03-03 draft.tex
Moved pictures to local directory.
Added abstract.

@@
-\documentclass[letterpaper, 10pt, conference]{ieeeconf/ieeeconf} % Change font size to 9pt
+\documentclass[letterpaper, 10pt, conference]{ieeeconf} % Change font size to 9pt
 
@@
 \begin{abstract} 
-
+In this paper we introduce methods of deriving and computing maximal positive robust invariant
+sets for linear discrete time systems with additive uncertainty. We consider two different sets of
+uncertainties, state dependent uncertainty which allows us to handle multiplicative as well as
+linearised systems easily, and scaled sets of uncertainty. We provide the framework for the analytic
+treatment of both and illustrate their benefits in two numerical examples.
 \end{abstract}

### 2015-03-15 draft.tex
Revised changes.

@@
 \usepackage{mathrsfs}
+\usepackage{todonotes}
 
@@
 }
+\newcommand{\note}[1]{\todo[inline]{#1}}
 
@@
 properties of these sets have been fairly well studied, see~\cite{blanchini:2007}. Here by disturbance
-invariant sets we mean set $\mathscr X$ containing initial conditions for the perturbed linear system
+invariant sets we mean a subset of the state constraint set $\mathscr X\subseteq\mathcal X_0\subseteq\mathbb R^n$ 
+containing initial conditions for the perturbed linear system
 \begin{equation}\label{eq:system:equation}
@@
 \end{equation}
-where $\Psi$ is Hurwitz, $x,x^+\in\mathbb R^n$ the state and the successor state, and where 
+where $\Psi$ is Hurwitz, $x,x^+\in\mathcal X_0$ the state and the successor state, and where 
 $v\in\mathscr V$ denotes the perturbation, such that the successor state is contained in the 
-disturbance invariant $x^+\in\mathscr X$ set for all possible realisations of the 
+disturbance invariant set $x^+\in\mathscr X$ for all possible realisations of the 
 perturbation $v\in\mathscr V$. That is summarised in the implicit definition
-\begin{equation}\label{eq:definition:mrpi:set:state:dependent}
+\begin{equation}\label{eq:definition:MRPI:set:state:dependent}
 	\mathscr X = \{x:\Psi x + v\in\mathscr X\; \forall v\in\mathscr V\}.
 \end{equation}
-These sets are known as robust positive invariant (RPI) sets, for obvious reasons we are interested 
-the largest such set, i.e. the set containing all other RPI sets $\mathscr X\subseteq\mathcal X^\infty$,
-this set is called the maximal robust positive invariant (mRPI) set. Even though analytical properties
+These sets are known as robust positive invariant (RPI) sets. In many applications we are interested in the largest such
+set $\mathcal X^\infty$, i.e. the set containing all other RPI sets $\mathscr X\subseteq\mathcal X^\infty$,
+this set is called the maximal robust positive invariant (MRPI) set. These sets are used e.g. as terminal regions in 
+robust model predictive control. Even though analytical properties
 of these sets were derived early after their introduction, it took more than two decades until algorithms
-were introduced to numerically compute mRPI sets~\cite{DeSantis:1994,Kolmanovsky:1995,Blanchini:1994}. Earlier algorithms
+were introduced to numerically compute MRPI sets~\cite{DeSantis:1994,Kolmanovsky:1995,Blanchini:1994}. 
+\note{You commented 'check', I didn't know what that meant.}
+Earlier algorithms
 did not guarantee finite determinability of $\mathcal X^\infty$, see e.g.~\cite{Blanchini:1990}, or 
@@
 In the afore mentioned algorithms the perturbation was considered to belong to a fixed compact set, in this paper
-we consider sets that vary with parameters. First we consider the set of disturbances to be state dependent, i.e.
+we consider sets that vary with parameters. First we consider the set of disturbances to be state dependent, e.g.
 \begin{equation}\label{eq:PWA:distrubance:set}
-	\mathcal V(x) = \left\{v: Gv\leq\max\{{\bf{1}},H^x x\}\right\},
+	\mathcal V(x) = \left\{v: Gv\leq H(x)\right\},
 \end{equation}
-where the maximum is understood to be element-wise. This means that in the first part of the paper
-we will discuss the computation of $\mathcal X^\infty$ for the case where $\mathscr V=\mathcal V(x)$.
+where $H(x)$ is a piecewise affine function. This means that in the first part of the paper
+we discuss the computation of $\mathcal X^\infty$ for the case where $\mathscr V=\mathcal V(x)$.
 The case where the disturbance depends on the state has been studied analytically before but not 
-extensively, see~\cite{Kuntsevich:1995}.
+extensively, see~\cite{Kuntsevich:1995}. These kind of disturbance constraints can be used to
+account for linearisation errors, as will be shown in section~\ref{sec:first:example}, but can also
+be used to treat multiplicative uncertainty.
 
@@
 \end{equation}
-with $\theta>-1$. To distinguish the resulting sets from regular mRPI sets we use $\mathcal Z^\infty$
-to emphasise that $\mathcal Z^\infty$ itself is not an mRPI set, however by fixing $\theta=\hat\theta$ the
-set $\mathcal Z^\infty\vert_{\hat\theta}$ is an mRPI set. To our best knowledge, this setup has not been 
-presented in the literature.
+with $\theta>-1$. To distinguish the resulting sets from regular MRPI sets we use $\mathcal Z^\infty$
+to emphasise that $\mathcal Z^\infty$ itself is not an MRPI set, however by fixing $\theta=\hat\theta$ the
+set $\mathcal Z^\infty\vert_{\hat\theta}$ is an MRPI set. To our best knowledge, this setup has not been 
+presented in the literature. This type of disturbance constraints can be used to study the sensitivity of
+the MRPI set to changes in the disturbance \emph{strength}.
 
 The remainder of this paper is structured: In section~\ref{sec:parametrically:convex:set:operations} we
-introduce the notion of \emph{parametric convexity} and of its general implications, this is necessary 
-for the convexity of the mRPI set. The algorithm to compute the mRPI set for state dependent disturbance
-constraints is presented in section~\ref{sec:state:dep:mrpi}, we also prove its finite determinability.
+introduce the notion of \emph{parametric convexity} and of its general implications, this is sufficient 
+for the convexity of the MRPI set. The algorithm to compute the MRPI set for state dependent disturbance
+constraints is presented in section~\ref{sec:state:dep:MRPI}, we also prove its finite determinability.
 In section~\ref{sec:first:example} we demonstrate the algorithm using a numerical exemplary system, a
-levitating ball setup. The case of scaled disturbance constraints is discussed in section~\ref{sec:mRPI:parametrised}
-where the algorithm for the parametrised mRPI set as well as the proof for its finite determinability
-are also presented. Section~\ref{sec:second:example} illustrates the use of parametrised mRPI sets using
+levitating ball setup. The case of scaled disturbance constraints is discussed in section~\ref{sec:MRPI:parametrised}
+where the algorithm for the parametrised MRPI set as well as the proof for its finite determinability
+are also presented. Section~\ref{sec:second:example} illustrates the use of parametrised MRPI sets using
 again the levitating ball example and illustrating some of possible robustness analyses of the parametrised
-mRPI sets with a numerical example. The paper is concluded in section~\ref{sec:conclusions}.
+MRPI sets with a numerical example. The paper is concluded in section~\ref{sec:conclusions}.
+
+In the remainder of this paper we use the notion of a polyhedra for sets that can be represented as
+the intersection of a finite number of halfspaces, polytopic sets for bounded polyhedral.
+By ${\bf{1}}$ we denote the column vector of ones in appropriate dimension, $\wedge$ denotes the logical and. 
 %
@@
     \begin{defn}[Parametric Convexity]\label{def:parametric:convexity}
-      Let $X\subseteq\mathbb R^n$ and $Y\subseteq\mathbb R^m$ and $T:X\rightarrow Y$, $X\ni s\mapsto T(s)\subset Y$ be a 
+      Let $X\subseteq\mathbb R^n, Y\subseteq\mathbb R^m$, let $\mathcal P(Y)$ denote the power set of $Y$ 
+      and $T:X\rightarrow \mathcal P(Y)$, $X\ni s\mapsto T(s)\subset Y$ be a 
       continuous point-to-set map. The map $T$ is called \emph{parametrically convex} if it satisfies
@@
     \begin{defn}[Parametric Pontryagin Difference]\label{def:parametric:pontryagin:difference}
-Let $S\subseteq X$ and let $T:X\to X$ be a continuous point-to-set map,
+Let $S\subseteq X$ and let $T:X\to\mathcal P(X)$ be a continuous point-to-set map,
 then the \emph{parametric Pontryagin difference} $S\ominus T(S)$ is 
-      \begin{equation}
+      \begin{equation}\label{eq:definition:parametric:pontryagin:difference}
         S\ominus T(S) = \left\{x\in X: \{x\} \oplus T(x)\subseteq S\right\},
@@
 %
+    Notice that for constant maps $T$
+    definition~\eqref{eq:definition:parametric:pontryagin:difference} is equivalent to the 
+    well known Pontryagin difference.
     For parametric Pontryagin differences of convex sets and parametrically convex maps we have the following result.
@@
     \begin{thm}\label{thm:convexity:of:pontryagin:difference}
-      Let $S\subseteq X$ be a convex set and let $T:X\rightarrow X$ be a parametrically convex point-to-set
+      Let $S\subseteq X$ be a convex set and let $T:X\rightarrow\mathcal P(X)$ be a parametrically convex point-to-set
       map, then $S\ominus T(S)$ is convex. 
@@
 %
-    In the given setup we consider a point-to-set map defined by
-    \begin{equation}\label{eq:definition:disturbance:set}
-      \mathcal V(x) = \{v:\,G v \leq H(x)\}
-    \end{equation}
-    where $H$ is elementwise convex in $x$, so that 
+  Consider a point-to-set map defined by~\eqref{eq:PWA:distrubance:set}
+    where, for now, $H$ is elementwise convex in $x\in \mathscr X\subseteq\mathbb R^n$, so that 
     $H_i(\lambda x_1+(1-\lambda)x_2)\leq \lambda H_i(x_1)+(1-\lambda)H_i(x_2)$ for 
-    $\lambda\in[0,1]$.  For such sets we have the following result.
+    $\lambda\in[0,1]$ and $x_1, x_2\in X$.  For such sets we have the following result:
     \begin{thm}\label{thm:convex:parametric:set}
-      $\mathcal V (x)$ defined in~\eqref{eq:definition:disturbance:set} is parametrically convex.
+      The point-to-set map $\mathcal V (x)$ defined in~\eqref{eq:PWA:distrubance:set} is parametrically 
+      convex for all $x\in X.$
     \end{thm}
@@
 \def\genmat{\Xi} \def\genvec{\xi}Lemmas~\ref{thm:convexity:of:pontryagin:difference} 
-and~\ref{thm:convex:parametric:set} imply that the difference of a convex set and 
-$\mathcal V(x)$ is a convex set.
+and~\ref{thm:convex:parametric:set} imply that the parametric Pontryagin difference between a convex set $\mathcal X$ and 
+the point-to-set map $\mathcal V(x)$, i.e. $\mathcal X\ominus \mathcal V(\mathcal X)$, is a convex set.
 Furthermore, we will see that if $\mathcal X$ is polyhedral and $\mathcal 
-V(x)$ is as defined in~\eqref{eq:PWA:distrubance:set}, then $\mathcal X\ominus\mathcal V(\mathcal X)$ is 
+V(x)$ is point wise polytopic, then $\mathcal X\ominus\mathcal V(\mathcal X)$ is 
 again a polytopic set. This will become more clear in the next section when we describe 
-the computation of the mRPI set~\eqref{eq:definition:mrpi:set:state:dependent}.
+the computation of the MRPI set~\eqref{eq:definition:MRPI:set:state:dependent}.
 %
@@
 %
-\section{Maximal Robust Positive Invariant Sets for State Dependent Disturbance}\label{sec:state:dep:mrpi}
-In this section we describe an iterative algorithm to compute the mRPI 
-set~\eqref{eq:definition:mrpi:set:state:dependent} for a linear system~\eqref{eq:system:equation}.
-For this notice that the set $\mathcal V(x)$ can be represented as the convex hull of its vertices 
-$\mathcal V(x) = \conv\{v_i(x)\}$. Since ${\mathcal{V}}(x)$
+\section{Maximal Robust Positive Invariant Sets for State Dependent Disturbance}\label{sec:state:dep:MRPI}
+In this section we describe an iterative algorithm to compute the MRPI 
+set~\eqref{eq:definition:MRPI:set:state:dependent} for a linear system~\eqref{eq:system:equation} subject to disturbance
+$v\in\mathcal V(x)$ where $\mathcal V(x)$ is defined as in~\eqref{eq:PWA:distrubance:set} with a piecewise affine $H(x)$.
+Notice that the set $\mathcal V(x)$ is pointwise polytopic for finite $x\in\mathcal X_0$ and can hence be represented as the 
+convex hull of its vertices $\mathcal V(x) = \conv\{v_i(x)\}$. Since ${\mathcal{V}}(x)$
 has a piece-wise affine dependence on $x$ the vertices $v_i(x)$ are also piece-wise affine in $x$.
-The set $\mathcal X^\infty$ as defined in~\eqref{eq:definition:mrpi:set:state:dependent} 
+The set $\mathcal X^\infty$ as defined in~\eqref{eq:definition:MRPI:set:state:dependent} 
 requires to satisfy $\Psi x + v\in\mathcal X^\infty$ for all
-$x\in\mathcal X^\infty$ and $v\in\mathcal V(x)$, to compute the mRPI set we start from a given set
-$\mathcal X_0 = \{x:\;\genmat_{0,i}x\leq \genvec_{0,i}\,\forall i\in\mathcal I_0\}$, e.g.
-the system constraints, and 
-\emph{cut off} all points that do not satisfy the invariance condition in one step, two steps, 
-etc. until only points satisfying the conditions are left. I.e. we iteratively introduce 
-constraints that cut off all points for which the successor state can lie outside 
+$x\in\mathcal X^\infty$ and $v\in\mathcal V(x)$. To compute the MRPI set we start from the given 
+state constraint set
+$\mathcal X_0 = \{x:\;\genmat_{0,i}x\leq \genvec_{0,i}\,\forall i\in\mathcal I_0\}$ and 
+\emph{cut off} all points that do not satisfy the invariance condition in $k$ steps, $k\in\mathbb N$. 
+So that all points remaining satisfy the invariance condition~\eqref{eq:definition:MRPI:set:state:dependent}. 
+I.e. we iteratively introduce 
+constraints that separate all points for which the successor state can lie outside 
 $\mathcal X_0$. So for the first iteration we need to enforce the constraint:
@@
 \begin{multline}
-	v_{l,i}^\ast(x)=\begin{split}\max& \genmat_{0,i}\Psi^{l-1}v_j(x)\\ j&\end{split}
-	 = \begin{split}&\max \genmat_{0,i}\Psi^{l-1}v \\ &v\in\mathcal V(x)\end{split}\\
-	= \begin{split}&\max \genmat_{0,i}\tilde v\\ &\tilde v\in \Psi^{l-1}\mathcal V(x) \end{split}
+	v_{l,i}^\ast(x)=\max_j \genmat_{0,i}\Psi^{l-1}v_j(x)\\
+	 = \begin{array}{rl} \max& \genmat_{0,i}\Psi^{l-1}v \\ \text{s.t.}& v\in\mathcal V(x)\end{array}
+	 = \begin{array}{rl} \max& \genmat_{0,i}\tilde v\\ \text{s.t.}& \tilde v\in \Psi^{l-1}\mathcal V(x) \end{array}
 \end{multline}
@@
 %
-\begin{thm}\label{thm:finite:mRPI:set:state:dependable}
+\begin{thm}\label{thm:finite:MRPI:set:state:dependable}
 Let the system constraints be contained in a band $\mathcal X_0\subseteq B=\{x:\Gamma x\leq{\bf{1}}\wedge 
--\Gamma x\leq{\bf{1}}\}$, let the pair $(\Psi,\Gamma)$ be observable and let $\mathcal V(\mathcal X_0)$ be bounded, 
-then $\mathcal X_N\subseteq \mathcal X_{N+1}$ for a finite $N$. Hence the mRPI set $\mathcal X^\infty 
-=\mathcal X_N$ is a finite polytope.
+-\Gamma x\leq{\bf{1}}\}$, let the pair $(\Psi,\Gamma)$ be observable and let $\mathcal V(x)$ be defined by~\eqref{eq:PWA:distrubance:set}
+with a piecewise affine $H$, 
+then $\mathcal X_N\subseteq \mathcal X_{N+1}$ for a finite $N$. Hence the MRPI set $\mathcal X^\infty 
+=\mathcal X_N$ is a polytope.
 \end{thm}
@@
 \begin{proof}
+Notice that with~\eqref{eq:set:iteration:state:dependent:constraints} it is easy to see that in early
+iterations the parametric Pontryagin difference can yield the empty set. The empty set however is
+an admissible polytope, i.e. an admissible MRPI set. For the remainder of this proof we assume
+that the MRPI set is non-empty. For this notice that on any compact set $\mathcal S\subset\mathbb R^n$ we
+have $\bigcup_{s\in\mathcal S}\mathcal V(s)$ is compact.
+
 The proof has two main steps: First we will prove that $\mathcal X_p$ is compact for $p\leq n$
@@
 the set $\mathcal X_{n+1}$ is also bounded. The case that $\tilde N<n$ occurs when $\Gamma$
-has more than rank one. To see that $D_k$ grows exponentially we use that $\mathcal V(\mathcal X_0)$
-is bounded, let $K_1$ denote the smallest ball that contains $\mathcal V(\mathcal X_0)$ and let
+has more than rank one. To see that $D_k$ grows exponentially we use that $\mathcal V(\mathcal X_{n+1})$
+is bounded, let $K_1$ denote the smallest ball that contains $\mathcal V(\mathcal X_{n+1})$ and let
 $\bar\lambda$ denote the magnitude of the largest eigenvalue of $\Psi$. Furthermore, let $K_1$
@@
 \begin{equation}
-D_k = \underbrace{\Psi^{-k}\mathcal X_0}_{(\ast)} \ominus \underbrace{\left(\bigoplus_{i\leq k-1} 
-\Psi^i\mathcal V(\mathcal X_k)\right)}_{(\ast\ast)}.
+D_k = \underbrace{\Psi^{-k}\mathcal X_0}_{(i)} \ominus \underbrace{\left(\bigoplus_{i\leq k-1} 
+\Psi^i\mathcal V(\mathcal X_k)\right)}_{(ii)}.
 \end{equation}
 Since $\Psi$ is asymptotically stable we know that $\bar\lambda<1$ and so we have 
-$\bar\lambda^{-l}K_1\subseteq\Psi^{-l} K_1 \subseteq \Psi^{-l}\mathcal X_0 = (\ast)$
-which implies exponential growth of $D_k$ as long as $(\ast\ast)$ is bounded.
-To bound $(\ast\ast)$ we use $(\ast\ast)\subseteq \oplus_{i\leq k-1} \bar\lambda^i K_2 \subseteq
-\frac{1}{1-\bar\lambda} K_2$. This concludes the proof: We proved that $D_k$ grows exponentially,
+$\bar\lambda^{-l}K_1\subseteq\Psi^{-l} K_1 \subseteq \Psi^{-l}\mathcal X_0 = (i)$
+which implies exponential growth of $D_k$ as long as $(ii)$ is bounded. Recall that we assume
+that the MRPI set is non-empty.
+Hence, to bound $(ii)$ we use $k\geq n+1$ where $(ii)\subseteq \oplus_{i\leq k-1} \bar\lambda^i K_2 \subseteq
+\frac{1}{1-\bar\lambda} K_2$ holds. This concludes the proof: We proved that $D_k$ grows exponentially,
 that it contains an exponentially growing ball. We proved that the subtrahend is bounded inside a ball of
@@
 %
-In this section we discuss the calculation of the mRPI set for a simplified model of the levitating
+In this section we discuss the calculation of the MRPI set for a linearised simplified model of the levitating
 ball system depict in figure~\ref{fig:levitating:ball}. The system dynamics for the ball are given
@@
 with the sampling rate $T_s$. We hence define the system matrix $A = (I+T_s\frac{\partial f}{\partial x}(\hat x,\hat u))$
-and the input matrix $B = T_s \frac{\partial f}{\partial u}(\hat x,\hat u)$. In order to obtain a 
-representation of additive disturbances depending on the state and input like~\eqref{eq:definition:disturbance:set}
-we use the mean-value theorem for vector valued functions:
+and the input matrix $B = T_s \frac{\partial f}{\partial u}(\hat x,\hat u)$. 
+Notice that using a non-autonomous model does not affect our analysis since we analyse the closed loop system
+governed by a linear state feedback controller $u=Kx$. To cope with disturbance optimally we use $K$ 
+being the solution to robust Lyapunov condition $V(x)-V((A+BK)x+Dw)\leq \gamma^2w^Tw$ with $V(x)=x^T P x\geq0$, i.e.
+$x^TPx - ((A+BK)x+Dw)^TP((A+BK)x+Dw)\geq x^T(Q+K^TRK)x -\gamma^2 w^Tw$ for a minimised $\gamma^2$, 
+see e.g.~\cite{Boyd:94}.
+In order to obtain a 
+representation of additive disturbances depending on the state and input like~\eqref{eq:PWA:distrubance:set}
+we use the mean-value theorem for vector valued functions, see e.g.~\cite{Apostol:1974}:
 %
 %
-\begin{thm}\label{thm:mean:value:theorem}
+\begin{thm}[Mean Value Theorem]\label{thm:mean:value:theorem}
 Let $\mathcal X\subset\mathbb R^n$ be open, $g : \mathcal X \rightarrow\mathbb R^m$ continuously differentiable, 
@@
 %
-This implies that for any linearised state $\tilde x$ we obtain the expression
+This implies that for any state $\tilde x$ of linearised we obtain the expression
 $\tilde x^+ = A\tilde x+B\tilde u + H^x\tilde x + H^u \tilde u$, however the computation
-of $H^x$ and $H^u$ requires solving a nonlinear integral. Assume that inside given compact system
-constraints $\mathcal X$ and $\mathcal U$ we had extremal values of $H^x$ and $H^u$, i.e.
+of $H^x$ and $H^u$ requires solving a nonlinear integral. Assume that
+for $x\in\mathcal X$ and $u\in\mathcal U$, where $\mathcal X$ and $\mathcal U$ are compact
+sets, we had extremal values of $H^x$ and $H^u$, i.e.
 $H^x\tilde x+H^u\tilde u\in\conv_k\{H^x_k\tilde x + H^u_k\tilde u\}$ for all $(\tilde x,\tilde u)\in\mathcal X\times \mathcal U$.
@@
 \times\mathcal U$ if we constraint $v\in\mathcal V(\tilde x,\tilde u)$. For general nonlinear systems
-finding the extremal values of $(H^x,H^u)$ can not be done easily, so for the example of the 
-levitating ball we use the parameters: $Ts=30ms, C=1, m=100g, \hat x_1 = 50mm$ and $\mathcal X=\{x:
+finding the extremal values of $(H^x,H^u)$ can not be done easily.
+To obtain values for $(H^x_k,H^u_k)$ we sample $\mathcal X\times\mathcal U$ and evaluate the integral 
+expressions defining $(H^x_k,H^u_k)$ pointwise. For this we use the numerical values for the example of the 
+levitating ball: $Ts=30ms, C=1, m=100g, \hat x_1 = 50mm$ and $\mathcal X=\{x:
 \abs{\hat x_1-x_1}\leq 1mm\wedge \abs{x_2}\leq 105\frac{mm}{s}\}$, $\mathcal U=\{u:\abs{\hat u-u}\leq10mA\}$.
-Using 25 samples of $(H^x,H^u)$ we obtain the invariant set shown in figure~\ref{fig:mrpi:set:levitating:ball},
+Using a total of 25 samples for the computation of $(H^x,H^u)$ we obtain the invariant set shown in figure~\ref{fig:MRPI:set:levitating:ball},
 which is less conservative than using fixed bounds on the nonlinearities as we will see in the next example.
+The algorithm terminates after 3 iterations.
 %
@@
 \caption{The maximal robust positive invariant set for the levitating ball system.}
-\label{fig:mrpi:set:levitating:ball}
+\label{fig:MRPI:set:levitating:ball}
 \end{figure}
@@
 %
-\section{Maximal Robust Positive Invariant Sets for Parametrised Disturbance}\label{sec:mRPI:parametrised}
+\section{Maximal Robust Positive Invariant Sets for Parametrised Disturbance}\label{sec:MRPI:parametrised}
 %
 %
-In this section we describe the computation of the mRPI set for~\eqref{eq:system:equation}
+In this section we describe the computation of the MRPI set for~\eqref{eq:system:equation}
 but using a disturbance set that is parametrised for scaling, i.e. $\mathcal V(\theta) = \{v: Gv\leq(1+\theta){\bf{1}}\} 
@@
 the disturbance set $\mathcal V(\theta)$ with non-uniform scaling of the input constraint set
-$\mathcal U({\bf{\alpha}}) = \{u: Fu\leq\left(I+\text{diag}(\alpha_1,\dots,\alpha_p)\right){\bf{1}}\}$, 
-this can be used to study closed loop systems subject to a given feedback controller.
+$\mathcal U({\bf{\alpha}}) = \{u: Fu\leq\left(I+\text{diag}(\alpha_1,\dots,\alpha_p)\right){\bf{1}}\}$.
+The necessity of uniform scaling of the disturbance constraints is due to a finesse we use to avoid
+solving multiparametric linear programs in every substep of the proposed iteration.
+A representation of the MRPI set of a system parametrised with respect to a scaling parameter allows us
+to study the system's sensitivity to \emph{stronger/weaker} disturbance, the sensitivity to input 
+constraints can be useful to choose particular actuators.
 %
@@
 %
-In the following we describe an algorithm to compute the mRPI set $\mathcal Z^\infty$ contained in 
+In the following we describe an algorithm to compute the MRPI set $\mathcal Z^\infty$ contained in 
 $\mathcal Z = \{(x,\theta):\mathcal F_i x+\mathcal G_i\theta \leq 1,\forall\, i\leq m\}$.
-As in the state dependent case we iteratively introduce constraints \emph{cutting off} points
+As in the state dependent case we iteratively introduce constraints \emph{separating} points
 for which the successor state can lie outside the previous set, i.e. starting from $Z_0 = \mathcal Z$
@@
 \[
-\begin{array}{rl}
-\max&\mathcal F_i \Psi^l v \\ \text{s.t.}&v\in\bar{\mathcal{V}}
-\end{array} = 
-\begin{array}{rl}
-\max&\mathcal F_i \tilde  v \\ \text{s.t.}&\Psi^{-l} \tilde v\in\bar{\mathcal{V}}
-\end{array} = 
-\begin{array}{rl}
-\max&\mathcal F_i v \\ \text{s.t.}& \tilde v\in\Psi^l\bar{\mathcal{V}}
+\small
+\begin{array}{rlcrlcrl}
+\max&\mathcal F_i \Psi^l v &=& \max&\mathcal F_i \tilde  v &=& \max&\mathcal F_i v \\ 
+\text{s.t.}&v\in\bar{\mathcal{V}} & & \text{s.t.}&\Psi^{-l} \tilde v\in\bar{\mathcal{V}} & &
+\text{s.t.}& \tilde v\in\Psi^l\bar{\mathcal{V}}
 \end{array}
@@
 %
-$\bar{\mathcal{V}}=\mathcal V(0)$ for notational convenience. So that for any fixed $\hat\theta>-1$
+where $\bar{\mathcal{V}}=\mathcal V(0)$ for notational convenience. For any fixed $\hat\theta>-1$
 we have the closed form description
@@
 %
-The iteration terminates when $Z_k\subseteq Z_{k+1}$. Like in section~\ref{sec:state:dep:mrpi}
+The iteration terminates when $Z_k\subseteq Z_{k+1}$. As in section~\ref{sec:state:dep:MRPI}
 we will require $\mathcal Z\vert_{\hat\theta}$ to be contained in an observable band, i.e. that 
@@
 pair $(\Psi,\Gamma)$ be observable and let $\mathcal V(0)$ be bounded, then $Z_N\subseteq Z_{N+1}$
-for a finite $N$. Hence the mRPI set $\mathcal Z^\infty = Z_N$ is a finite polyhedron.
+for a finite $N$. Hence the MRPI set $\mathcal Z^\infty = Z_N$ is a finite polyhedron.
 \end{thm}
+\note{You wrote to highlight $\mathcal V(0)$ being bounded was an assumption. It is necessary so I 
+don't know what to do with this.}
 %
 \begin{proof}
-The argumentation in this completely analogue to the one in Lemma~\ref{thm:finite:mRPI:set:state:dependable}.
+The proof is, completely analogue to the proof of Lemma~\ref{thm:finite:MRPI:set:state:dependable}.
 First we argue that for each fixed $\hat\theta$ the set $Z_k\vert_{\hat\theta}$ becomes compact using the same
-observability argument as in Lemma~\ref{thm:finite:mRPI:set:state:dependable}.
+observability argument as in Lemma~\ref{thm:finite:MRPI:set:state:dependable}.
 We then use the representation~\eqref{eq:closed:form:parametrised:iterates} to argue that $D_k$ as
@@
 %
-In this section we compute the mRPI set for the levitating ball exemplary system presented in 
-section~\ref{sec:first:example} as well as for a direct torque fed pendulum to illustrate both
+In this section we compute the MRPI set for the levitating ball example system presented in 
+section~\ref{sec:first:example} as well as for a purely numerical model to illustrate both
 the effectiveness of the afore presented algorithm for state dependent disturbances as well as
-the system analysis tool that is the parametrised mRPI set. First we present the parametrised mRPI
+the system analysis tool that is the parametrised MRPI set. First we present the parametrised MRPI
 set for the levitating ball, notice that in order to obtain comparable results we need to get fixed bounds
-on the effect of nonlinearities on each state, i.e. a constant version 
-of~\eqref{eq:definition:element:wise:constraints:on:nonlinearities}. Using the same constraint set 
+on the effect of nonlinearities on each state, i.e. a fixed set containing the set $\mathcal V(x,u)$ 
+in~\eqref{eq:definition:element:wise:constraints:on:nonlinearities} for all $(x,u)\in\mathcal X\times\mathcal U$. 
+Using the same constraint set 
 $\mathcal X \times \mathcal U$ to determine the maximal and minimal values for nonlinear effects
 we obtain a constant set which is non symmetric around the origin due to nonlinearity. We also introduce
-a scaling parameter $\alpha$ such that $\mathcal U(0)=\mathcal U$. For this setup we obtain the mRPI
+a scaling parameter $\alpha$ such that $\mathcal U(0)=\mathcal U$ for $\alpha=0$. For this setup we obtain the MRPI
 set $\mathcal Z^\infty=\{(x,\theta,\alpha): \Lambda_i^x x + \Lambda_i^\theta \theta + \Lambda_i^\alpha \alpha\leq
@@
 remain unchanged throughout the computation of $\mathcal Z^\infty$ so that $\Lambda^\alpha$ has only non
-positive entries, i.e. increasing $\alpha$ will enlarge the parametrised mRPI set $\mathcal Z^\infty\vert_{\alpha_1}
+positive entries, i.e. increasing $\alpha$ will enlarge the parametrised MRPI set $\mathcal Z^\infty\vert_{\alpha_1}
 \subseteq\mathcal Z^\infty\vert_{\alpha_2}$ for $\alpha_1\leq\alpha_2$.
 
-First we want to compare the mRPI set $\mathcal X^\infty$ obtained with state dependent disturbance 
+First we want to compare the MRPI set $\mathcal X^\infty$ obtained with state dependent disturbance 
 constraints with the parametrised one $\mathcal Z^\infty$. To do this we compute the scaling parameter 
-$\alpha_{\min}$ such that $\mathcal X^\infty\subseteq\mathcal Z^\infty\vert_{(0,\alpha_{\min})}$.
+$\alpha_{\min}$ such that $\mathcal X^\infty\subseteq\mathcal Z^\infty\vert_{(\theta=0,\alpha=\alpha_{\min})}$.
 We can do this by solving $m_\infty$ linear programs
@@
 \Lambda_i^\theta\cdot 0 + \Lambda_i^\alpha \alpha \leq \lambda_i$. Solving this we obtain the 
-minimal value $\alpha_{\min} = 1.7555$ and the mRPI sets shown in Figure~\ref{fig:minimal:scaling:comparison:mRPIs}.
-Caution is advised when interpreting $\alpha>0$, since the system is nonlinear extrapolations bare very
+minimal value $\alpha_{\min} = 1.7555$ and the MRPI sets shown in Figure~\ref{fig:minimal:scaling:comparison:MRPIs}.
+The computation terminates after seven iterations and produces a polyhedron $\mathcal Z^\infty$ supported by $m_\infty=10$
+planes.
+Caution is advised when interpreting $\alpha>0$, since the system is nonlinear extrapolations reveal very
 little insight, the only information we can safely extract is that the current set of inputs $\mathcal U(0)=\mathcal U$ 
-is not large enough to cope with the perturbation set containing given by upper bounds of the nonlinear effects.
+is not large enough to cope with the perturbation set given by upper bounds of the nonlinear effects.
 %
@@
 \end{lpic}
-\caption{Minimal scaling for mRPI set computed for constant disturbance which contains
- mRPI set for piecewise affine disturbances is $\alpha=1.7555$. Note that since the nonlinearities of the system
- dynamics are not symmetrical around the equilibrium the mRPI set with fixed constraints on the perturbation
+\caption{Minimal scaling for MRPI set computed for constant disturbance which contains
+ MRPI set for piecewise affine disturbances is $\alpha=1.7555$. Note that since the nonlinearities of the system
+ dynamics are not symmetrical around the equilibrium the MRPI set with fixed constraints on the disturbance
  is non-symmetric.}
- \label{fig:minimal:scaling:comparison:mRPIs}
+ \label{fig:minimal:scaling:comparison:MRPIs}
 \end{figure}
 
-In the second example we compute the parametrised mRPI set for the system
+In the second example, we compute the parametrised MRPI set for the system
+%
 $$
@@
 \underbrace{\left(\begin{array}{cc} 1 & 1 \\ 1 & -1\end{array}\right)}_B u + 
-\underbrace{\left(\begin{array}{cc} 1 & 2 \\ 2 & 1 \end{array}\right)}_D w
+\underbrace{\left(\begin{array}{cc} 1 & 2 \\ 2 & 1 \end{array}\right)}_D w.
 $$
+%
 We use the constraint sets $\mathcal U(\alpha) = \{u: Fu\leq(I+\text{diag}(\alpha)){\bf{1}} \wedge
@@
 \abs{w_1}\leq 0.1(1+\theta)\wedge \abs{w_2}\leq 0.15(1+\theta)\}$. The constraint matrix $F$ is given by
+%
 $$
@@
 $$
+%
+All constraints were mainly chosen to be illustrative.
 We can now analyse the effect of changing individual constraints on the input by changing $\alpha$ as well as the
@@
 $\mathcal Z(x,\theta,\alpha) = \left\{(x,\theta,\alpha): Kx\in\mathcal U(\alpha)\wedge K_w x\in\mathcal W
-(\theta)\wedge \alpha,\theta>-{\bf{1}}\right\}$, with $K$ and $K_w$ being the solution to the semidefinite program
+(\theta)\wedge \alpha,\theta>-{\bf{1}}\right\}$, with $K$ and $K_w$ being the solution to the aforementioned semidefinite program
 $x^TPx - ((A+BK)x+Dw)^TP((A+BK)x+Dw)\geq x^T(Q+K^TRK)x -\gamma^2 w^Tw$, i.e. $K_w = (\gamma^2-D^TPD)D^TP(A+BK)$.
-We use $Q = \text{diag}(2,1)$ and $R = I$. Using these numerical values we determine the mRPI set 
-$\mathcal Z^\infty$ after 22 iterations, it has 61 facets. Notice that in addition to the sign of 
-the sensitivity of the mRPI set on $\alpha$ we know that since we introduced each facet of $\mathcal Z$
-to depend only on one $\alpha_i$, since the algorithm does not change the elements corresponding to $\alpha$
-and due to orthogonality two facets depending on different elements of $\alpha$ can not be reduced to 
-one facet depending on both. I.e. $\Lambda^\alpha$ has no more than one entry per row. We can therefore 
-compute which $\alpha_i$ will change the mRPI set the most. This can be done by element wise calculating
+We use $Q = \text{diag}(2,1)$ and $R = I$. Using these numerical values we determine the MRPI set 
+$\mathcal Z^\infty$. After 22 iterations the algorithm terminates producing a total of 61 facets. 
+Notice that we not only know the sign of the elements of $\mathcal H$, but we also know that each facet of $\mathcal Z(x,\theta,\alpha)$
+depends at most on one $\alpha_i$, the algorithm does not affect the elements corresponding on $\alpha$ and reduction
+methods can not reduce rows depending on two individual variables, therefore we know that $\Lambda^\alpha$ will have at 
+most one nonzero entry per row. We can therefore 
+compute which $\alpha_i$ will change the MRPI set the most. This can be done by element wise calculating
 $$
@@
 i.e. the third input constraint.
-Analogue to the first example we might want to know how much disturbance the closed loop system can 
-take such that a given set is contained in the mRPI set $\mathcal C\subseteq\mathcal Z^\infty\vert_{(\theta,0)}$.
+Analogous to the first example we might want to know how much disturbance the closed loop system can 
+take such that a given set is contained in the MRPI set $\mathcal C\subseteq\mathcal Z^\infty\vert_{(\theta,0)}$.
 We used the non-positivity of $\mathcal H$ to argue the non-positivity of $\Lambda^\alpha$, however we
@@
 $$
-The extremal values for which $\mathcal C$ is contained in the mRPI set are given by
+The extremal values for which $\mathcal C$ is contained in the MRPI set are given by
 the smallest $\theta_{\max}$ satisfying $\gamma_i+\Lambda^{1,\alpha}_i\hat\alpha+
@@
 The numerical values for the example are given by $[\theta_{\min},\theta_{\max}]=[-0.9999,6.2582]$.
-A two and three dimensional illustration of the parametrised mRPI set is given in Figure~\ref{fig:two:dim:example}
+A two and three dimensional illustration of the parametrised MRPI set is given in Figure~\ref{fig:two:dim:example}
 and~\ref{fig:three:dim:example} respectively.
@@
 \includegraphics[width=\columnwidth]{twoDimensional}
-\caption{The extremal mRPI sets $\mathcal Z^\infty\vert_{({\bf{0}},\theta_{min})}$ and $\mathcal Z^\infty
+\caption{The extremal MRPI sets $\mathcal Z^\infty\vert_{({\bf{0}},\theta_{min})}$ and $\mathcal Z^\infty
 \vert_{({\bf{0}},\theta_{\max})}$ containing the unit box.}
@@
 \includegraphics[width=\columnwidth]{threeDimensional}
-\caption{The parametrised mRPI set for $\alpha={\bf{0}}$. Containing the unit box in the 
+\caption{The parametrised MRPI set for $\alpha={\bf{0}}$. Containing the unit box in the 
 interior between $\theta_{\min}$ and $\theta_{\max}$.}
@@
 %
-In this paper we discussed extensions to existing computational methods to determine mRPI sets
+In this paper we discussed extensions to existing computational methods to determine MRPI sets
 for linear systems subject to additive disturbance in two cases. The case of state dependent case
-which can be applied to determine approximations to mRPI sets for linearised nonlinear systems as was shown
-for the example of a levitating ball system. We also introduced the computation of mRPI sets using 
+which can be applied to determine approximations to MRPI sets for linearised nonlinear systems as was shown
+for the example of a levitating ball system. We also introduced the computation of MRPI sets using 
 scaling parameters which allows various system analyses using uniform scaling for the disturbance sets
 and non-uniform scaling for the input constraints. The effectiveness of state dependent disturbance
-sets was demonstrated by comparing the two mRPI methods.
+sets was demonstrated by comparing the two MRPI methods.
 \bibliographystyle{IEEEtran}

### 2015-03-17 draft.tex
Updated title, abstract and introduction

@@
 \usepackage{lpic}
+\usepackage{overpic}
 % \usepackage{blkarray}
@@
 \begin{document}
-  \title{Advances in Robust Positive Invariant Set Computation}
+%  \title{Advances in Robust Positively Invariant Set Computation}
+  \title{Robust positively invariant sets for state dependent and scaled disturbances}
 
@@
 \begin{abstract} 
-In this paper we introduce methods of deriving and computing maximal positive robust invariant
-sets for linear discrete time systems with additive uncertainty. We consider two different sets of
-uncertainties, state dependent uncertainty which allows us to handle multiplicative as well as
-linearised systems easily, and scaled sets of uncertainty. We provide the framework for the analytic
-treatment of both and illustrate their benefits in two numerical examples.
+  This paper introduces methods of deriving and computing maximal robust positively invariant sets for linear discrete time systems with additive model uncertainty.
+Two types of uncertainty are considered: state dependent uncertainty, which handles multiplicative parametric model uncertainty as well as linearisation errors for nonlinear systems, and scaled sets of uncertainty.
+We provide a framework for analysing both types of uncertainty with illustrative examples.
 \end{abstract}
@@
 \section{Introduction}
-Ever since the introduction of disturbance invariant sets in~\cite{Glover:1971}, the analytic
-properties of these sets have been fairly well studied, see~\cite{blanchini:2007}. Here by disturbance
-invariant sets we mean a subset of the state constraint set $\mathscr X\subseteq\mathcal X_0\subseteq\mathbb R^n$ 
-containing initial conditions for the perturbed linear system
+The analytic properties of disturbance invariant sets have been widely studied (see e.g.~\cite{blanchini:2007}) since their introduction in~\cite{Glover:1971}.
+A disturbance invariant set $\mathscr X$ is a subset of the state constraint set $\mathcal X_0\subseteq\mathbb R^n$ that contains states $x$ of the perturbed linear system
 \begin{equation}\label{eq:system:equation}
-	x^+ = \Psi x + v,
+	x^+ = \Psi x + v
 \end{equation}
-where $\Psi$ is Hurwitz, $x,x^+\in\mathcal X_0$ the state and the successor state, and where 
-$v\in\mathscr V$ denotes the perturbation, such that the successor state is contained in the 
-disturbance invariant set $x^+\in\mathscr X$ for all possible realisations of the 
-perturbation $v\in\mathscr V$. That is summarised in the implicit definition
+(where $\Psi$ is Hurwitz, $x,x^+\in\mathcal X_0$, and 
+$v\in\mathscr V$) such that the successor state $x^+$ is contained in the 
+disturbance invariant set for all possible realisations of the 
+unknown disturbance $v$. This is summarised in the implicit definition
 \begin{equation}\label{eq:definition:MRPI:set:state:dependent}
@@
 \end{equation}
-These sets are known as robust positive invariant (RPI) sets. In many applications we are interested in the largest such
-set $\mathcal X^\infty$, i.e. the set containing all other RPI sets $\mathscr X\subseteq\mathcal X^\infty$,
-this set is called the maximal robust positive invariant (MRPI) set. These sets are used e.g. as terminal regions in 
-robust model predictive control. Even though analytical properties
-of these sets were derived early after their introduction, it took more than two decades until algorithms
-were introduced to numerically compute MRPI sets~\cite{DeSantis:1994,Kolmanovsky:1995,Blanchini:1994}. 
-\note{You commented 'check', I didn't know what that meant.}
+Thus an disturbance invariant set is a type of robust positive invariant (RPI) set. In many applications we are interested in the largest such
+set, denoted $\mathcal X^\infty$, which is given by the union of all RPI sets $\mathscr X\subseteq\mathcal X^\infty$.
+This set is known as the maximal robust positive invariant (MRPI) set and has been used extensively, for example to define terminal regions in
+robust model predictive control. Although analytical properties
+of these sets were derived soon after their introduction, algorithms for numerically computing MRPI sets were introduced much later~\cite{DeSantis:1994,Kolmanovsky:1995,Blanchini:1994}. 
+%\note{You commented 'check', I didn't know what that meant.}
 Earlier algorithms
@@
 %
-In the afore mentioned algorithms the perturbation was considered to belong to a fixed compact set, in this paper
-we consider sets that vary with parameters. First we consider the set of disturbances to be state dependent, e.g.
+However for the case of disturbances that belong to a fixed set $\mathscr V$, methods of computing $\mathcal X^\infty$ are well established~\cite{blanchini:2007}.
+
+This paper considers
+sets of disturbances that depend on parameters. First we consider disturbance sets that are state dependent, of the form
 \begin{equation}\label{eq:PWA:distrubance:set}
@@
 \end{equation}
-where $H(x)$ is a piecewise affine function. This means that in the first part of the paper
-we discuss the computation of $\mathcal X^\infty$ for the case where $\mathscr V=\mathcal V(x)$.
-The case where the disturbance depends on the state has been studied analytically before but not 
-extensively, see~\cite{Kuntsevich:1995}. These kind of disturbance constraints can be used to
-account for linearisation errors, as will be shown in section~\ref{sec:first:example}, but can also
-be used to treat multiplicative uncertainty.
+where $H(x)$ is a piecewise affine function. For the case that $\mathscr V=\mathcal V(x)$ we
+provide conditions for convexity and finite determination of $\mathcal X^\infty$ and discuss computation of $\mathcal X^\infty$.
+The case of disturbances depending on states (or control inputs) is considered in~\cite{Kuntsevich:1995,rakovic06}, but the convexity analysis of this paper is novel.
+State dependent disturbance constraints can
+account for linearisation errors, as shown in section~\ref{sec:first:example}, as well as more general multiplicative parametric model uncertainty.
 
-The second case we consider is the case of a scaled set of disturbance, i.e.
+The second case considered is that of scaled disturbance sets of the form
 \begin{equation}
@@
 \end{equation}
-with $\theta>-1$. To distinguish the resulting sets from regular MRPI sets we use $\mathcal Z^\infty$
-to emphasise that $\mathcal Z^\infty$ itself is not an MRPI set, however by fixing $\theta=\hat\theta$ the
-set $\mathcal Z^\infty\vert_{\hat\theta}$ is an MRPI set. To our best knowledge, this setup has not been 
-presented in the literature. This type of disturbance constraints can be used to study the sensitivity of
+for scalar $\theta>-1$. For $\mathscr V = \mathcal V(\theta)$ we compute sets $\mathcal Z^\infty$ in $(x\times\theta)$-space with the property that 
+% To distinguish the resulting sets from regular MRPI sets we use $\mathcal Z^\infty$
+% to emphasise that $\mathcal Z^\infty$ 
+the intersection, $\mathcal Z^\infty\vert_{\hat\theta}$, with the subspace on which $\theta=\hat\theta$ for given $\hat\theta$ is an MRPI set. To our best knowledge, this setup has not been 
+considered in the literature. This type of disturbance constraint can be used to study the sensitivity of
 the MRPI set to changes in the disturbance \emph{strength}.
 
-The remainder of this paper is structured: In section~\ref{sec:parametrically:convex:set:operations} we
-introduce the notion of \emph{parametric convexity} and of its general implications, this is sufficient 
+The paper is structured as follows: In section~\ref{sec:parametrically:convex:set:operations} we
+introduce the notion of \emph{parametric convexity} and discuss its implications, in particular as a condition 
 for the convexity of the MRPI set. The algorithm to compute the MRPI set for state dependent disturbance
-constraints is presented in section~\ref{sec:state:dep:MRPI}, we also prove its finite determinability.
-In section~\ref{sec:first:example} we demonstrate the algorithm using a numerical exemplary system, a
-levitating ball setup. The case of scaled disturbance constraints is discussed in section~\ref{sec:MRPI:parametrised}
+constraints is presented in section~\ref{sec:state:dep:MRPI}, and we also prove its finite determinability.
+In section~\ref{sec:first:example} the algorithm is illustrated using an exemplar system, a magnetically levitated ball.
+The case of scaled disturbance constraints is discussed in section~\ref{sec:MRPI:parametrised}
 where the algorithm for the parametrised MRPI set as well as the proof for its finite determinability
 are also presented. Section~\ref{sec:second:example} illustrates the use of parametrised MRPI sets using
-again the levitating ball example and illustrating some of possible robustness analyses of the parametrised
+again the levitating ball example and illustrating a robustness analyses of the parametrised
 MRPI sets with a numerical example. The paper is concluded in section~\ref{sec:conclusions}.
 
-In the remainder of this paper we use the notion of a polyhedra for sets that can be represented as
-the intersection of a finite number of halfspaces, polytopic sets for bounded polyhedral.
-By ${\bf{1}}$ we denote the column vector of ones in appropriate dimension, $\wedge$ denotes the logical and. 
+Throughout this paper we refer to sets that can be represented as intersections of finite numbers of half spaces as polyhedra, and to bounded polyhedra as polytopic sets.
+%By ${\bf{1}}$ we denote 
+Also ${\bf{1}}$ denotes the column vector of ones in appropriate dimensions, and $\wedge$ is the logical AND operator. 
 %
@@
 \centering
-\begin{lpic}{levitatingBall}
-\lbl[tr]{25,3; $m g$}
-\lbl[br]{25,25; $c\frac{i^2}{x^2}$}
-\lbl[bl]{49,17; $y$}
-\lbl[bl]{56,55; $i$}
-\end{lpic}
+\begin{overpic}[scale=0.75]{levitatingBall}
+\put(30,5){$m g$}
+\put(30,41){$c\frac{i^2}{x^2}$}
+\put(78,28){$y$}
+\put(90,89){$i$}
+\end{overpic}
+% \begin{lpic}[scale=0.5]{levitatingBall}
+% \lbl[tr]{25,3; $m g$}
+% \lbl[br]{25,25; $c\frac{i^2}{x^2}$}
+% \lbl[bl]{49,17; $y$}
+% \lbl[bl]{56,55; $i$}
+% \end{lpic}
+\vspace{-2mm}
 \caption{Levitating ball system.}
@@
 \end{thm}
-\note{You wrote to highlight $\mathcal V(0)$ being bounded was an assumption. It is necessary so I 
-don't know what to do with this.}
+%\note{You wrote to highlight $\mathcal V(0)$ being bounded was an assumption. It is necessary so I don't know what to do with this.}
 %
 \begin{proof}
-The proof is, completely analogue to the proof of Lemma~\ref{thm:finite:MRPI:set:state:dependable}.
+The proof is similar to that of Lemma~\ref{thm:finite:MRPI:set:state:dependable}.
 First we argue that for each fixed $\hat\theta$ the set $Z_k\vert_{\hat\theta}$ becomes compact using the same
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{twoDimensional}
+\centerline{\includegraphics[scale=0.6]{twoDimensional}}
 \caption{The extremal MRPI sets $\mathcal Z^\infty\vert_{({\bf{0}},\theta_{min})}$ and $\mathcal Z^\infty
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{threeDimensional}
+\centerline{\includegraphics[scale=0.6]{threeDimensional}}
 \caption{The parametrised MRPI set for $\alpha={\bf{0}}$. Containing the unit box in the 

### 2015-03-19 draft.tex
test
Nothing really.

@@
 \begin{abstract} 
-  This paper introduces methods of deriving and computing maximal robust positively invariant sets for linear discrete time systems with additive model uncertainty.
-Two types of uncertainty are considered: state dependent uncertainty, which handles multiplicative parametric model uncertainty as well as linearisation errors for nonlinear systems, and scaled sets of uncertainty.
-We provide a framework for analysing both types of uncertainty with illustrative examples.
+  This paper introduces methods of deriving and computing maximal robust positively invariant sets 
+  for linear discrete time systems with additive model uncertainty. Two types of uncertainty are 
+  considered: state dependent uncertainty, which handles multiplicative parametric model uncertainty 
+  as well as linearisation errors for nonlinear systems, and scaled sets of uncertainty. We provide 
+  a framework for analysing both types of uncertainty with illustrative examples.
 \end{abstract}
@@
 \section{Introduction}
-The analytic properties of disturbance invariant sets have been widely studied (see e.g.~\cite{blanchini:2007}) since their introduction in~\cite{Glover:1971}.
-A disturbance invariant set $\mathscr X$ is a subset of the state constraint set $\mathcal X_0\subseteq\mathbb R^n$ that contains states $x$ of the perturbed linear system
+The analytic properties of disturbance invariant sets have been widely studied (see e.g.~\cite{blanchini:2007}) 
+since their introduction in~\cite{Glover:1971}. A disturbance invariant set $\mathscr X$ is a subset of the 
+state constraint set $\mathcal X_0\subseteq\mathbb R^n$ that contains states $x$ of the perturbed linear system
 \begin{equation}\label{eq:system:equation}
@@
 \end{equation}
-Thus an disturbance invariant set is a type of robust positive invariant (RPI) set. In many applications we are interested in the largest such
-set, denoted $\mathcal X^\infty$, which is given by the union of all RPI sets $\mathscr X\subseteq\mathcal X^\infty$.
-This set is known as the maximal robust positive invariant (MRPI) set and has been used extensively, for example to define terminal regions in
+Thus an disturbance invariant set is a type of robust positive invariant (RPI) set. 
+In many applications we are interested in the largest such set, denoted $\mathcal X^\infty$, which is given 
+by the union of all RPI sets $\mathscr X\subseteq\mathcal X^\infty$. This set is known as the maximal robust 
+positive invariant (MRPI) set and has been used extensively, for example to define terminal regions in 
 robust model predictive control. Although analytical properties
-of these sets were derived soon after their introduction, algorithms for numerically computing MRPI sets were introduced much later~\cite{DeSantis:1994,Kolmanovsky:1995,Blanchini:1994}. 
+of these sets were derived soon after their introduction, algorithms for numerically computing MRPI sets 
+were introduced much later~\cite{DeSantis:1994,Kolmanovsky:1995,Blanchini:1994}. 
 %\note{You commented 'check', I didn't know what that meant.}
-Earlier algorithms
-did not guarantee finite determinability of $\mathcal X^\infty$, see e.g.~\cite{Blanchini:1990}, or 
-did not guarantee to produce the maximal RPI set, e.g.~\cite{Blanchini:1991}. 
+Earlier algorithms did not guarantee finite determinability of $\mathcal X^\infty$, see e.g.~\cite{Blanchini:1990}, 
+or did not guarantee to produce the maximal RPI set, e.g.~\cite{Blanchini:1991}. 
 %
-However for the case of disturbances that belong to a fixed set $\mathscr V$, methods of computing $\mathcal X^\infty$ are well established~\cite{blanchini:2007}.
+However for the case of disturbances that belong to a fixed set $\mathscr V$, methods of computing 
+$\mathcal X^\infty$ are well established~\cite{blanchini:2007}.
 
-This paper considers
-sets of disturbances that depend on parameters. First we consider disturbance sets that are state dependent, of the form
+This paper considers sets of disturbances that depend on parameters. First we consider disturbance 
+sets that are state dependent, of the form
 \begin{equation}\label{eq:PWA:distrubance:set}
@@
 where $H(x)$ is a piecewise affine function. For the case that $\mathscr V=\mathcal V(x)$ we
-provide conditions for convexity and finite determination of $\mathcal X^\infty$ and discuss computation of $\mathcal X^\infty$.
-The case of disturbances depending on states (or control inputs) is considered in~\cite{Kuntsevich:1995,rakovic06}, but the convexity analysis of this paper is novel.
-State dependent disturbance constraints can
-account for linearisation errors, as shown in section~\ref{sec:first:example}, as well as more general multiplicative parametric model uncertainty.
+provide conditions for convexity and finite determination of $\mathcal X^\infty$ and discuss 
+computation of $\mathcal X^\infty$. The case of disturbances depending on states (or control inputs) 
+is considered in~\cite{Kuntsevich:1995,rakovic06}, but the convexity analysis of this paper is novel. 
+State dependent disturbance constraints can account for linearisation errors, as shown in section~\ref{sec:first:example}, 
+as well as more general multiplicative parametric model uncertainty.
 
@@
 \end{equation}
-for scalar $\theta>-1$. For $\mathscr V = \mathcal V(\theta)$ we compute sets $\mathcal Z^\infty$ in $(x\times\theta)$-space with the property that 
+for scalar $\theta>-1$. For $\mathscr V = \mathcal V(\theta)$ we compute sets $\mathcal Z^\infty$ in 
+$(x\times\theta)$-space with the property that 
 % To distinguish the resulting sets from regular MRPI sets we use $\mathcal Z^\infty$
 % to emphasise that $\mathcal Z^\infty$ 
-the intersection, $\mathcal Z^\infty\vert_{\hat\theta}$, with the subspace on which $\theta=\hat\theta$ for given $\hat\theta$ is an MRPI set. To our best knowledge, this setup has not been 
+the intersection, $\mathcal Z^\infty\vert_{\hat\theta}$, with the subspace on which $\theta=\hat\theta$ 
+for given $\hat\theta$ is an MRPI set. To our best knowledge, this setup has not been 
 considered in the literature. This type of disturbance constraint can be used to study the sensitivity of
@@
 constraints is presented in section~\ref{sec:state:dep:MRPI}, and we also prove its finite determinability.
-In section~\ref{sec:first:example} the algorithm is illustrated using an exemplar system, a magnetically levitated ball.
-The case of scaled disturbance constraints is discussed in section~\ref{sec:MRPI:parametrised}
+In section~\ref{sec:first:example} the algorithm is illustrated using an exemplar system, a magnetically 
+levitated ball. The case of scaled disturbance constraints is discussed in section~\ref{sec:MRPI:parametrised}
 where the algorithm for the parametrised MRPI set as well as the proof for its finite determinability
@@
 
-Throughout this paper we refer to sets that can be represented as intersections of finite numbers of half spaces as polyhedra, and to bounded polyhedra as polytopic sets.
-%By ${\bf{1}}$ we denote 
-Also ${\bf{1}}$ denotes the column vector of ones in appropriate dimensions, and $\wedge$ is the logical AND operator. 
+Throughout this paper we refer to sets that can be represented as intersections of finite numbers of half 
+spaces as polyhedra, and to bounded polyhedra as polytopic sets. ${\bf{1}}$ denotes the column vector of 
+ones in appropriate dimensions, and $\wedge$ is the logical AND operator. 
 %

### 2015-03-19 draft.tex
edited sections II and II - please check proof of Lemma 3.1 carefully!

--- 2015-03-17 draft.tex
@@
 \section{Introduction}
-The analytic properties of disturbance invariant sets have been widely studied (see e.g.~\cite{blanchini:2007}) since their introduction in~\cite{Glover:1971}.
-A disturbance invariant set $\mathscr X$ is a subset of the state constraint set $\mathcal X_0\subseteq\mathbb R^n$ that contains states $x$ of the perturbed linear system
+The analytic properties of disturbance invariant sets have been widely
+studied (e.g.~\cite{blanchini:2007}) 
+since their introduction in~\cite{Glover:1971,bertsekas71}. A disturbance invariant set $\mathscr X$ is a subset of the 
+state constraint set $\mathcal X_0\subseteq\mathbb R^n$ containing states $x$ of the perturbed linear system
 \begin{equation}\label{eq:system:equation}
@@
 \end{equation}
-Thus an disturbance invariant set is a type of robust positive invariant (RPI) set. In many applications we are interested in the largest such
-set, denoted $\mathcal X^\infty$, which is given by the union of all RPI sets $\mathscr X\subseteq\mathcal X^\infty$.
-This set is known as the maximal robust positive invariant (MRPI) set and has been used extensively, for example to define terminal regions in
-robust model predictive control. Although analytical properties
-of these sets were derived soon after their introduction, algorithms for numerically computing MRPI sets were introduced much later~\cite{DeSantis:1994,Kolmanovsky:1995,Blanchini:1994}. 
+Thus a disturbance invariant set is a type of robust positively invariant (RPI) set. 
+In many applications we are interested in the largest such set, denoted $\mathcal X^\infty$, which is given 
+by the union of all RPI sets $\mathscr X\subseteq\mathcal X^\infty$. This set is known as the maximal robust 
+positively invariant (MRPI) set and has been used extensively, for example, to define terminal regions in 
+robust model predictive control~\cite{mayne:2000}. Although analytical properties
+of these sets were derived soon after their introduction, algorithms for numerically computing MRPI sets 
+were introduced much later~\cite{Blanchini:1994,DeSantis:1994,Kolmanovsky:1998}. 
 %\note{You commented 'check', I didn't know what that meant.}
-Earlier algorithms
-did not guarantee finite determinability of $\mathcal X^\infty$, see e.g.~\cite{Blanchini:1990}, or 
-did not guarantee to produce the maximal RPI set, e.g.~\cite{Blanchini:1991}. 
+Earlier algorithms did not guarantee finite determinability of $\mathcal X^\infty$, see e.g.~\cite{Blanchini:1990}, 
+or did not guarantee to produce the maximal RPI set, e.g.~\cite{Blanchini:1991}. 
 %
-However for the case of disturbances that belong to a fixed set $\mathscr V$, methods of computing $\mathcal X^\infty$ are well established~\cite{blanchini:2007}.
+However for the case of disturbances belonging to a fixed set $\mathscr V$, methods of computing 
+$\mathcal X^\infty$ are well established~\cite{blanchini:2007}.
 
-This paper considers
-sets of disturbances that depend on parameters. First we consider disturbance sets that are state dependent, of the form
+This paper considers sets of disturbances that depend on
+parameters. First we consider state-dependent sets,
 \begin{equation}\label{eq:PWA:distrubance:set}
@@
 \end{equation}
-where $H(x)$ is a piecewise affine function. For the case that $\mathscr V=\mathcal V(x)$ we
-provide conditions for convexity and finite determination of $\mathcal X^\infty$ and discuss computation of $\mathcal X^\infty$.
-The case of disturbances depending on states (or control inputs) is considered in~\cite{Kuntsevich:1995,rakovic06}, but the convexity analysis of this paper is novel.
-State dependent disturbance constraints can
-account for linearisation errors, as shown in section~\ref{sec:first:example}, as well as more general multiplicative parametric model uncertainty.
+where $G$ is a real matrix,
+%$G\in\mathbb R^{n_G\times n_v}$, 
+$H(x)$ is a piecewise affine function, and the inequality applies elementwise. For the case that $\mathscr V=\mathcal V(x)$ we
+provide conditions for convexity and finite determination of $\mathcal X^\infty$ and discuss 
+computation of $\mathcal X^\infty$. The case of disturbances depending on states (or control inputs) 
+is considered in~\cite{Kuntsevich:1995,rakovic06} but the convexity
+analysis of this paper and the associated computational approach are novel. 
+State dependent disturbance constraints can account for linearisation errors, as shown in section~\ref{sec:first:example}, 
+as well as more general multiplicative parametric model uncertainty.
 
@@
 
-The paper is structured as follows: In section~\ref{sec:parametrically:convex:set:operations} we
-introduce the notion of \emph{parametric convexity} and discuss its implications, in particular as a condition 
-for the convexity of the MRPI set. The algorithm to compute the MRPI set for state dependent disturbance
-constraints is presented in section~\ref{sec:state:dep:MRPI}, and we also prove its finite determinability.
-In section~\ref{sec:first:example} the algorithm is illustrated using an exemplar system, a magnetically levitated ball.
-The case of scaled disturbance constraints is discussed in section~\ref{sec:MRPI:parametrised}
-where the algorithm for the parametrised MRPI set as well as the proof for its finite determinability
-are also presented. Section~\ref{sec:second:example} illustrates the use of parametrised MRPI sets using
-again the levitating ball example and illustrating a robustness analyses of the parametrised
-MRPI sets with a numerical example. The paper is concluded in section~\ref{sec:conclusions}.
+The structure of the paper is as follows: We introduce the notion of \emph{parametric convexity} In
+Section~\ref{sec:parametrically:convex:set:operations} and discuss its implications, in particular as a condition 
+for convexity of the MRPI set. The algorithm to compute the MRPI set for state dependent disturbance
+constraints and its finite determinability are discussed in Section~\ref{sec:state:dep:MRPI}.
+Section~\ref{sec:first:example} illustrates the algorithm using the example of a magnetically 
+levitated ball. The case of scaled disturbance constraints is discussed in Section~\ref{sec:MRPI:parametrised},
+which gives the algorithm for computing the parametrised MRPI set and
+proves its finite determinability. Section~\ref{sec:second:example} illustrates the use of
+parametrised MRPI sets using the levitating ball example, and illustrates a robustness analysis of the parametrised
+MRPI sets with a numerical example. Section~\ref{sec:conclusions}
+provides conclusions.
 
 Throughout this paper we refer to sets that can be represented as intersections of finite numbers of half spaces as polyhedra, and to bounded polyhedra as polytopic sets.
-%By ${\bf{1}}$ we denote 
 Also ${\bf{1}}$ denotes the column vector of ones in appropriate dimensions, and $\wedge$ is the logical AND operator.
+
 %
@@
 \section{Parametrically convex set operations}\label{sec:parametrically:convex:set:operations}
-In this section we discuss sets that depend on a state-like parameter (so called point-to-set maps, 
-see~\cite{Hogan:1973}), and extend the existing set algebra~\cite{blanchini:2007} to 
+This section discusses sets that depend on a state-like parameter (so called point-to-set maps, 
+see~\cite{Hogan:1973}), and extends the existing set algebra~\cite{blanchini:2007} to 
 accommodate such sets. We present the general case first, then derive the computation of
@@
     \begin{defn}[Parametric Convexity]\label{def:parametric:convexity}
-      Let $X\subseteq\mathbb R^n, Y\subseteq\mathbb R^m$, let $\mathcal P(Y)$ denote the power set of $Y$ 
+      Let $X\subseteq\mathbb R^n, Y\subseteq\mathbb R^m$, let $\mathcal P(Y)$ denote the power set of $Y$, 
       and $T:X\rightarrow \mathcal P(Y)$, $X\ni s\mapsto T(s)\subset Y$ be a 
@@
 %
-    In the following we will need to be able to compute differences of sets
-    analogous to the Pontryagin difference in~\cite{Kolmanovsky:1998} but using parametrised 
-    sets, this is defined as follows:
+The difference of sets can be defined for parametrised sets analogously to the Pontryagin difference~\cite{Kolmanovsky:1998} as follows:
 %
@@
 %
-    Notice that for constant maps $T$
-    definition~\eqref{eq:definition:parametric:pontryagin:difference} is equivalent to the 
-    well known Pontryagin difference.
-    For parametric Pontryagin differences of convex sets and parametrically convex maps we have the following result.
+    Notice that, for a constant map $T$, the definition~\eqref{eq:definition:parametric:pontryagin:difference} is equivalent to the 
+    well-known Pontryagin difference.
+    For the parametric Pontryagin difference of a convex set and a parametrically convex map we have the following result.
 %
@@
       by definition of the parametric Pontryagin difference, we have
-      \begin{equation}
+\[%      \begin{equation}
         \{z_i\} \oplus T(z_i) \subseteq S,\; i=1,2.
-      \end{equation}
+\]%      \end{equation}
       To see that $ Z$ is convex we show that line segments between
@@
 %
-  Consider a point-to-set map defined by~\eqref{eq:PWA:distrubance:set}
-    where, for now, $H$ is elementwise convex in $x\in \mathscr X\subseteq\mathbb R^n$, so that 
-    $H_i(\lambda x_1+(1-\lambda)x_2)\leq \lambda H_i(x_1)+(1-\lambda)H_i(x_2)$ for 
-    $\lambda\in[0,1]$ and $x_1, x_2\in X$.  For such sets we have the following result:
+  % Consider a point-to-set map~\eqref{eq:PWA:distrubance:set},
+  %   where $H$ is elementwise convex in $x\in \mathcal X\subset \mathbb R^n$, with elements $H_i(x)$ satisfying
+  %   $H_i(\lambda x_1+(1-\lambda)x_2)\leq \lambda H_i(x_1)+(1-\lambda)H_i(x_2)$, for all    $\lambda\in[0,1]$, and $x_1, x_2\in\mathcal X$.  For such sets we have the result:
+%A family of parametrically convex sets is defined as follows.
     \begin{thm}\label{thm:convex:parametric:set}
-      The point-to-set map $\mathcal V (x)$ defined in~\eqref{eq:PWA:distrubance:set} is parametrically 
-      convex for all $x\in X.$
+      The point-to-set map $\mathcal V (x)$ defined by~\eqref{eq:PWA:distrubance:set} is parametrically 
+      convex for all $x\in \mathcal X$ if $H(x)$ is elementwise convex in $x\in \mathcal X\subset \mathbb R^n$ (i.e.~if each element $H_i(x)$ of $H(x)$ satisfies
+    $H_i(\lambda x_1+(1-\lambda)x_2)\leq \lambda H_i(x_1)+(1-\lambda)H_i(x_2)$ for all    $\lambda\in[0,1]$ and $x_1, x_2\in\mathcal X$).
     \end{thm}
+    % \begin{thm}\label{thm:convex:parametric:set}
+    %   The point-to-set map $\mathcal V (x)$ defined by~\eqref{eq:PWA:distrubance:set} for a function $H(x)$ that is elementwise convex in $x\in \mathcal X\subset \mathbb R^n$ (i.e.~each element $H_i(x)$ of $H(x)$ satisfies
+    % $H_i(\lambda x_1+(1-\lambda)x_2)\leq \lambda H_i(x_1)+(1-\lambda)H_i(x_2)$ for all    $\lambda\in[0,1]$ and $x_1, x_2\in\mathcal X$) is parametrically 
+    %   convex for all $x\in \mathcal X$.
+    % \end{thm}
 %
@@
       To show that $\mathcal V(\lambda x_1 + (1-\lambda)x_2)\subseteq 
-      \lambda\mathcal V(x_1) \oplus(1-\lambda)\mathcal V(x_2)$ for all $\lambda \in [0,1]$ we note that
+      \lambda\mathcal V(x_1) \oplus(1-\lambda)\mathcal V(x_2)$ for all $\lambda \in [0,1]$ and $x_1, x_2\in\mathcal X$ we note that
         \begin{align*}
@@
 %
-\def\genmat{\Xi} \def\genvec{\xi}Lemmas~\ref{thm:convexity:of:pontryagin:difference} 
-and~\ref{thm:convex:parametric:set} imply that the parametric Pontryagin difference between a convex set $\mathcal X$ and 
-the point-to-set map $\mathcal V(x)$, i.e. $\mathcal X\ominus \mathcal V(\mathcal X)$, is a convex set.
-Furthermore, we will see that if $\mathcal X$ is polyhedral and $\mathcal 
-V(x)$ is point wise polytopic, then $\mathcal X\ominus\mathcal V(\mathcal X)$ is 
-again a polytopic set. This will become more clear in the next section when we describe 
-the computation of the MRPI set~\eqref{eq:definition:MRPI:set:state:dependent}.
+\def\genmat{\Xi} \def\genvec{\xi}
+% Lemmas~\ref{thm:convexity:of:pontryagin:difference} 
+% and~\ref{thm:convex:parametric:set} imply that the parametric Pontryagin difference between a convex set $\mathcal X$ and 
+% the point-to-set map $\mathcal V(x)$, i.e. $\mathcal X\ominus \mathcal V(\mathcal X)$, is a convex set.
+% Furthermore, we will see that if $\mathcal X$ is polytopic and $\mathcal 
+% V(x)$ is pointwise polytopic, then $\mathcal X\ominus\mathcal V(\mathcal X)$ is 
+% again a polytopic set. This will become more clear in the next section when we describe 
+% the computation of the MRPI set~\eqref{eq:definition:MRPI:set:state:dependent}.
+%
+Lemmas~\ref{thm:convexity:of:pontryagin:difference} 
+and~\ref{thm:convex:parametric:set} imply that, if $\mathcal V(x)$ is defined by \eqref{eq:PWA:distrubance:set} in terms of an elementwise convex function $H(x)$, then the parametric Pontryagin difference $\mathcal X\ominus \mathcal V(\mathcal X)$
+is a convex set.
+Furthermore, we will see in the next section that, if $\mathcal X$ is polytopic and $\mathcal 
+V(x)$ is pointwise polytopic, then $\mathcal X\ominus\mathcal V(\mathcal X)$ is 
+again a polytopic set. 
+%This will become more clear in the next section when we describe 
+%the computation of the MRPI set~\eqref{eq:definition:MRPI:set:state:dependent}.
 %
@@
 %
-\section{Maximal Robust Positive Invariant Sets for State Dependent Disturbance}\label{sec:state:dep:MRPI}
+\section{Maximal Robust Positively Invariant Sets for State Dependent Disturbance}\label{sec:state:dep:MRPI}
 In this section we describe an iterative algorithm to compute the MRPI 
 set~\eqref{eq:definition:MRPI:set:state:dependent} for a linear system~\eqref{eq:system:equation} subject to disturbance
-$v\in\mathcal V(x)$ where $\mathcal V(x)$ is defined as in~\eqref{eq:PWA:distrubance:set} with a piecewise affine $H(x)$.
-Notice that the set $\mathcal V(x)$ is pointwise polytopic for finite $x\in\mathcal X_0$ and can hence be represented as the 
+$v\in\mathcal V(x)$ where $\mathcal V(x)$ is a parametrically convex point-to-set map defined by~\eqref{eq:PWA:distrubance:set} with a piecewise affine $H(x)$.
+Notice that the set $\mathcal V(x)$ is pointwise polytopic 
+%\note{is it necessary to assume that $\mathcal V(x)$ is bounded $\forall x\in\mathcal X_0$?}
+for finite $x\in\mathcal X_0$ and can hence be represented as the 
 convex hull of its vertices $\mathcal V(x) = \conv\{v_i(x)\}$. Since ${\mathcal{V}}(x)$
-has a piece-wise affine dependence on $x$ the vertices $v_i(x)$ are also piece-wise affine in $x$.
+has a piecewise affine dependence on $x$ the vertices $v_i(x)$ are also piecewise affine in $x$.
 The set $\mathcal X^\infty$ as defined in~\eqref{eq:definition:MRPI:set:state:dependent} 
-requires to satisfy $\Psi x + v\in\mathcal X^\infty$ for all
+is required to satisfy $\Psi x + v\in\mathcal X^\infty$ for all
 $x\in\mathcal X^\infty$ and $v\in\mathcal V(x)$. To compute the MRPI set we start from the given 
 state constraint set
-$\mathcal X_0 = \{x:\;\genmat_{0,i}x\leq \genvec_{0,i}\,\forall i\in\mathcal I_0\}$ and 
-\emph{cut off} all points that do not satisfy the invariance condition in $k$ steps, $k\in\mathbb N$. 
-So that all points remaining satisfy the invariance condition~\eqref{eq:definition:MRPI:set:state:dependent}. 
-I.e. we iteratively introduce 
-constraints that separate all points for which the successor state can lie outside 
-$\mathcal X_0$. So for the first iteration we need to enforce the constraint:
+\[
+\mathcal X_0 = \{x:\;\genmat_{0,i}x\leq \genvec_{0,i}\,\forall i\in\mathcal I_0\}
+\]
+and
+recursively \emph{cut off} points that cannot satisfy the invariance condition~\eqref{eq:definition:MRPI:set:state:dependent}
+%\emph{cut off} all points that do not satisfy the invariance condition in $k$ steps, $k\in\mathbb N$. 
+%So that all points remaining satisfy the invariance condition~\eqref{eq:definition:MRPI:set:state:dependent}
+by iteratively introducing
+constraints that exclude all points for which the successor state can lie outside 
+$\mathcal X_0$. The first iteration enforces the constraint:
 %
-\begin{equation}\begin{split}
+\[%\begin{equation}
+\begin{split}
 	&\genmat_{0,i}(\Psi x + v)\overset{!}{\leq}\genvec_{0,i}\;\forall v\in\conv\{v_i(x)\}\\
 	&\genmat_{0,i}\Psi x + \max_{v\in\mathcal V(x)} \genmat_{0,i} v \leq \genvec_{0,i}\\
-	&\genmat_{0,i}\Psi x + \underbrace{\max_{j} \genmat_{0,i} v_j(x)}_{v_{0,i}^\ast(x)} \leq \genvec_{0,i}.
-\end{split}\end{equation}
+	&\genmat_{0,i}\Psi x + \underbrace{\max_{j} \genmat_{0,i} v_j(x)}_{=v_{0,i}^\ast(x)} \leq \genvec_{0,i}.
+\end{split}
+\]%\end{equation}
 %
-to each inequality.
-Notice that $v_{0,i}^\ast(x)$ is not necessarily given by one unique maximiser, 
+for each $i\in \mathcal I_0$.
+Notice that $v_{0,i}^\ast(x)$ is not necessarily given by a unique maximiser, 
 but is the solution of a multiparametric linear program and hence will be given 
 by a vertex $v_i(x)$ of $\mathcal V(x)$ for each $x$ on that facet.
-Since each vertex is a piece-wise affine function of $x$ the maximum $v_{0,i}^\ast(x)$ will also
+Since each vertex is a piece-wise affine function of $x$, the maximum $v_{0,i}^\ast(x)$ will also
 be piece-wise affine
@@
 %
-\begin{multline}
+\begin{multline*}
 	\mathcal X_2 = \mathcal X_1 \cap \\ \{x:\genmat_{0,i}\Psi(\Psi x + v) + v_{0,i}^\ast(x)\leq\genvec_{0,i}\,
@@
 	= \mathcal X_1 \cap \{x: \genmat_{0,i}\Psi^2 x + v_{1,i}^\ast(x) + v_{0,i}^\ast(x)\leq\genvec_{0,i}\,\forall 
-	i\in\mathcal I_0\}.
-\end{multline}
+	i\in\mathcal I_0\},
+\end{multline*}
 %
-And we analogously define
+and after $(k+1)$ iterations we have
 %
-\begin{equation}
+\[%\begin{equation}
 	\mathcal X_{k+1} = \mathcal X_k\cap \{x:\genmat_{0,i}\Psi^k x + \sum_{l=0}^{k-1}v_{l,i}^\ast(x)
 	\leq\genvec_{0,i}\,\forall i\in\mathcal I_0\},
-\end{equation}
+\]%\end{equation}
 %
-where we have 
+where 
 %
-\begin{multline}
-	v_{l,i}^\ast(x)=\max_j \genmat_{0,i}\Psi^{l-1}v_j(x)\\
-	 = \begin{array}{rl} \max& \genmat_{0,i}\Psi^{l-1}v \\ \text{s.t.}& v\in\mathcal V(x)\end{array}
-	 = \begin{array}{rl} \max& \genmat_{0,i}\tilde v\\ \text{s.t.}& \tilde v\in \Psi^{l-1}\mathcal V(x) \end{array}
-\end{multline}
+%\begin{equation}
+\begin{align*}
+	v_{l,i}^\ast(x)&=\max_j \ \genmat_{0,i}\Psi^{l-1}v_j(x)
+	 = \begin{array}[t]{rl} \max& \genmat_{0,i}\Psi^{l-1}v \\ \text{s.t.}& v\in\mathcal V(x)\end{array} \\
+	 &= \begin{array}[t]{rl} \max& \genmat_{0,i}\tilde v\\ \text{s.t.}& \tilde v\in \Psi^{l-1}\mathcal V(x) \end{array}
+\end{align*}
+%\end{equation}
 %
-In a closed form the iterates can be expressed as
+In closed form the iterates can be expressed as
 %
@@
 	=\mathcal X_k\cap D_k \\
-	=& \bigcap_{l\leq k+1}\left( \Psi^{-l} \mathcal X_0 \underset{i\leq l-1}{\bigominus} \Psi^i \mathcal V(\mathcal X_{l-1})\right).
+	=& \bigcap_{0\leq l\leq k+1}\left( \Psi^{-l} \mathcal X_0 \underset{i\leq l-1}{\bigominus} \Psi^i \mathcal V(\mathcal X_{l-1})\right).
 \end{split}\end{equation}
@@
 $\mathcal X^\infty$, i.e. that there exists a finite number $N$ such that $x\in\mathcal X_N$ implies
-$\Psi x + v \in\mathcal X_N$ for all $v\in\mathcal V(x)$ and the set therefore is robustly positive invariant.
+$\Psi x + v \in\mathcal X_N$ for all $v\in\mathcal V(x)$ and therefore $\mathcal X_N$ is robustly positively invariant.
 %
 \begin{thm}\label{thm:finite:MRPI:set:state:dependable}
-Let the system constraints be contained in a band $\mathcal X_0\subseteq B=\{x:\Gamma x\leq{\bf{1}}\wedge 
+Let the state constraint set $\mathcal X_0$ be contained in a band: $\mathcal X_0\subseteq B=\{x:\Gamma x\leq{\bf{1}}\wedge 
 -\Gamma x\leq{\bf{1}}\}$, let the pair $(\Psi,\Gamma)$ be observable and let $\mathcal V(x)$ be defined by~\eqref{eq:PWA:distrubance:set}
-with a piecewise affine $H$, 
-then $\mathcal X_N\subseteq \mathcal X_{N+1}$ for a finite $N$. Hence the MRPI set $\mathcal X^\infty 
+with a piecewise affine $H(x)$, 
+then $\mathcal X_N\subseteq \mathcal X_{N+1}$ for a finite $N$, and hence the MRPI set $\mathcal X^\infty 
 =\mathcal X_N$ is a polytope.
@@
 \begin{proof}
-Notice that with~\eqref{eq:set:iteration:state:dependent:constraints} it is easy to see that in early
-iterations the parametric Pontryagin difference can yield the empty set. The empty set however is
-an admissible polytope, i.e. an admissible MRPI set. For the remainder of this proof we assume
-that the MRPI set is non-empty. For this notice that on any compact set $\mathcal S\subset\mathbb R^n$ we
-have $\bigcup_{s\in\mathcal S}\mathcal V(s)$ is compact.
+From~\eqref{eq:set:iteration:state:dependent:constraints} it is clear that $\mathcal X^\infty = \emptyset$ if $\mathcal X_k =\emptyset$ for any $k\geq 0$.
+%Notice that with~\eqref{eq:set:iteration:state:dependent:constraints} it is easy to see that in early iterations the parametric Pontryagin difference can yield the empty set.
+The empty set however is an admissible polytope, i.e.
+an admissible MRPI set.
+For the remainder of the proof we assume
+that the MRPI set $\mathcal X^\infty$ is non-empty. For this we require that $\bigcup_{s\in\mathcal S}\mathcal V(s)$ is compact on any compact set $\mathcal S\subset\mathbb R^n$.
 
-The proof has two main steps: First we will prove that $\mathcal X_p$ is compact for $p\leq n$
-where $n$ is the state dimension. The second step is to prove that in~\eqref{eq:set:iteration:state:dependent:constraints}
+The proof has two main steps: First we prove that $\mathcal X_p$ is compact for $p\leq n$
+where $n$ is the dimension of the state $x$. The second step is to prove that in~\eqref{eq:set:iteration:state:dependent:constraints}
 the set $D_k$ grows exponentially, i.e. that for any given compact set $\mathcal C$ there exists
-a $\tilde N$ such that $\mathcal C\subseteq D_{\tilde N}$. The proof is concluded by setting 
-$\mathcal C = \mathcal X_p$ and using $N = \tilde N$. For the first step, notice that the observability of
-$(\Psi,\Gamma)$ is equivalent to the observability matrix $\Omega$ having full rank, i.e.
+finite $\tilde N$ such that $\mathcal C\subseteq D_{\tilde N}$. The proof is concluded by setting 
+$\mathcal C = \mathcal X_{\tilde N}$ and deducing that $N = \tilde N$.
+
+For the first step, notice that observability of
+$(\Psi,\Gamma)$ is equivalent to the observability matrix $\Omega$ having full rank, i.e.\ $\mathrm{rank}(\Omega) = \mathrm{rank}(\begin{bmatrix} \Gamma^T \ \cdots \ (\Gamma\Psi^{n-1})^T\end{bmatrix}) = n$.
+% \[
+% \Omega = \left(\begin{array}{c}
+% \Gamma\\ \vdots \\ \Gamma\Psi^{n-1}
+% \end{array}\right)
+% \]
+%having a trivial kernel. 
+But  this implies that the set 
 \[
-\Omega = \left(\begin{array}{c}
-\Gamma\\ \vdots \\ \Gamma\Psi^{n-1}
-\end{array}\right)
+\mathcal P_{n} = \{x: 
+\Omega x\leq{\bf{1}}\wedge-\Omega x\leq{\bf{1}}\} = \bigcap_{0\leq l\leq n-1} \Psi^{-l} B
 \]
-having a trivial kernel. But this then implies that the set $\mathcal P_{n+1} = \{x: 
-\Omega x\leq{\bf{1}}\wedge-\Omega x\leq{\bf{1}}\} = \bigcap_{l\leq n+1} \Psi^{-l} B$ is bounded.
-Notice that the containment $\mathcal X_k\subseteq \mathcal P_k$ holds for all $k$ and hence
-the set $\mathcal X_{n+1}$ is also bounded. The case that $\tilde N<n$ occurs when $\Gamma$
-has more than rank one. To see that $D_k$ grows exponentially we use that $\mathcal V(\mathcal X_{n+1})$
-is bounded, let $K_1$ denote the smallest ball that contains $\mathcal V(\mathcal X_{n+1})$ and let
-$\bar\lambda$ denote the magnitude of the largest eigenvalue of $\Psi$. Furthermore, let $K_1$
+is bounded, and since $\mathcal X_k\subseteq \mathcal P_k$ for all $k$, 
+the set $\mathcal X_{n}$ is also bounded. The case that $\tilde N<n$ can occur if $\mathrm{rank}(\Gamma) > 1$.
+%has more than rank one. 
+More generally, to show that $D_k$ grows exponentially we use the boundedness of $\mathcal V(\mathcal X_{n})$. Let $K_1$ denote the smallest ball that contains $\mathcal V(\mathcal X_{n})$ and let
+$\bar\lambda$ denote the magnitude of the largest eigenvalue of $\Psi$. Furthermore, let $K_2$
 be the biggest ball that is contained in $\mathcal X_{0}$. $D_k$ has the representation
 \begin{equation}
-D_k = \underbrace{\Psi^{-k}\mathcal X_0}_{(i)} \ominus \underbrace{\left(\bigoplus_{i\leq k-1} 
-\Psi^i\mathcal V(\mathcal X_k)\right)}_{(ii)}.
+D_k = \underbrace{\Psi^{-k}\mathcal X_0}_{=\mathcal S_1} \ominus \underbrace{\left(\bigoplus_{i\leq k-1} 
+\Psi^i\mathcal V(\mathcal X_k)\right)}_{=\mathcal S_2}.
 \end{equation}
-Since $\Psi$ is asymptotically stable we know that $\bar\lambda<1$ and so we have 
-$\bar\lambda^{-l}K_1\subseteq\Psi^{-l} K_1 \subseteq \Psi^{-l}\mathcal X_0 = (i)$
-which implies exponential growth of $D_k$ as long as $(ii)$ is bounded. Recall that we assume
-that the MRPI set is non-empty.
-Hence, to bound $(ii)$ we use $k\geq n+1$ where $(ii)\subseteq \oplus_{i\leq k-1} \bar\lambda^i K_2 \subseteq
-\frac{1}{1-\bar\lambda} K_2$ holds. This concludes the proof: We proved that $D_k$ grows exponentially,
-that it contains an exponentially growing ball. We proved that the subtrahend is bounded inside a ball of
-finite radius, and hence we conclude that after a finite number of iterations $N$ intersecting with $D_{N+1}$
-will no longer change $\mathcal X_N$.
+Since $\Psi$ is asymptotically stable we have $\bar\lambda<1$ and therefore
+$\bar\lambda^{-l}K_1\subseteq\Psi^{-l} K_1 \subseteq \Psi^{-l}\mathcal X_0 = \mathcal S_1$,
+implying exponential growth of $D_k$ provided $\mathcal S_2$ is bounded. 
+%Recall that we assume
+%However the MRPI set is non-empty by assumption, and t
+To bound $\mathcal S_2$ we note that $\mathcal S_2\subseteq \oplus_{i\leq k-1} \bar\lambda^i K_2 \subseteq
+\frac{1}{1-\bar\lambda} K_2$ holds for $k\geq n$. This concludes the proof since $D_k$ grows exponentially,
+%as it contains an exponentially growing ball. We proved that 
+whereas $\mathcal X_k$ is contained in a ball of
+finite radius, and hence we conclude from \eqref{eq:set:iteration:state:dependent:constraints} that 
+$\mathcal X_{k+1} = \mathcal X _k$ for all $k\geq N$ and therefore $\mathcal X _N = \mathcal X^\infty$ for finite $N$.
+%after a finite number of iterations $N$ intersecting with $D_{N+1}$
+%will no longer change $\mathcal X_N$.
 \end{proof}
 %
-We have seen that we can compute a the maximal robust positive invariant set $\mathcal X^\infty$ for linear 
+We have seen that we can compute a the maximal robust positively invariant set $\mathcal X^\infty$ for linear 
 systems with state dependent constraints. In the next section we will illustrate the concept with an 
@@
 \end{lpic}
-\caption{The maximal robust positive invariant set for the levitating ball system.}
+\caption{The maximal robust positively invariant set for the levitating ball system.}
 \label{fig:MRPI:set:levitating:ball}
@@
 %
-\section{Maximal Robust Positive Invariant Sets for Parametrised Disturbance}\label{sec:MRPI:parametrised}
+\section{Maximal Robust Positively Invariant Sets for Parametrised Disturbance}\label{sec:MRPI:parametrised}
 %

### 2015-03-20 draft.tex
H has to be convex not only PWA!
Edited sections IV to VII and .bib Please check carefully…

@@
   for linear discrete time systems with additive model uncertainty. Two types of uncertainty are 
-  considered: state dependent uncertainty, which handles multiplicative parametric model uncertainty 
-  as well as linearisation errors for nonlinear systems, and scaled sets of uncertainty. We provide 
+  considered: state dependent uncertainty, which can handle multiplicative parametric model uncertainty 
+  as well as linearisation errors for nonlinear systems, and scaled
+  sets of uncertainty. We provide 
   a framework for analysing both types of uncertainty with illustrative examples.
@@
 since their introduction in~\cite{Glover:1971,bertsekas71}. A disturbance invariant set $\mathscr X$ is a subset of the 
-state constraint set $\mathcal X_0\subseteq\mathbb R^n$ containing states $x$ of the perturbed linear system
+state constraint set $\mathcal X_0\subseteq\mathbb R^n$ containing
+states $x$ of the perturbed linear system
 \begin{equation}\label{eq:system:equation}
@@
 (where $\Psi$ is Hurwitz, $x,x^+\in\mathcal X_0$, and 
-$v\in\mathscr V$) such that the successor state $x^+$ is contained in the 
-disturbance invariant set for all possible realisations of the 
-unknown disturbance $v$. This is summarised in the implicit definition
+$v\in\mathscr V$), such that the successor state $x^+$ is contained in $\mathscr X$
+%the disturbance invariant set 
+for all possible realisations of the 
+unknown disturbance $v$. Thus a disturbance invariant set is a type of robust positively invariant (RPI) set. 
+This is summarised in the implicit definition
 \begin{equation}\label{eq:definition:MRPI:set:state:dependent}
@@
 \end{equation}
-Thus a disturbance invariant set is a type of robust positively invariant (RPI) set. 
+
 In many applications we are interested in the largest such set, denoted $\mathcal X^\infty$, which is given 
@@
 robust model predictive control~\cite{mayne:2000}. Although analytical properties
-of these sets were derived soon after their introduction, algorithms for numerically computing MRPI sets 
+of these sets were derived at the time of their introduction, algorithms for numerically computing MRPI sets 
 were introduced much later~\cite{Blanchini:1994,DeSantis:1994,Kolmanovsky:1998}. 
@@
 Earlier algorithms did not guarantee finite determinability of $\mathcal X^\infty$, see e.g.~\cite{Blanchini:1990}, 
-or did not guarantee to produce the maximal RPI set, e.g.~\cite{Blanchini:1991}. 
+or were not guaranteed to produce the maximal RPI set, e.g.~\cite{Blanchini:1991}. 
 %
 However for the case of disturbances belonging to a fixed set $\mathscr V$, methods of computing 
-$\mathcal X^\infty$ are well established~\cite{blanchini:2007}.
+$\mathcal X^\infty$ are now well established~\cite{blanchini:2007}.
 
@@
 parameters. First we consider state-dependent sets,
-\begin{equation}\label{eq:PWA:distrubance:set}
+\begin{equation}\label{eq:PWA:disturbance:set}
 	\mathcal V(x) = \left\{v: Gv\leq H(x)\right\},
@@
 %$G\in\mathbb R^{n_G\times n_v}$, 
-$H(x)$ is a piecewise affine function, and the inequality applies elementwise. For the case that $\mathscr V=\mathcal V(x)$ we
+$H(x)$ is a convex piecewise affine function, and the inequality applies elementwise. For the case that $\mathscr V=\mathcal V(x)$ we
 provide conditions for convexity and finite determination of $\mathcal X^\infty$ and discuss 
@@
 constraints and its finite determinability are discussed in Section~\ref{sec:state:dep:MRPI}.
-Section~\ref{sec:first:example} illustrates the algorithm using the example of a magnetically 
+Section~\ref{sec:first:example} illustrates the algorithm using a nonlinear model of a magnetically 
 levitated ball. The case of scaled disturbance constraints is discussed in Section~\ref{sec:MRPI:parametrised},
@@
 Throughout this paper we refer to sets that can be represented as intersections of finite numbers of half spaces as polyhedra, and to bounded polyhedra as polytopic sets.
-Also ${\bf{1}}$ denotes the column vector of ones in appropriate dimensions, and $\wedge$ is the logical AND operator.
-
+For sets $\mathcal A, \mathcal B \subset\mathbb R^n$, the Minkowski set addition is denoted $\mathcal A\oplus\mathcal B = \{c : c = a + b\; \forall\,a\in\mathcal A,\, b\in\mathcal B\}$.
+We use ${\bf{1}}$ to denote the column vector of ones in appropriate dimensions, and $\wedge$ is the logical AND operator. 
 %
@@
 \section{Parametrically convex set operations}\label{sec:parametrically:convex:set:operations}
-This section discusses sets that depend on a state-like parameter (so called point-to-set maps, 
+This section discusses sets that depend on a parameter such as the state of \eqref{eq:system:equation} (so called point-to-set maps, 
 see~\cite{Hogan:1973}), and extends the existing set algebra~\cite{blanchini:2007} to 
-accommodate such sets. We present the general case first, then derive the computation of
-the case with piece-wise affine sets.
+accommodate such sets. We present the general case first, then illustrate it with the example of a pointwise polyhedral set in the form of (\ref{eq:PWA:disturbance:set})
+% with piecewise affine $H(x)$.
 %
@@
 %
-In (\ref{eq:pconvexdef}), $\oplus$ denotes the Minkowski set addition
-      \begin{equation}
-        \mathcal A\oplus\mathcal B = \{c : c = a + b\; \forall\,a\in\mathcal A,\, b\in\mathcal B\}.
-      \end{equation}
+% In (\ref{eq:pconvexdef}), $\oplus$ denotes the Minkowski set addition
+%       \begin{equation}
+%         \mathcal A\oplus\mathcal B = \{c : c = a + b\; \forall\,a\in\mathcal A,\, b\in\mathcal B\}.
+%       \end{equation}
 %
@@
 %
-  % Consider a point-to-set map~\eqref{eq:PWA:distrubance:set},
-  %   where $H$ is elementwise convex in $x\in \mathcal X\subset \mathbb R^n$, with elements $H_i(x)$ satisfying
-  %   $H_i(\lambda x_1+(1-\lambda)x_2)\leq \lambda H_i(x_1)+(1-\lambda)H_i(x_2)$, for all    $\lambda\in[0,1]$, and $x_1, x_2\in\mathcal X$.  For such sets we have the result:
-%A family of parametrically convex sets is defined as follows.
+Now consider a parametrically convex set of the form of~\eqref{eq:PWA:disturbance:set}.
     \begin{thm}\label{thm:convex:parametric:set}
-      The point-to-set map $\mathcal V (x)$ defined by~\eqref{eq:PWA:distrubance:set} is parametrically 
+      The point-to-set map $\mathcal V (x)$ defined by~\eqref{eq:PWA:disturbance:set} is parametrically 
       convex for all $x\in \mathcal X$ if $H(x)$ is elementwise convex in $x\in \mathcal X\subset \mathbb R^n$ (i.e.~if each element $H_i(x)$ of $H(x)$ satisfies
@@
     % \begin{thm}\label{thm:convex:parametric:set}
-    %   The point-to-set map $\mathcal V (x)$ defined by~\eqref{eq:PWA:distrubance:set} for a function $H(x)$ that is elementwise convex in $x\in \mathcal X\subset \mathbb R^n$ (i.e.~each element $H_i(x)$ of $H(x)$ satisfies
+    %   The point-to-set map $\mathcal V (x)$ defined by~\eqref{eq:PWA:disturbance:set} for a function $H(x)$ that is elementwise convex in $x\in \mathcal X\subset \mathbb R^n$ (i.e.~each element $H_i(x)$ of $H(x)$ satisfies
     % $H_i(\lambda x_1+(1-\lambda)x_2)\leq \lambda H_i(x_1)+(1-\lambda)H_i(x_2)$ for all    $\lambda\in[0,1]$ and $x_1, x_2\in\mathcal X$) is parametrically 
@@
 Lemmas~\ref{thm:convexity:of:pontryagin:difference} 
-and~\ref{thm:convex:parametric:set} imply that, if $\mathcal V(x)$ is defined by \eqref{eq:PWA:distrubance:set} in terms of an elementwise convex function $H(x)$, then the parametric Pontryagin difference $\mathcal X\ominus \mathcal V(\mathcal X)$
+and~\ref{thm:convex:parametric:set} imply that, if $\mathcal V(x)$ is defined by \eqref{eq:PWA:disturbance:set} in terms of an elementwise convex function $H(x)$, then the parametric Pontryagin difference $\mathcal X\ominus \mathcal V(\mathcal X)$
 is a convex set.
-Furthermore, we will see in the next section that, if $\mathcal X$ is polytopic and $\mathcal 
+As we show in the next section, if $\mathcal X$ is polytopic and $\mathcal 
 V(x)$ is pointwise polytopic, then $\mathcal X\ominus\mathcal V(\mathcal X)$ is 
-again a polytopic set. 
+also a polytope. 
 %This will become more clear in the next section when we describe 
@@
 In this section we describe an iterative algorithm to compute the MRPI 
-set~\eqref{eq:definition:MRPI:set:state:dependent} for a linear system~\eqref{eq:system:equation} subject to disturbance
-$v\in\mathcal V(x)$ where $\mathcal V(x)$ is a parametrically convex point-to-set map defined by~\eqref{eq:PWA:distrubance:set} with a piecewise affine $H(x)$.
-Notice that the set $\mathcal V(x)$ is pointwise polytopic 
+set~\eqref{eq:definition:MRPI:set:state:dependent} for a linear system~\eqref{eq:system:equation} subject to disturbances
+$v\in\mathcal V(x)$ where $\mathcal V(x)$ is a parametrically convex point-to-set map defined by~\eqref{eq:PWA:disturbance:set} with a piecewise affine function $H(x)$.
+We assume (without loss of generality) that the set $\mathcal V(x)$ is pointwise compact and polytopic 
 %\note{is it necessary to assume that $\mathcal V(x)$ is bounded $\forall x\in\mathcal X_0$?}
@@
 The next iterate is defined by
+\begin{align*}
+	\mathcal X_2 &= \mathcal X_1 \cap \\ &\{x:\genmat_{0,i}\Psi(\Psi x + v) + v_{0,i}^\ast(x)\leq\genvec_{0,i}\,
+	\forall i\in\mathcal I_0,v\in\mathcal V(x)\}\\
+&= \mathcal X_1 \cap \{x: \genmat_{0,i}\Psi^2 x + v_{1,i}^\ast(x) + v_{0,i}^\ast(x)\leq\genvec_{0,i}\,\forall 
+	i\in\mathcal I_0\}
+\end{align*}
 %
-\begin{multline*}
-	\mathcal X_2 = \mathcal X_1 \cap \\ \{x:\genmat_{0,i}\Psi(\Psi x + v) + v_{0,i}^\ast(x)\leq\genvec_{0,i}\,
-	\forall i\in\mathcal I_0,v\in\mathcal V(x)\}\\
-	= \mathcal X_1 \cap \{x: \genmat_{0,i}\Psi^2 x + v_{1,i}^\ast(x) + v_{0,i}^\ast(x)\leq\genvec_{0,i}\,\forall 
-	i\in\mathcal I_0\},
-\end{multline*}
-%
-and after $(k+1)$ iterations we have
+and at the $(k+1)$st iteration we have
 %
@@
 	v_{l,i}^\ast(x)&=\max_j \ \genmat_{0,i}\Psi^{l-1}v_j(x)
-	 = \begin{array}[t]{rl} \max& \genmat_{0,i}\Psi^{l-1}v \\ \text{s.t.}& v\in\mathcal V(x)\end{array} \\
-	 &= \begin{array}[t]{rl} \max& \genmat_{0,i}\tilde v\\ \text{s.t.}& \tilde v\in \Psi^{l-1}\mathcal V(x) \end{array}
+	 = \begin{array}[t]{rl} \displaystyle\max_v & \genmat_{0,i}\Psi^{l-1}v \\ \text{s.t.}& v\in\mathcal V(x)\end{array} \\
+	 &= \begin{array}[t]{rl} \displaystyle\max_{\tilde v} & \genmat_{0,i}\tilde v\\ \text{s.t.}& \tilde v\in \Psi^{l-1}\mathcal V(x) \end{array}
 \end{align*}
@@
 %
-In closed form the iterates can be expressed as
+In closed form the iterates can be expressed (assuming for convenience that $\Psi$ is invertible) as
 %
@@
 	=\mathcal X_k\cap D_k \\
-	=& \bigcap_{0\leq l\leq k+1}\left( \Psi^{-l} \mathcal X_0 \underset{i\leq l-1}{\bigominus} \Psi^i \mathcal V(\mathcal X_{l-1})\right).
+	=& \bigcap_{0\leq l\leq k+1}\left( \Psi^{-l} \mathcal X_0 \underset{0 \leq i\leq l-1}{\bigominus} \Psi^i \mathcal V(\mathcal X_{l-1})\right).
 \end{split}\end{equation}
@@
 We will use~\eqref{eq:set:iteration:state:dependent:constraints} to prove the finite determinability of
-$\mathcal X^\infty$, i.e. that there exists a finite number $N$ such that $x\in\mathcal X_N$ implies
-$\Psi x + v \in\mathcal X_N$ for all $v\in\mathcal V(x)$ and therefore $\mathcal X_N$ is robustly positively invariant.
+$\mathcal X^\infty$, namely that there exists a finite number $N$ such that $x\in\mathcal X_N$ implies
+$\Psi x + v \in\mathcal X_N$ for all $v\in\mathcal V(x)$ and hence $\mathcal X_N$ is robustly positively invariant.
 %
@@
 Let the state constraint set $\mathcal X_0$ be contained in a band: $\mathcal X_0\subseteq B=\{x:\Gamma x\leq{\bf{1}}\wedge 
--\Gamma x\leq{\bf{1}}\}$, let the pair $(\Psi,\Gamma)$ be observable and let $\mathcal V(x)$ be defined by~\eqref{eq:PWA:distrubance:set}
-with a piecewise affine $H(x)$, 
-then $\mathcal X_N\subseteq \mathcal X_{N+1}$ for a finite $N$, and hence the MRPI set $\mathcal X^\infty 
+-\Gamma x\leq{\bf{1}}\}$, let the pair $(\Psi,\Gamma)$ be observable and let $\mathcal V(x)$ be defined by~\eqref{eq:PWA:disturbance:set}
+in terms of a piecewise affine function $H(x)$.
+Then $\mathcal X_N\subseteq \mathcal X_{N+1}$ for a finite $N$, and hence the MRPI set $\mathcal X^\infty 
 =\mathcal X_N$ is a polytope.
@@
 the set $D_k$ grows exponentially, i.e. that for any given compact set $\mathcal C$ there exists
-finite $\tilde N$ such that $\mathcal C\subseteq D_{\tilde N}$. The proof is concluded by setting 
-$\mathcal C = \mathcal X_{\tilde N}$ and deducing that $N = \tilde N$.
+finite $N$ such that $\mathcal C\subseteq D_{N}$. The proof is concluded by setting 
+$\mathcal C = \mathcal X_{N}$ and deducing that $\mathcal X^\infty = \mathcal X_N$.
 
@@
 is bounded, and since $\mathcal X_k\subseteq \mathcal P_k$ for all $k$, 
-the set $\mathcal X_{n}$ is also bounded. The case that $\tilde N<n$ can occur if $\mathrm{rank}(\Gamma) > 1$.
-%has more than rank one. 
-More generally, to show that $D_k$ grows exponentially we use the boundedness of $\mathcal V(\mathcal X_{n})$. Let $K_1$ denote the smallest ball that contains $\mathcal V(\mathcal X_{n})$ and let
-$\bar\lambda$ denote the magnitude of the largest eigenvalue of $\Psi$. Furthermore, let $K_2$
-be the biggest ball that is contained in $\mathcal X_{0}$. $D_k$ has the representation
+the set $\mathcal X_{n}$ is also bounded. 
+%The case that  $N<n$ can occur if $\mathrm{rank}(\Gamma) > 1$.
+%More generally, to 
+To show that $D_k$ grows exponentially we use the compactness of $\mathcal V(\mathcal X_{n})$. Let $K_1$ denote the smallest ball that contains $\mathcal V(\mathcal X_{n})$ and let
+$\rho$ denote the spectral radius of $\Psi$. Furthermore, let $K_2$
+be the biggest ball that is contained in $\mathcal X_{0}$. From~\eqref{eq:set:iteration:state:dependent:constraints}, $D_k$ has the representation
 \begin{equation}
@@
 \end{equation}
-Since $\Psi$ is asymptotically stable we have $\bar\lambda<1$ and therefore
-$\bar\lambda^{-l}K_1\subseteq\Psi^{-l} K_1 \subseteq \Psi^{-l}\mathcal X_0 = \mathcal S_1$,
+Since $\Psi$ is asymptotically stable we have $\rho<1$ and therefore
+$\rho^{-l}K_1\subseteq\Psi^{-l} K_1 \subseteq \Psi^{-l}\mathcal X_0 = \mathcal S_1$,
 implying exponential growth of $D_k$ provided $\mathcal S_2$ is bounded. 
@@
 %However the MRPI set is non-empty by assumption, and t
-To bound $\mathcal S_2$ we note that $\mathcal S_2\subseteq \oplus_{i\leq k-1} \bar\lambda^i K_2 \subseteq
-\frac{1}{1-\bar\lambda} K_2$ holds for $k\geq n$. This concludes the proof since $D_k$ grows exponentially,
-%as it contains an exponentially growing ball. We proved that 
+To bound $\mathcal S_2$ we note that for $k\geq n$ we have $\mathcal S_2\subseteq \bigoplus_{0\leq i\leq k-1} \rho^i K_2 \subseteq
+\frac{1}{1-\rho} K_2$.
+Thus $D_k$ grows exponentially,
 whereas $\mathcal X_k$ is contained in a ball of
@@
 %
-In this section we discuss the calculation of the MRPI set for a linearised simplified model of the levitating
-ball system depict in figure~\ref{fig:levitating:ball}. The system dynamics for the ball are given
+In this section we discuss the calculation of the MRPI set for a linearised simplified model of the magnetic levitation system depict in figure~\ref{fig:levitating:ball}.
+The system dynamics for the ball are given
 by $m \ddot y = m g - c\frac{i^2}{y^2}$, where $m,g,c,i$ and $y$ denote the mass of the ball, the gravitational
@@
 is present when $x_2=0$ and $u=\sqrt{\frac{gm}{c}}x_1$ for any positive position $x_1>0$.
-Linearising the nonlinear differential equation $\dot x = f(x,u)$ around $\hat x, \hat u$ we obtain
+Linearising the nonlinear differential equation $\dot x = f(x,u)$ around $\hat x, \hat u$ we obtain the linear approximation
 %
@@
 We derive discrete time system dynamics using the explicit Euler formula $x^+=x+T_s f(x,u) =:\tilde f(x,u)$,
-with the sampling rate $T_s$. We hence define the system matrix $A = (I+T_s\frac{\partial f}{\partial x}(\hat x,\hat u))$
+with the sampling rate $T_s$. Hence we define the system matrix $A = (I+T_s\frac{\partial f}{\partial x}(\hat x,\hat u))$
 and the input matrix $B = T_s \frac{\partial f}{\partial u}(\hat x,\hat u)$. 
 Notice that using a non-autonomous model does not affect our analysis since we analyse the closed loop system
-governed by a linear state feedback controller $u=Kx$. To cope with disturbance optimally we use $K$ 
-being the solution to robust Lyapunov condition $V(x)-V((A+BK)x+Dw)\leq \gamma^2w^Tw$ with $V(x)=x^T P x\geq0$, i.e.
+governed by a linear state feedback controller $u=Kx$. We choose $K$ as the solution of the robust Lyapunov condition $V(x)-V((A+BK)x+Dw)\leq \gamma^2w^Tw$ with $V(x)=x^T P x\geq0$, i.e.
 $x^TPx - ((A+BK)x+Dw)^TP((A+BK)x+Dw)\geq x^T(Q+K^TRK)x -\gamma^2 w^Tw$ for a minimised $\gamma^2$, 
 see e.g.~\cite{Boyd:94}.
-In order to obtain a 
-representation of additive disturbances depending on the state and input like~\eqref{eq:PWA:distrubance:set}
-we use the mean-value theorem for vector valued functions, see e.g.~\cite{Apostol:1974}:
+A representation of additive disturbances that act on the state of the linearised model as a result of the linearisation error can be obtained using the mean-value theorem for vector valued functions (e.g.~\cite{Apostol:1974}):
 %
@@
 %
-Using the mean value theorem~\ref{thm:mean:value:theorem}
+Using the Mean Value Theorem~\ref{thm:mean:value:theorem}
 and the linearisation for $\Delta x = \hat x + \tilde x$ and $\Delta u = \hat u + \tilde u$ we
@@
 %
-This implies that for any state $\tilde x$ of linearised we obtain the expression
+Thus for any state $\tilde x=\Delta x - \hat{x}$ we obtain the (exact) dynamics
 $\tilde x^+ = A\tilde x+B\tilde u + H^x\tilde x + H^u \tilde u$, however the computation
-of $H^x$ and $H^u$ requires solving a nonlinear integral. Assume that
+of $H^x$ and $H^u$ requires solving a nonlinear integral. Suppose that
 for $x\in\mathcal X$ and $u\in\mathcal U$, where $\mathcal X$ and $\mathcal U$ are compact
-sets, we had extremal values of $H^x$ and $H^u$, i.e.
+sets, we have extremal values of $H^x$ and $H^u$, i.e.
 $H^x\tilde x+H^u\tilde u\in\conv_k\{H^x_k\tilde x + H^u_k\tilde u\}$ for all $(\tilde x,\tilde u)\in\mathcal X\times \mathcal U$.
-Clearly, we can then introduce the element wise bound disturbance 
+Clearly, we can then introduce the element\-wise disturbance bound 
 %
@@
 \mathcal V(x,u)=\left\{v:\min_k\{
-H^x_{k,i}x+H^u_{k,i}u\}\leq v_i\,\wedge\right. \\ \left.v_i \leq \max_k\{H^x_{k,i}x+H^u_{k,i}u\}\, i =1,\dots,n\right\}.
+H^x_{k,i}x+H^u_{k,i}u\}\leq v_i\,\wedge\right. \\ \left.v_i \leq \max_k\{H^x_{k,i}x+H^u_{k,i}u\}, \, i =1,\dots,n\right\}.
 \end{split}
@@
 guarantee that $\tilde x^+ = A\tilde x + B\tilde u + v$ accounts for all nonlinearities within $\mathcal X
-\times\mathcal U$ if we constraint $v\in\mathcal V(\tilde x,\tilde u)$. For general nonlinear systems
-finding the extremal values of $(H^x,H^u)$ can not be done easily.
+\times\mathcal U$ if we constrain $v\in\mathcal V(\tilde x,\tilde u)$. For general nonlinear systems
+finding the extremal values of $(H^x,H^u)$ cannot be done easily.
 To obtain values for $(H^x_k,H^u_k)$ we sample $\mathcal X\times\mathcal U$ and evaluate the integral 
@@
 which is less conservative than using fixed bounds on the nonlinearities as we will see in the next example.
-The algorithm terminates after 3 iterations.
+The algorithm for computing the MRPI set terminates after 3 iterations.
 %
@@
 %
-In this section we describe the computation of the MRPI set for~\eqref{eq:system:equation}
-but using a disturbance set that is parametrised for scaling, i.e. $\mathcal V(\theta) = \{v: Gv\leq(1+\theta){\bf{1}}\} 
-= (1+\theta)\mathcal V(0)$, for $\theta>-1$. We will be able to combine the uniform scaling of 
+In this section we describe the computation of the MRPI set for~\eqref{eq:system:equation} with a disturbance set parametrised by a scalar $\theta$:
+\[
+\mathcal V(\theta) = \{v: Gv\leq(1+\theta){\bf{1}}\} 
+= (1+\theta)\mathcal V(0), \ \ \theta>-1.
+\]
+For input constrained systems under a given feedback law, we combine the uniform scaling of 
 the disturbance set $\mathcal V(\theta)$ with non-uniform scaling of the input constraint set
-$\mathcal U({\bf{\alpha}}) = \{u: Fu\leq\left(I+\text{diag}(\alpha_1,\dots,\alpha_p)\right){\bf{1}}\}$.
-The necessity of uniform scaling of the disturbance constraints is due to a finesse we use to avoid
-solving multiparametric linear programs in every substep of the proposed iteration.
+\[
+\mathcal U({\bf{\alpha}}) = \{u: Fu\leq\left(I+\text{diag}(\alpha_1,\dots,\alpha_p)\right){\bf{1}}\}.
+\]
+The necessity of uniform scaling of the disturbance constraints is due to the method we use to avoid
+solving multiparametric linear programs in every step of the proposed iteration.
 A representation of the MRPI set of a system parametrised with respect to a scaling parameter allows us
-to study the system's sensitivity to \emph{stronger/weaker} disturbance, the sensitivity to input 
+to study the system's sensitivity to \emph{stronger/weaker} disturbances; similarly analysing the sensitivity to scaling of input 
 constraints can be useful to choose particular actuators.
@@
 \[
-0<\begin{array}{rl}
-\max & c^T v\\
-\text{s.t.}& Gv \leq (1+\theta){\bf{1}}\\
-&\theta>-1
+0<\begin{array}[t]{rl}
+\displaystyle\max_v & c^T v\\
+\text{s.t.}& Gv \leq (1+\theta){\bf{1}}
+%\\
+%&\theta>-1
 \end{array}
@@
 \begin{split}
-	D_0 =& \{\mathcal F_i(\Psi x+v) + \mathcal G_i\theta \leq 1 \forall\, v\in\mathcal V(\theta), i\leq m\}\\
-	=&\left\{\mathcal F_i\Psi x + \begin{array}{rl}\max& F_i v \\ \text{s.t.}& Gv \leq 
-	(1+\theta){\bf{1}} \\ &\theta>-1\end{array}
-	 + \mathcal G_i \theta \leq 1 \forall\, i\leq m\right\}\\
-	=&\left\{\mathcal F_i\Psi x + (1+\theta)\underbrace{\begin{array}{rl}\max& F_i v \\ 
+	D_0 =& \{\mathcal F_i(\Psi x+v) + \mathcal G_i\theta \leq 1 \ \forall\, v\in\mathcal V(\theta), \ i\leq m\}\\
+	=&\Biggl\{\mathcal F_i\Psi x + \begin{array}[t]{rl}\displaystyle\max_v& F_i v \\ \text{s.t.}& Gv \leq 
+	(1+\theta){\bf{1}} \end{array}
+	 + \mathcal G_i \theta \leq 1 \ \forall\, i\leq m\Biggr\}\\
+	=&\Biggl\{\mathcal F_i\Psi x + (1+\theta)\underbrace{\begin{array}[t]{rl}\displaystyle\max_v& F_i v \\ 
 	\text{s.t.}& Gv \leq {\bf{1}}\end{array}}_{v_{0,i}^\ast}
-	 + \mathcal G_i \theta \leq 1 \forall\, i\leq m\right\}\\
-	=&\{\mathcal F_i\Psi x + (\mathcal G_i + v_{0,i}^\ast)\theta \leq 1 - v_{0,1}^\ast \forall i\leq m
+	 + \mathcal G_i \theta \leq 1 \ \forall\, i\leq m\Biggr\}\\
+	=&\{\mathcal F_i\Psi x + (\mathcal G_i + v_{0,i}^\ast)\theta \leq 1 - v_{0,1}^\ast \ \forall \, i\leq m
 	\}
@@
 \begin{equation}\label{eq:parametrised:Dk}\small
-	D_k = \{\mathcal F_i\Psi^{k+1}x+ \left(\mathcal G_i +\sum_{0\leq l\leq k} v_{l,i}^\ast\right)\theta \leq 1 
-	- \sum_{0\leq l\leq k} v_{l,i}^\ast\, i\leq m\}
+	D_k = \biggl\{\mathcal F_i\Psi^{k+1}x+ \biggl(\mathcal G_i +\sum_{0\leq l\leq k} v_{l,i}^\ast\biggr)\theta \leq 1 
+	- \sum_{0\leq l\leq k} v_{l,i}^\ast\, i\leq m\biggr\}
 \end{equation}
@@
 \begin{equation}\label{eq:definition:v:ast}
-v_{l,i}^\ast = \begin{array}{rl}\max & \mathcal F_i \Psi^{l} v \\ \text{s.t.}& Gv\leq{\bf{1}}
+v_{l,i}^\ast = \begin{array}[t]{rl}\displaystyle\max_v & \mathcal F_i \Psi^{l} v \\ \text{s.t.}& Gv\leq{\bf{1}}
 \end{array}
@@
 \begin{array}{rlcrlcrl}
-\max&\mathcal F_i \Psi^l v &=& \max&\mathcal F_i \tilde  v &=& \max&\mathcal F_i v \\ 
+\max_v&\mathcal F_i \Psi^l v &=& \max_{\tilde v}&\mathcal F_i \tilde  v &=& \max_{\tilde v}&\mathcal F_i \tilde v \\ 
 \text{s.t.}&v\in\bar{\mathcal{V}} & & \text{s.t.}&\Psi^{-l} \tilde v\in\bar{\mathcal{V}} & &
@@
 	\Psi^{-1}Z_k\vert_{\hat\theta}\ominus\Psi^{k-1}\mathcal V(\hat\theta)\right)\\
-	&=\bigcap_{l\leq k}\left(\Psi^{-l}\mathcal Z\vert_{\hat\theta}\underset{i\leq l-1}{\bigominus} 
+	&=\bigcap_{0\leq l\leq k}\left(\Psi^{-l}\mathcal Z\vert_{\hat\theta}\underset{0\leq i\leq l-1}{\bigominus} 
 	\Psi^i \mathcal V(\hat\theta)
@@
 The iteration terminates when $Z_k\subseteq Z_{k+1}$. As in section~\ref{sec:state:dep:MRPI}
-we will require $\mathcal Z\vert_{\hat\theta}$ to be contained in an observable band, i.e. that 
-the set $\{x:\mathcal Fx \leq {\bf{1}}-\mathcal G\hat\theta\}=\mathcal Z\vert_{\hat\theta}\subseteq
-\mathcal B=\{x:\Gamma x\leq {\bf{1}}\wedge -\Gamma x\leq {\bf{1}}\}$ for all $\hat\theta>-1$. We have the
+we will require $\mathcal Z\vert_{\hat\theta}$ to be contained in an observable band: $\mathcal Z\vert_{\hat\theta}=\{x:\mathcal Fx \leq {\bf{1}}-\mathcal G\hat\theta\}\subseteq
+\mathcal B=\{x:\Gamma x\leq {\bf{1}}\wedge -\Gamma x\leq {\bf{1}}\}$ for all $\hat\theta>-1$. We have the following result.
 %
@@
 in~\eqref{eq:parametrised:Dk} grows exponentially and therefore contains any compact set after a finite number
-of iterations. The fact that $\theta$ was fixed to $\hat\theta$ does not change anything since
-our argument is constructed for a fixed matrix $\Gamma$ where the rows had to be scaled by 
-$\frac{1}{1-\mathcal G_i\hat\theta}$ and we could rescale them to accommodate any other choice of $\hat\theta>-1$.
+of iterations. Fixing $\theta=\hat\theta$ does not affect the result since
+our argument is constructed for a fixed matrix $\Gamma$ with rows scaled by 
+$\frac{1}{1-\mathcal G_i\hat\theta}$; clearly we can re-scale the rows to accommodate any other choice of $\hat\theta>-1$.
 \end{proof}
-We now have a way to scale the the disturbance set uniformly, as mentioned earlier we can extend the algorithm
-to accommodate non uniformly parametrised input constraints to accommodate more degrees of freedom for 
-system analysis by simply using $\mathcal Z = \{(x,\theta,\alpha): \mathcal F x + \mathcal G\theta + 
-\mathcal H \alpha \leq {\bf{1}}\}$. This does not affect the algorithm since at each step of the iteration 
-the elements of $\mathcal H$ remain unchanged. In the next section we will illustrate the algorithm.
+
+The iterative process described above allows uniform scaling of the disturbance set.
+As mentioned earlier, the algorithm can be extended to the case of non-uniformly scaled input constraints to accommodate more degrees of freedom for
+system analysis simply by using 
+\[
+\mathcal Z = \{(x,\theta,\alpha): \mathcal F x + \mathcal G\theta + 
+\mathcal H \alpha \leq {\bf{1}}\}.
+\]
+This does not affect the algorithm since at each step of the iteration 
+the elements of $\mathcal H$ remain unchanged. 
+%In the next section we will illustrate the algorithm.
 %
@@
 %
-\section{Example}\label{sec:second:example}
+\section{Examples}\label{sec:second:example}
 %
 %
-In this section we compute the MRPI set for the levitating ball example system presented in 
-section~\ref{sec:first:example} as well as for a purely numerical model to illustrate both
-the effectiveness of the afore presented algorithm for state dependent disturbances as well as
-the system analysis tool that is the parametrised MRPI set. First we present the parametrised MRPI
-set for the levitating ball, notice that in order to obtain comparable results we need to get fixed bounds
-on the effect of nonlinearities on each state, i.e. a fixed set containing the set $\mathcal V(x,u)$ 
+In this section we compute MRPI sets for the levitating ball system presented in 
+section~\ref{sec:first:example} and for a purely numerical model.
+These examples illustrate the effectiveness of the proposed approach for state dependent disturbances and the use of parametrised MRPI sets as a system analysis tool.
+
+First we present the parametrised MRPI
+set for the levitating ball. To obtain results comparable to those in Section~\ref{sec:first:example} we derive fixed bounds
+on the effect of nonlinearities on each state by finding a fixed set containing the set $\mathcal V(x,u)$ 
 in~\eqref{eq:definition:element:wise:constraints:on:nonlinearities} for all $(x,u)\in\mathcal X\times\mathcal U$. 
-Using the same constraint set 
-$\mathcal X \times \mathcal U$ to determine the maximal and minimal values for nonlinear effects
-we obtain a constant set which is non symmetric around the origin due to nonlinearity. We also introduce
+%Using the same constraint set $\mathcal X \times \mathcal U$ to determine 
+This yields a constant set $\mathcal V$ which is non-symmetric around the origin due to nonlinearity. We also introduce
 a scaling parameter $\alpha$ such that $\mathcal U(0)=\mathcal U$ for $\alpha=0$. For this setup we obtain the MRPI
@@
 
-First we want to compare the MRPI set $\mathcal X^\infty$ obtained with state dependent disturbance 
-constraints with the parametrised one $\mathcal Z^\infty$. To do this we compute the scaling parameter 
-$\alpha_{\min}$ such that $\mathcal X^\infty\subseteq\mathcal Z^\infty\vert_{(\theta=0,\alpha=\alpha_{\min})}$.
-We can do this by solving $m_\infty$ linear programs
+First we compare the MRPI set $\mathcal X^\infty$ obtained with state dependent disturbance 
+constraints with the parametrised set $\mathcal Z^\infty$. To do this we compute the scaling parameter 
+$\alpha_{\min}$ such that $\mathcal X^\infty\subseteq\mathcal Z^\infty\vert_{(\alpha=\alpha_{\min},\theta=0)}$
+by solving $m_\infty$ linear programs
 %
@@
 \[
-	\gamma_i^\ast = \left\{\begin{split}
-	\max& \;\Lambda_i^x x\\
-	\text{s.t.}& \;x\in\mathcal X^\infty
-	\end{split}
-	\right.
+	\gamma_i^\ast = \begin{aligned}[t]
+	\max_x & \ \Lambda_i^x x\\
+	\text{s.t.}& \ x\in\mathcal X^\infty
+	\end{aligned}
 \]
@@
 planes.
-Caution is advised when interpreting $\alpha>0$, since the system is nonlinear extrapolations reveal very
-little insight, the only information we can safely extract is that the current set of inputs $\mathcal U(0)=\mathcal U$ 
+Caution is advised when interpreting $\alpha>0$, since the system is nonlinear.
+extrapolations reveal little insight, however $\alpha_{\min} > 1$ indicates that the current set of inputs $\mathcal U(0)=\mathcal U$ 
 is not large enough to cope with the perturbation set given by upper bounds of the nonlinear effects.
@@
 \end{lpic}
-\caption{Minimal scaling for MRPI set computed for constant disturbance which contains
- MRPI set for piecewise affine disturbances is $\alpha=1.7555$. Note that since the nonlinearities of the system
+\caption{The minimal scaling of the constant disturbance set such that the associated MRPI set contains
+the MRPI set for piecewise affine disturbances is $\alpha_{\min}=1.7555$. Note that since the nonlinearities of the system
  dynamics are not symmetrical around the equilibrium the MRPI set with fixed constraints on the disturbance
@@
 %
-All constraints were mainly chosen to be illustrative.
-We can now analyse the effect of changing individual constraints on the input by changing $\alpha$ as well as the
-effect of perturbations. To initialise the iteration we use
+The constraints of this example were chosen for  illustrative purposes.
+We now analyse the effects of changing individual constraints on the control input (by changing $\alpha$) as well as the
+effect of scaling the perturbations $w$ (through $\theta$). To initialise the iteration we use
 $\mathcal Z(x,\theta,\alpha) = \left\{(x,\theta,\alpha): Kx\in\mathcal U(\alpha)\wedge K_w x\in\mathcal W
-(\theta)\wedge \alpha,\theta>-{\bf{1}}\right\}$, with $K$ and $K_w$ being the solution to the aforementioned semidefinite program
+(\theta)\wedge \alpha,\theta>-{\bf{1}}\right\}$, for $K$ and $K_w$ satisfying the robust Lyapunov condition
 $x^TPx - ((A+BK)x+Dw)^TP((A+BK)x+Dw)\geq x^T(Q+K^TRK)x -\gamma^2 w^Tw$, i.e. $K_w = (\gamma^2-D^TPD)D^TP(A+BK)$.
@@
 $\mathcal Z^\infty$. After 22 iterations the algorithm terminates producing a total of 61 facets. 
-Notice that we not only know the sign of the elements of $\mathcal H$, but we also know that each facet of $\mathcal Z(x,\theta,\alpha)$
-depends at most on one $\alpha_i$, the algorithm does not affect the elements corresponding on $\alpha$ and reduction
-methods can not reduce rows depending on two individual variables, therefore we know that $\Lambda^\alpha$ will have at 
+By examining the conditions on $\mathcal H$ and the scaling parameters $\alpha$, it is possible to show that 
+$\Lambda^\alpha$ can have at 
 most one nonzero entry per row. We can therefore 
-compute which $\alpha_i$ will change the MRPI set the most. This can be done by element wise calculating
+compute which $\alpha_i$ will change the MRPI set the most. This can be done elementwise by calculating
 $$
-	\max_i  \frac{-\Lambda_i^\alpha}{\norm{\Lambda_i^x}_2}.
+	\max_i \  \frac{-\Lambda_i^\alpha}{\norm{\Lambda_i^x}_2}.
 $$
-In our example the greatest sensitivity corresponds to $\alpha_3$ with a numerical value of $2.6458\times 10^9$, 
+For this example the greatest sensitivity corresponds to $\alpha_3$ with a numerical value of $2.6458\times 10^9$, 
 i.e. the third input constraint.
-Analogous to the first example we might want to know how much disturbance the closed loop system can 
-take such that a given set is contained in the MRPI set $\mathcal C\subseteq\mathcal Z^\infty\vert_{(\theta,0)}$.
-We used the non-positivity of $\mathcal H$ to argue the non-positivity of $\Lambda^\alpha$, however we
-can not use a similar argument for $\Lambda^\theta$, in fact it is easy to see that both signs are likely to be 
-present in $\Lambda^\theta$. The condition $\theta>-1$ implies that $\Lambda^\theta$ has at least one negative
-element, on the other hand the elements of $\Lambda^\theta$ are given by $\mathcal G_i + \sum_{l\leq k}v_{l,i}^\ast$.
-We know $\mathcal G$ and hence we know that most entries are zero, so that $\Lambda^\theta$ has positive entries.
-Let $(\Lambda^1,\lambda^1)$ and $(\Lambda^2,\lambda^2)$ denote all rows such that $\Lambda^{1,\theta}>0$ and
+Similarly to the first example we might also want to know how much disturbance the closed loop system can tolerate such that a given set is contained in the MRPI set $\mathcal C\subseteq\mathcal Z^\infty\vert_{(0,\theta)}$.
+Although non-positivity of $\mathcal H$ implies non-positivity of $\Lambda^\alpha$, a similar argument cannot be applied to $\Lambda^\theta$.
+% , in fact it is easy to see that both signs are likely to be 
+% present in $\Lambda^\theta$. The condition $\theta>-1$ implies that $\Lambda^\theta$ has at least one negative
+% element, on the other hand the elements of $\Lambda^\theta$ are given by $\mathcal G_i + \sum_{l\leq k}v_{l,i}^\ast$.
+% We know $\mathcal G$ and hence we know that most entries are zero, so that $\Lambda^\theta$ has positive entries.
+Let $(\Lambda^1,\lambda^1)$ and $(\Lambda^2,\lambda^2)$ denote all rows of $\Lambda^\theta$ such that $\Lambda^{1,\theta}>0$ and
 $\Lambda^{2,\theta}\leq0$. This implies that for any fixed $\hat\alpha$ the set $\mathcal Z^\infty\vert_{\hat\alpha}$
@@
 $$
-	\gamma_i = \left\{\begin{array}{rl}
-	\max& \Lambda^{1,x}x\\
+	\gamma_i = \begin{array}[t]{rl}
+	\displaystyle\max_x& \Lambda^{1,x}x\\
 	\text{s.t.}& x\in\mathcal C
 	\end{array}
-	\right.\;
-	\delta_i = \left\{\begin{array}{rl}
-	\max& \Lambda^{2,x}x\\
+	\qquad
+	\delta_i = \begin{array}[t]{rl}
+	\displaystyle\max_x& \Lambda^{2,x}x\\
 	\text{s.t.}& x\in\mathcal C
 	\end{array}
-	\right. .
+	.
 $$
@@
 The numerical values for the example are given by $[\theta_{\min},\theta_{\max}]=[-0.9999,6.2582]$.
-A two and three dimensional illustration of the parametrised MRPI set is given in Figure~\ref{fig:two:dim:example}
+Two- and three-dimensional illustrations of the parametrised MRPI set are given in Figure~\ref{fig:two:dim:example}
 and~\ref{fig:three:dim:example} respectively.
@@
 \centerline{\includegraphics[scale=0.6]{twoDimensional}}
-\caption{The extremal MRPI sets $\mathcal Z^\infty\vert_{({\bf{0}},\theta_{min})}$ and $\mathcal Z^\infty
-\vert_{({\bf{0}},\theta_{\max})}$ containing the unit box.}
+\caption{The extremal MRPI sets $\mathcal Z^\infty\vert_{(0,\theta_{min})}$ and $\mathcal Z^\infty
+\vert_{(0,\theta_{\max})}$ containing the unit box.}
 \label{fig:two:dim:example}
@@
 \centerline{\includegraphics[scale=0.6]{threeDimensional}}
-\caption{The parametrised MRPI set for $\alpha={\bf{0}}$. Containing the unit box in the 
+\caption{The parametrised MRPI set for $\alpha=0$. Containing the unit box in the 
 interior between $\theta_{\min}$ and $\theta_{\max}$.}
@@
 %
-In this paper we discussed extensions to existing computational methods to determine MRPI sets
-for linear systems subject to additive disturbance in two cases. The case of state dependent case
-which can be applied to determine approximations to MRPI sets for linearised nonlinear systems as was shown
-for the example of a levitating ball system. We also introduced the computation of MRPI sets using 
-scaling parameters which allows various system analyses using uniform scaling for the disturbance sets
-and non-uniform scaling for the input constraints. The effectiveness of state dependent disturbance
-sets was demonstrated by comparing the two MRPI methods.
-\bibliographystyle{IEEEtran}
-\bibliography{IEEEabrv,MyLib}
+In this paper we discussed extensions to existing computational methods to determine MRPI sets for linear systems subject to additive disturbance for two descriptions of the sets bounding unknown additive disturbances.
+The case of state dependent disturbances was considered, and applied to the problem of determining approximations to MRPI sets for linearised nonlinear systems.
+This was illustrated using the example of a magnetic levitation system.
+Secondly the computation of MRPI sets for systems with disturbance and control inputs bounded by scaled sets was considered.
+This enables system analyses based on uniform scaling applied to disturbance sets and non-uniform scaling of input constraints.
+A comparison of the two approaches shows the effectiveness of the method based on state dependent disturbance sets.
+
+\bibliographystyle{IEEEtran} \bibliography{IEEEabrv,MyLib}
 %

### 2015-03-20 draft.tex
Edited section IV - linearised model and derivation of linearisation errors.

@@
 \begin{equation}
-D_k = \underbrace{\Psi^{-k}\mathcal X_0}_{=\mathcal S_1} \ominus \underbrace{\left(\bigoplus_{i\leq k-1} 
-\Psi^i\mathcal V(\mathcal X_k)\right)}_{=\mathcal S_2}.
+D_k = \underbrace{\Psi^{-k}\mathcal X_0}_{=\mathcal S_1} \ominus \underbrace{\biggl(\bigoplus_{i\leq k-1} 
+\Psi^i\mathcal V(\mathcal X_k)\biggr)}_{=\mathcal S_2}.
 \end{equation}
@@
 For illustration purposes we neglect inductive dynamics and use the current $u=i$ as an input and the position
-$y$ and its first derivative $\dot y$ as the states, i.e. $x = (y,\dot y)^T$. We find that an equilibrium
-is present when $x_2=0$ and $u=\sqrt{\frac{gm}{c}}x_1$ for any positive position $x_1>0$.
-Linearising the nonlinear differential equation $\dot x = f(x,u)$ around $\hat x, \hat u$ we obtain the linear approximation
+$y$ and its first derivative $\dot y$ as the states, i.e. $x = (y,\dot
+y)^T$. We find that any equilibrium has $\dot{y}=0$ and
+$u=\sqrt{\frac{gm}{c}} y$ for any positive position $y>0$.
+Linearising the nonlinear differential equation $\dot x = f(x,u)$
+around an equilibrium point $(\hat x, \hat u)$ 
+%such that $f(\hat x,\hat u) = 0$, 
+gives the approximate model 
 %
 \begin{equation}
-	\Delta \dot x = \underbrace{\left(\begin{array}{cc}
+	 \dot{\tilde{x}} \approx \underbrace{\left(\begin{array}{cc}
 	0 & 1 \\ \frac{2c\hat u^2}{m\hat x_1^3} & 0
-	\end{array}\right)}_{\frac{\partial f}{\partial x}(\hat x,\hat u)}\Delta x + \underbrace{\left(\begin{array}{c}
+	\end{array}\right)}_{\frac{\partial f}{\partial x}(\hat x,\hat
+      u)}\tilde x 
++ \underbrace{\left(\begin{array}{c}
 	0 \\ - \frac{2c\hat u}{m\hat x_1^2}
-	\end{array}\right)}_{\frac{\partial f}{\partial u}(\hat x,\hat u)}\Delta u.
+	\end{array}\right)}_{\frac{\partial f}{\partial u}(\hat x,\hat
+      u)}\tilde u
 \end{equation}
 %
-We derive discrete time system dynamics using the explicit Euler formula $x^+=x+T_s f(x,u) =:\tilde f(x,u)$,
-with the sampling rate $T_s$. Hence we define the system matrix $A = (I+T_s\frac{\partial f}{\partial x}(\hat x,\hat u))$
-and the input matrix $B = T_s \frac{\partial f}{\partial u}(\hat x,\hat u)$. 
-Notice that using a non-autonomous model does not affect our analysis since we analyse the closed loop system
-governed by a linear state feedback controller $u=Kx$. We choose $K$ as the solution of the robust Lyapunov condition $V(x)-V((A+BK)x+Dw)\leq \gamma^2w^Tw$ with $V(x)=x^T P x\geq0$, i.e.
-$x^TPx - ((A+BK)x+Dw)^TP((A+BK)x+Dw)\geq x^T(Q+K^TRK)x -\gamma^2 w^Tw$ for a minimised $\gamma^2$, 
-see e.g.~\cite{Boyd:94}.
-A representation of additive disturbances that act on the state of the linearised model as a result of the linearisation error can be obtained using the mean-value theorem for vector valued functions (e.g.~\cite{Apostol:1974}):
+where $\tilde{x} = x-\hat{x}$, $\tilde{u} = u -\hat{u}$.
+We derive the discrete time dynamics with sampling rate $T_s$ using
+the Euler formula $x^+=x+T_s f(x,u) =:\tilde f(x,u)$ giving
+\[
+\tilde{x}^+ \approx A \tilde{x} + B \tilde{u}, \quad
+\Biggl\{\begin{aligned} A &= I+T_s\frac{\partial f}{\partial  x}(\hat
+  x,\hat u) \\
+B &= T_s \frac{\partial f}{\partial u}(\hat x,\hat u)
+\end{aligned}
+\]
+Although this system has a control input, the algorithm for computing the
+MRPI set is applicable since we consider the closed loop system under
+linear feedback  $u=Kx$, where $K$ satisfies the robust Lyapunov condition $V(x)-V((A+BK)x+Dw)\leq \gamma^2w^Tw$ with $V(x)=x^T P x\geq0$, i.e.
+$x^TPx - ((A+BK)x+Dw)^TP((A+BK)x+Dw)\geq x^T(Q+K^TRK)x -\gamma^2 w^Tw$
+for a minimum  $\gamma^2$, see e.g.~\cite{Boyd:94}.
+A representation of disturbances acting on the linearised
+model due to linearisation errors can be obtained using the
+Mean Value Theorem for vector-valued functions (e.g.~\cite{Apostol:1974}).
 %
@@
 \begin{thm}[Mean Value Theorem]\label{thm:mean:value:theorem}
-Let $\mathcal X\subset\mathbb R^n$ be open, $g : \mathcal X \rightarrow\mathbb R^m$ continuously differentiable, 
-and $x \in\mathcal X, h \in\mathbb R^n$ vectors such that the 
-whole line segment $x + th$ remains in $\mathcal X$ for $0 \leq t \leq 1$. Then
+Let $g : \mathcal X \rightarrow\mathbb R^m$ be continuously
+differentiable, $\mathcal X\subset\mathbb R^n$ be open,
+and $x \in\mathcal X$, $h \in\mathbb R^n$ be such that 
+$x + th \in\mathcal X$ for all $t\in [0 ,1]$. Then
 \begin{equation}
@@
 %
-Using the Mean Value Theorem~\ref{thm:mean:value:theorem}
-and the linearisation for $\Delta x = \hat x + \tilde x$ and $\Delta u = \hat u + \tilde u$ we
-get the successor state:
+Using the Mean Value Theorem
+and the linearisation around $(\hat{x},\hat{u})$, we obtain the successor state:
 %
-\begin{equation}
-	\begin{split}
-	\Delta x^+ = \underbrace{\tilde f(\hat x, \hat u)}_{\hat x} + \int_0^1\frac{\partial\tilde 
-	f}{\partial x}(\hat x + t\tilde x
-	,\hat u + t\tilde u)dt\cdot \tilde x +\\
-	 \int_0^1\frac{\partial\tilde f}{\partial u}(\hat x + t\tilde x
-	,\hat u + t\tilde u)dt\cdot \tilde u + A \tilde x + B \tilde u - A \tilde x - B\tilde u\\
-	\Leftrightarrow \tilde x^+ = A\tilde x + B \tilde x +\left(
-	\int_0^1\frac{\partial\tilde f}{\partial x}(\hat x + t\tilde x,\hat u + t\tilde u)dt - A
-	\right)\tilde x + \\ \left(
-	\int_0^1\frac{\partial\tilde f}{\partial u}(\hat x + t\tilde x,\hat u + t\tilde u)dt - B
-	\right)\tilde u
-	\end{split}
-\end{equation}
+\begin{align*}
+x^+ &= \tilde{f}(\hat{x} + \tilde{x},\hat{u} + \tilde{u}) 
+\\
+&= \tilde f(\hat x, \hat u) 
++ \int_0^1\frac{\partial\tilde f}{\partial x}(\hat x + t\tilde x,
+\hat u + t\tilde u) dt \cdot \tilde x  \\
+&\quad + \int_0^1\frac{\partial\tilde f}{\partial u}(\hat x + t\tilde x,\hat u+
+t\tilde u) dt\cdot \tilde u \\
+%+ A \tilde x + B \tilde u - A \tilde x - B\tilde u\\
+\Leftrightarrow 
+\tilde x^+ &= A\tilde{x} + B \tilde{u} +\Bigl(
+\int_0^1\frac{\partial\tilde f}{\partial x}(\hat x + t\tilde x,\hat u
+             + t\tilde u)dt - A \Bigr)\tilde x 
+\\ 
+&\quad +\Bigl(\int_0^1\frac{\partial\tilde f}{\partial u}(\hat x + t\tilde x,\hat u + t\tilde u)dt - B\Bigr)\tilde u
+\end{align*}
 %
-Thus for any state $\tilde x=\Delta x - \hat{x}$ we obtain the (exact) dynamics
-$\tilde x^+ = A\tilde x+B\tilde u + H^x\tilde x + H^u \tilde u$, however the computation
-of $H^x$ and $H^u$ requires solving a nonlinear integral. Suppose that
+This implies the dynamics
+\[
+\tilde x^+ = A\tilde x+B\tilde u + H^x\tilde x + H^u \tilde u, 
+\]
+where
+$H^x$ and $H^u$ can be determined by integration. Suppose that
 for $x\in\mathcal X$ and $u\in\mathcal U$, where $\mathcal X$ and $\mathcal U$ are compact
-sets, we have extremal values of $H^x$ and $H^u$, i.e.
+sets, the values of $H^x$ and $H^u$ are known, i.e.\
 $H^x\tilde x+H^u\tilde u\in\conv_k\{H^x_k\tilde x + H^u_k\tilde u\}$ for all $(\tilde x,\tilde u)\in\mathcal X\times \mathcal U$.
@@
 %
-\begin{equation}\label{eq:definition:element:wise:constraints:on:nonlinearities}
-\begin{split}
-\mathcal V(x,u)=\left\{v:\min_k\{
-H^x_{k,i}x+H^u_{k,i}u\}\leq v_i\,\wedge\right. \\ \left.v_i \leq \max_k\{H^x_{k,i}x+H^u_{k,i}u\}, \, i =1,\dots,n\right\}.
-\end{split}
-\end{equation}
+\begin{multline}\label{eq:definition:element:wise:constraints:on:nonlinearities}
+\mathcal V(x,u)=\biggl\{v:\min_k\{
+H^x_{k,i}x+H^u_{k,i}u\}\leq v_i\,\wedge 
+\\ 
+v_i \leq \max_k\{H^x_{k,i}x+H^u_{k,i}u\}, \, i =1,\dots,n\biggr\}.
+\end{multline}
 %
@@
 $\Lambda^{2,\theta}\leq0$. This implies that for any fixed $\hat\alpha$ the set $\mathcal Z^\infty\vert_{\hat\alpha}$
-is compact, since $\mathcal Z^\infty\vert_{(\hat\alpha,\hat\theta)}$ is compact and there exists a maximal $\theta_{\max}$
-such that $\Lambda^{1,x}x+\Lambda^{1,\alpha}\hat\alpha+\Lambda^{1,\theta}\theta\leq\lambda^1$ can be satisfied
-analogue there is a minimal $\theta_{\min}$. We can solve the optimisation programs
+is compact, and since $\mathcal Z^\infty\vert_{(\hat\alpha,\hat\theta)}$
+is compact, there exist a maximal $\theta_{\max}$ and likewise a minimal $\theta_{\min}$
+such that $\Lambda^{1,x}x+\Lambda^{1,\alpha}\hat\alpha+\Lambda^{1,\theta}\theta\leq\lambda^1$ can be satisfied. We can solve the optimisation programs
 $$

### 2015-03-20 draft.tex
Convexity inserted.

--- 2015-03-19 draft.tex
@@
 set~\eqref{eq:definition:MRPI:set:state:dependent} for a linear system~\eqref{eq:system:equation} subject to disturbance
-$v\in\mathcal V(x)$ where $\mathcal V(x)$ is a parametrically convex point-to-set map defined by~\eqref{eq:PWA:distrubance:set} with a piecewise affine $H(x)$.
+$v\in\mathcal V(x)$ where $\mathcal V(x)$ is a parametrically convex point-to-set map defined 
+by~\eqref{eq:PWA:distrubance:set} with a convex piecewise affine $H(x)$.
 Notice that the set $\mathcal V(x)$ is pointwise polytopic 

### 2015-03-21 draft.tex
Made my changes.

--- 2015-03-20 draft.tex
@@
 were introduced much later~\cite{Blanchini:1994,DeSantis:1994,Kolmanovsky:1998}. 
-%\note{You commented 'check', I didn't know what that meant.}
 Earlier algorithms did not guarantee finite determinability of $\mathcal X^\infty$, see e.g.~\cite{Blanchini:1990}, 
@@
 where $G$ is a real matrix,
-%$G\in\mathbb R^{n_G\times n_v}$, 
 $H(x)$ is a convex piecewise affine function, and the inequality applies elementwise. For the case that $\mathscr V=\mathcal V(x)$ we
@@
 $(x\times\theta)$-space with the property that 
-% To distinguish the resulting sets from regular MRPI sets we use $\mathcal Z^\infty$
-% to emphasise that $\mathcal Z^\infty$ 
 the intersection, $\mathcal Z^\infty\vert_{\hat\theta}$, with the subspace on which $\theta=\hat\theta$ 
@@
 
-Throughout this paper we refer to sets that can be represented as intersections of finite numbers of half spaces as polyhedra, and to bounded polyhedra as polytopic sets.
-For sets $\mathcal A, \mathcal B \subset\mathbb R^n$, the Minkowski set addition is denoted $\mathcal A\oplus\mathcal B = \{c : c = a + b\; \forall\,a\in\mathcal A,\, b\in\mathcal B\}$.
-We use ${\bf{1}}$ to denote the column vector of ones in appropriate dimensions, and $\wedge$ is the logical AND operator. 
+Throughout this paper we refer to sets that can be represented as intersections of finite numbers of half 
+spaces as polyhedra, and to bounded polyhedra as polytopic sets. For sets $\mathcal A, \mathcal B 
+\subset\mathbb R^n$, the Minkowski set addition is denoted $\mathcal A\oplus\mathcal B = \{c : c = a + 
+b\; \forall\,a\in\mathcal A,\, b\in\mathcal B\}$. We use ${\bf{1}}$ to denote the column vector of ones 
+in appropriate dimensions, and $\wedge$ is the logical AND operator, index sets are denoted by $\mathcal I
+\subset\mathbb N$. 
 %
@@
 \section{Parametrically convex set operations}\label{sec:parametrically:convex:set:operations}
-This section discusses sets that depend on a parameter such as the state of \eqref{eq:system:equation} (so called point-to-set maps, 
-see~\cite{Hogan:1973}), and extends the existing set algebra~\cite{blanchini:2007} to 
-accommodate such sets. We present the general case first, then illustrate it with the example of a pointwise polyhedral set in the form of (\ref{eq:PWA:disturbance:set})
-% with piecewise affine $H(x)$.
+This section discusses sets that depend on a parameter such as the state of \eqref{eq:system:equation} 
+(so called point-to-set maps, see~\cite{Hogan:1973}), and extends the existing set algebra~\cite{blanchini:2007} to 
+accommodate such sets. We present the general case first, then illustrate it with the example 
+of a pointwise polyhedral set in the form of (\ref{eq:PWA:disturbance:set})
 %
@@
     \end{defn}
-%
-% In (\ref{eq:pconvexdef}), $\oplus$ denotes the Minkowski set addition
-%       \begin{equation}
-%         \mathcal A\oplus\mathcal B = \{c : c = a + b\; \forall\,a\in\mathcal A,\, b\in\mathcal B\}.
-%       \end{equation}
 %
@@
 by definition of the parametric Pontryagin difference, we have
-\[%      \begin{equation}
+%
+\[
         \{z_i\} \oplus T(z_i) \subseteq S,\; i=1,2.
-\]%      \end{equation}
+\]
+%
 To see that $ Z$ is convex we show that line segments between
@@
 \end{aligned}\]
+%
 where the last inclusion follows from the convexity of $\mathcal S$.
@@
   The point-to-set map $\mathcal V (x)$ defined by~\eqref{eq:PWA:disturbance:set} is parametrically 
-      convex for all $x\in \mathcal X$ if $H(x)$ is elementwise convex in $x\in \mathcal X\subset \mathbb R^n$ (i.e.~if each element $H_i(x)$ of $H(x)$ satisfies
-    $H_i(\lambda x_1+(1-\lambda)x_2)\leq \lambda H_i(x_1)+(1-\lambda)H_i(x_2)$ for all    $\lambda\in[0,1]$ and $x_1, x_2\in\mathcal X$).
+  convex for all $x\in \mathcal X$ if $H(x)$ is elementwise convex in $x\in \mathcal X\subset 
+  \mathbb R^n$ (i.e.~if each element $H_i(x)$ of $H(x)$ satisfies $H_i(\lambda x_1+(1-\lambda)x_2)\leq 
+  \lambda H_i(x_1)+(1-\lambda)H_i(x_2)$ for all    $\lambda\in[0,1]$ and $x_1, x_2\in\mathcal X$).
 \end{thm}
-    % \begin{thm}\label{thm:convex:parametric:set}
-    %   The point-to-set map $\mathcal V (x)$ defined by~\eqref{eq:PWA:disturbance:set} for a function $H(x)$ that is elementwise convex in $x\in \mathcal X\subset \mathbb R^n$ (i.e.~each element $H_i(x)$ of $H(x)$ satisfies
-    % $H_i(\lambda x_1+(1-\lambda)x_2)\leq \lambda H_i(x_1)+(1-\lambda)H_i(x_2)$ for all    $\lambda\in[0,1]$ and $x_1, x_2\in\mathcal X$) is parametrically 
-    %   convex for all $x\in \mathcal X$.
-    % \end{thm}
 %
 \begin{proof}
-      To show that $\mathcal V(\lambda x_1 + (1-\lambda)x_2)\subseteq 
-      \lambda\mathcal V(x_1) \oplus(1-\lambda)\mathcal V(x_2)$ for all $\lambda \in [0,1]$ and $x_1, x_2\in\mathcal X$ we note that
+To show that $\mathcal V(\lambda x_1 + (1-\lambda)x_2)\subseteq \lambda\mathcal V(x_1) \oplus(1-\lambda)
+\mathcal V(x_2)$ for all $\lambda \in [0,1]$ and $x_1, x_2\in\mathcal X$ we note that
+%
 \begin{align*}
@@
 \def\genmat{\Xi} \def\genvec{\xi}
-% Lemmas~\ref{thm:convexity:of:pontryagin:difference} 
-% and~\ref{thm:convex:parametric:set} imply that the parametric Pontryagin difference between a convex set $\mathcal X$ and 
-% the point-to-set map $\mathcal V(x)$, i.e. $\mathcal X\ominus \mathcal V(\mathcal X)$, is a convex set.
-% Furthermore, we will see that if $\mathcal X$ is polytopic and $\mathcal 
-% V(x)$ is pointwise polytopic, then $\mathcal X\ominus\mathcal V(\mathcal X)$ is 
-% again a polytopic set. This will become more clear in the next section when we describe 
-% the computation of the MRPI set~\eqref{eq:definition:MRPI:set:state:dependent}.
-%
-Lemmas~\ref{thm:convexity:of:pontryagin:difference} 
-and~\ref{thm:convex:parametric:set} imply that, if $\mathcal V(x)$ is defined by \eqref{eq:PWA:disturbance:set} in terms of an elementwise convex function $H(x)$, then the parametric Pontryagin difference $\mathcal X\ominus \mathcal V(\mathcal X)$
+Lemmas~\ref{thm:convexity:of:pontryagin:difference} and~\ref{thm:convex:parametric:set} imply that, 
+if $\mathcal V(x)$ is defined by \eqref{eq:PWA:disturbance:set} in terms of an elementwise convex 
+function $H(x)$, then the parametric Pontryagin difference $\mathcal X\ominus \mathcal V(\mathcal X)$
 is a convex set.
@@
 also a polytope. 
-%This will become more clear in the next section when we describe 
-%the computation of the MRPI set~\eqref{eq:definition:MRPI:set:state:dependent}.
 %
@@
 \section{Maximal Robust Positively Invariant Sets for State Dependent Disturbance}\label{sec:state:dep:MRPI}
-In this section we describe an iterative algorithm to compute the MRPI 
-set~\eqref{eq:definition:MRPI:set:state:dependent} for a linear system~\eqref{eq:system:equation} subject to disturbances
-$v\in\mathcal V(x)$ where $\mathcal V(x)$ is a parametrically convex point-to-set map defined by~\eqref{eq:PWA:disturbance:set} with a piecewise affine function $H(x)$.
+In this section we describe an iterative algorithm to compute the MRPI set~\eqref{eq:definition:MRPI:set:state:dependent} 
+for a linear system~\eqref{eq:system:equation} subject to disturbance
+$v\in\mathcal V(x)$ where $\mathcal V(x)$ is a parametrically convex point-to-set map defined 
+by~\eqref{eq:PWA:distrubance:set} with a convex piecewise affine $H(x)$.
+Notice that the set $\mathcal V(x)$ is pointwise polytopic set~\eqref{eq:definition:MRPI:set:state:dependent} 
+for a linear system~\eqref{eq:system:equation} subject to disturbances
+$v\in\mathcal V(x)$ where $\mathcal V(x)$ is a parametrically convex point-to-set map defined 
+by~\eqref{eq:PWA:disturbance:set} with a convex piecewise affine function $H(x)$.
 We assume (without loss of generality) that the set $\mathcal V(x)$ is pointwise compact and polytopic 
-%\note{is it necessary to assume that $\mathcal V(x)$ is bounded $\forall x\in\mathcal X_0$?}
 for finite $x\in\mathcal X_0$ and can hence be represented as the 
@@
 recursively \emph{cut off} points that cannot satisfy the invariance condition~\eqref{eq:definition:MRPI:set:state:dependent}
-%\emph{cut off} all points that do not satisfy the invariance condition in $k$ steps, $k\in\mathbb N$. 
-%So that all points remaining satisfy the invariance condition~\eqref{eq:definition:MRPI:set:state:dependent}
-by iteratively introducing
-constraints that exclude all points for which the successor state can lie outside 
+by iteratively introducing constraints that exclude all points for which the successor state can lie outside 
 $\mathcal X_0$. The first iteration enforces the constraint:
 %
-\[%\begin{equation}
+\[
 \begin{split}
@@
 \end{split}
-\]%\end{equation}
+\]
 %
@@
 Notice that $v_{0,i}^\ast(x)$ is not necessarily given by a unique maximiser, 
-but is the solution of a multiparametric linear program and hence will be given 
+but is the solution of a multi-parametric linear program and hence will be given 
 by a vertex $v_i(x)$ of $\mathcal V(x)$ for each $x$ on that facet.
@@
 %
-\[%\begin{equation}
+\[
 	\mathcal X_{k+1} = \mathcal X_k\cap \{x:\genmat_{0,i}\Psi^k x + \sum_{l=0}^{k-1}v_{l,i}^\ast(x)
 	\leq\genvec_{0,i}\,\forall i\in\mathcal I_0\},
-\]%\end{equation}
+\]
 %
@@
 %
-%\begin{equation}
 \begin{align*}
 	v_{l,i}^\ast(x)&=\max_j \ \genmat_{0,i}\Psi^{l-1}v_j(x)
-	 = \begin{array}[t]{rl} \displaystyle\max_v & \genmat_{0,i}\Psi^{l-1}v \\ \text{s.t.}& v\in\mathcal V(x)\end{array} \\
-	 &= \begin{array}[t]{rl} \displaystyle\max_{\tilde v} & \genmat_{0,i}\tilde v\\ \text{s.t.}& \tilde v\in \Psi^{l-1}\mathcal V(x) \end{array}
+	 = \begin{array}[t]{rl} \displaystyle\max_v & \genmat_{0,i}\Psi^{l-1}v \\ \text{s.t.}& v\in\mathcal V(x)
+   \end{array} \\ 
+   &= \begin{array}[t]{rl} \displaystyle\max_{\tilde v} & \genmat_{0,i}\tilde v\\ \text{s.t.}& \tilde v\in 
+   \Psi^{l-1}\mathcal V(x) \end{array}
 \end{align*}
-%\end{equation}
 %
-In closed form the iterates can be expressed (assuming for convenience that $\Psi$ is invertible) as
+In closed form the iterates can be expressed as
+\note{We actually do NOT assume that $\Psi$ is invertible! We don't need its inverse at any point! $\Psi^{-1}$ appears only
+in this closed form representation but it merely denotes the preimage of $\mathcal X_k$ because that is all we need that the preimages
+keep growing. It might be confusing with the notation but that is only to emphasise that it behaves like the inverse..}
 %
@@
 	=\mathcal X_k\cap D_k \\
-	=& \bigcap_{0\leq l\leq k+1}\left( \Psi^{-l} \mathcal X_0 \underset{0 \leq i\leq l-1}{\bigominus} \Psi^i \mathcal V(\mathcal X_{l-1})\right).
+	=& \bigcap_{0\leq l\leq k+1}\left( \Psi^{-l} \mathcal X_0 \underset{0 \leq i\leq l-1}{\bigominus} 
+  \Psi^i \mathcal V(\mathcal X_{l-1})\right).
 \end{split}\end{equation}
@@
 Let the state constraint set $\mathcal X_0$ be contained in a band: $\mathcal X_0\subseteq B=\{x:\Gamma x\leq{\bf{1}}\wedge 
--\Gamma x\leq{\bf{1}}\}$, let the pair $(\Psi,\Gamma)$ be observable and let $\mathcal V(x)$ be defined by~\eqref{eq:PWA:disturbance:set}
-in terms of a piecewise affine function $H(x)$.
-Then $\mathcal X_N\subseteq \mathcal X_{N+1}$ for a finite $N$, and hence the MRPI set $\mathcal X^\infty 
-=\mathcal X_N$ is a polytope.
+-\Gamma x\leq{\bf{1}}\}$, let the pair $(\Psi,\Gamma)$ be observable and let $\mathcal V(x)$ be defined 
+by~\eqref{eq:PWA:disturbance:set} in terms of a piecewise affine function $H(x)$. Then $\mathcal X_N\subseteq \mathcal 
+X_{N+1}$ for a finite $N$, and hence the MRPI set $\mathcal X^\infty =\mathcal X_N$ is a polytope.
 \end{thm}
@@
 \begin{proof}
-From~\eqref{eq:set:iteration:state:dependent:constraints} it is clear that $\mathcal X^\infty = \emptyset$ if $\mathcal X_k =\emptyset$ for any $k\geq 0$.
-%Notice that with~\eqref{eq:set:iteration:state:dependent:constraints} it is easy to see that in early iterations the parametric Pontryagin difference can yield the empty set.
-The empty set however is an admissible polytope, i.e.
-an admissible MRPI set.
-For the remainder of the proof we assume
-that the MRPI set $\mathcal X^\infty$ is non-empty. For this we require that $\bigcup_{s\in\mathcal S}\mathcal V(s)$ is compact on any compact set $\mathcal S\subset\mathbb R^n$.
+From~\eqref{eq:set:iteration:state:dependent:constraints} it is clear that $\mathcal X^\infty = \emptyset$ 
+if $\mathcal X_k =\emptyset$ for any $k\geq 0$. For the remainder of the proof we assume that the MRPI set 
+$\mathcal X^\infty$ is non-empty. For this we require that $\bigcup_{s\in\mathcal S}\mathcal V(s)$ is 
+compact on any compact set $\mathcal S\subset\mathbb R^n$.
 
@@
 
-For the first step, notice that observability of
-$(\Psi,\Gamma)$ is equivalent to the observability matrix $\Omega$ having full rank, i.e.\ $\mathrm{rank}(\Omega) = \mathrm{rank}(\begin{bmatrix} \Gamma^T \ \cdots \ (\Gamma\Psi^{n-1})^T\end{bmatrix}) = n$.
-% \[
-% \Omega = \left(\begin{array}{c}
-% \Gamma\\ \vdots \\ \Gamma\Psi^{n-1}
-% \end{array}\right)
-% \]
-%having a trivial kernel. 
+For the first step, notice that observability of $(\Psi,\Gamma)$ is equivalent to the observability matrix 
+$\Omega$ having full rank, i.e.\ $\mathrm{rank}(\Omega) = \mathrm{rank}(\begin{bmatrix} \Gamma^T \ \cdots \ 
+(\Gamma\Psi^{n-1})^T\end{bmatrix}) = n$.
+\note{This looks very MATLAB.. I don't like it.}
 But  this implies that the set 
+%
 \[
@@
 \]
+%
 is bounded, and since $\mathcal X_k\subseteq \mathcal P_k$ for all $k$, 
-the set $\mathcal X_{n}$ is also bounded. 
-%The case that  $N<n$ can occur if $\mathrm{rank}(\Gamma) > 1$.
-%More generally, to 
-To show that $D_k$ grows exponentially we use the compactness of $\mathcal V(\mathcal X_{n})$. Let $K_1$ denote the smallest ball that contains $\mathcal V(\mathcal X_{n})$ and let
+the set $\mathcal X_{n}$ is also bounded. To show that $D_k$ grows exponentially we use the compactness 
+of $\mathcal V(\mathcal X_{n})$. Let $K_1$ denote the smallest ball that contains $\mathcal V(\mathcal X_{n})$ and let
 $\rho$ denote the spectral radius of $\Psi$. Furthermore, let $K_2$
-be the biggest ball that is contained in $\mathcal X_{0}$. From~\eqref{eq:set:iteration:state:dependent:constraints}, $D_k$ has the representation
+be the biggest ball that is contained in $\mathcal X_{0}$. From~\eqref{eq:set:iteration:state:dependent:constraints}, 
+$D_k$ has the representation
+%
 \begin{equation}
@@
 \end{equation}
-Since $\Psi$ is asymptotically stable we have $\rho<1$ and therefore
-$\rho^{-l}K_1\subseteq\Psi^{-l} K_1 \subseteq \Psi^{-l}\mathcal X_0 = \mathcal S_1$,
-implying exponential growth of $D_k$ provided $\mathcal S_2$ is bounded. 
-%Recall that we assume
-%However the MRPI set is non-empty by assumption, and t
-To bound $\mathcal S_2$ we note that for $k\geq n$ we have $\mathcal S_2\subseteq \bigoplus_{0\leq i\leq k-1} \rho^i K_2 \subseteq
-\frac{1}{1-\rho} K_2$.
-Thus $D_k$ grows exponentially,
-whereas $\mathcal X_k$ is contained in a ball of
-finite radius, and hence we conclude from \eqref{eq:set:iteration:state:dependent:constraints} that 
+%
+Since $\Psi$ is asymptotically stable we have $\rho<1$ and therefore $\rho^{-l}K_1\subseteq\Psi^{-l} K_1 
+\subseteq \Psi^{-l}\mathcal X_0 = \mathcal S_1$, implying exponential growth of $D_k$ provided $\mathcal S_2$ 
+is bounded. To bound $\mathcal S_2$ we note that for $k\geq n$ we have $\mathcal S_2\subseteq 
+\bigoplus_{0\leq i\leq k-1} \rho^i K_2 \subseteq \frac{1}{1-\rho} K_2$. Thus $D_k$ grows exponentially, whereas 
+$\mathcal X_k$ is contained in a ball of finite radius, and hence we conclude from~\eqref{eq:set:iteration:state:dependent:constraints} that 
 $\mathcal X_{k+1} = \mathcal X _k$ for all $k\geq N$ and therefore $\mathcal X _N = \mathcal X^\infty$ for finite $N$.
-%after a finite number of iterations $N$ intersecting with $D_{N+1}$
-%will no longer change $\mathcal X_N$.
 \end{proof}
@@
 %
-In this section we discuss the calculation of the MRPI set for a linearised simplified model of the magnetic levitation system depict in figure~\ref{fig:levitating:ball}.
-The system dynamics for the ball are given
+In this section we discuss the calculation of the MRPI set for a linearised simplified model of the magnetic 
+levitation system depict in figure~\ref{fig:levitating:ball}. The system dynamics for the ball are given
 by $m \ddot y = m g - c\frac{i^2}{y^2}$, where $m,g,c,i$ and $y$ denote the mass of the ball, the gravitational
@@
 For illustration purposes we neglect inductive dynamics and use the current $u=i$ as an input and the position
-$y$ and its first derivative $\dot y$ as the states, i.e. $x = (y,\dot
-y)^T$. We find that any equilibrium has $\dot{y}=0$ and
-$u=\sqrt{\frac{gm}{c}} y$ for any positive position $y>0$.
-Linearising the nonlinear differential equation $\dot x = f(x,u)$
-around an equilibrium point $(\hat x, \hat u)$ 
-%such that $f(\hat x,\hat u) = 0$, 
-gives the approximate model 
+$y$ and its first derivative $\dot y$ as the states, i.e. $x = (y,\dot y)^T$. We find that any equilibrium has 
+$\dot{y}=0$ and $u=\sqrt{\frac{gm}{c}} y$ for any positive position $y>0$. Linearising the nonlinear differential 
+equation $\dot x = f(x,u)$ around an equilibrium point $(\hat x, \hat u)$ gives the approximate model 
 %
@@
 %
+\note{I find the $x^+\approx Ax+Bu$ notation very misleading! I prefer $=$ since we 
+will take it as an equality after all not handling discretisation errors at all..}
 where $\tilde{x} = x-\hat{x}$, $\tilde{u} = u -\hat{u}$.
@@
 MRPI set is applicable since we consider the closed loop system under
-linear feedback  $u=Kx$, where $K$ satisfies the robust Lyapunov condition $V(x)-V((A+BK)x+Dw)\leq \gamma^2w^Tw$ with $V(x)=x^T P x\geq0$, i.e.
-$x^TPx - ((A+BK)x+Dw)^TP((A+BK)x+Dw)\geq x^T(Q+K^TRK)x -\gamma^2 w^Tw$
+linear feedback  $u=Kx$, where $K$ satisfies the robust Lyapunov condition $V(x)-V((A+BK)x+Dw)\leq \gamma^2w^Tw$ 
+with $V(x)=x^T P x\geq0$, i.e. $x^TPx - ((A+BK)x+Dw)^TP((A+BK)x+Dw)\geq x^T(Q+K^TRK)x -\gamma^2 w^Tw$
 for a minimum  $\gamma^2$, see e.g.~\cite{Boyd:94}.
@@
 t\tilde u) dt\cdot \tilde u \\
-%+ A \tilde x + B \tilde u - A \tilde x - B\tilde u\\
 \Leftrightarrow 
@@
 This implies the dynamics
+%
 \[
@@
 \]
-where
-$H^x$ and $H^u$ can be determined by integration. Suppose that
-for $x\in\mathcal X$ and $u\in\mathcal U$, where $\mathcal X$ and $\mathcal U$ are compact
-sets, the values of $H^x$ and $H^u$ are known, i.e.\
-$H^x\tilde x+H^u\tilde u\in\conv_k\{H^x_k\tilde x + H^u_k\tilde u\}$ for all $(\tilde x,\tilde u)\in\mathcal X\times \mathcal U$.
+%
+where $H^x$ and $H^u$ can be determined by integration. 
+Suppose that for all $x\in\mathcal X$ and $u\in\mathcal U$, where $\mathcal X$ and $\mathcal U$ are compact sets,
+we can bound the values of $H^x x+ H^u u$ by a finite convex combination of extremal values, i.e. 
+$H^x x+H^u u\in\conv_k\{H^x_k x + H^u_k u\}$.
+\note{I did't like this passage. It made it seem obvious that the nonlinearities are contained in a polytope spanned by
+extremal values.. That's obviously not the case..}
 Clearly, we can then introduce the element\-wise disturbance bound 
@@
 %
-In this section we describe the computation of the MRPI set for~\eqref{eq:system:equation} with a disturbance set parametrised by a scalar $\theta$:
+In this section we describe the computation of the MRPI set for~\eqref{eq:system:equation} with a disturbance set 
+parametrised by a scalar $\theta$:
+%
 \[
@@
 \]
+%
 For input constrained systems under a given feedback law, we combine the uniform scaling of 
 the disturbance set $\mathcal V(\theta)$ with non-uniform scaling of the input constraint set
+%
 \[
@@
 \]
+%
 The necessity of uniform scaling of the disturbance constraints is due to the method we use to avoid
-solving multiparametric linear programs in every step of the proposed iteration.
+solving multi-parametric linear programs in every step of the proposed iteration.
 A representation of the MRPI set of a system parametrised with respect to a scaling parameter allows us
@@
 \begin{rem}
-The set $\mathcal V(\theta)$ is nonempty and contains the origin for all $\theta>-1$ and hence the 
+The set $\mathcal V(\theta)$ is non-empty and contains the origin for all $\theta>-1$ and hence the 
 maximum
@@
 \text{s.t.}& Gv \leq (1+\theta){\bf{1}}
-%\\
-%&\theta>-1
 \end{array}
@@
 %
-is positive for any nonzero $c$.
+is positive for any non-zero $c$.
 \end{rem}
@@
 In the following we describe an algorithm to compute the MRPI set $\mathcal Z^\infty$ contained in 
-$\mathcal Z = \{(x,\theta):\mathcal F_i x+\mathcal G_i\theta \leq 1,\forall\, i\leq m\}$.
+$\mathcal Z = \{(x,\theta):\mathcal F_i x+\mathcal G_i\theta \leq 1,\forall\, i\in\mathcal I\}$.
 As in the state dependent case we iteratively introduce constraints \emph{separating} points
@@
 \begin{split}
-	D_0 =& \{\mathcal F_i(\Psi x+v) + \mathcal G_i\theta \leq 1 \ \forall\, v\in\mathcal V(\theta), \ i\leq m\}\\
+	D_0 =& \{\mathcal F_i(\Psi x+v) + \mathcal G_i\theta \leq 1 \ \forall\, v\in\mathcal V(\theta), \ i\in\mathcal I_0\}\\
 	=&\Biggl\{\mathcal F_i\Psi x + \begin{array}[t]{rl}\displaystyle\max_v& F_i v \\ \text{s.t.}& Gv \leq 
 	(1+\theta){\bf{1}} \end{array}
-	 + \mathcal G_i \theta \leq 1 \ \forall\, i\leq m\Biggr\}\\
+	 + \mathcal G_i \theta \leq 1 \ \forall\, i\in\mathcal I_0\Biggr\}\\
 	=&\Biggl\{\mathcal F_i\Psi x + (1+\theta)\underbrace{\begin{array}[t]{rl}\displaystyle\max_v& F_i v \\ 
 	\text{s.t.}& Gv \leq {\bf{1}}\end{array}}_{v_{0,i}^\ast}
-	 + \mathcal G_i \theta \leq 1 \ \forall\, i\leq m\Biggr\}\\
-	=&\{\mathcal F_i\Psi x + (\mathcal G_i + v_{0,i}^\ast)\theta \leq 1 - v_{0,1}^\ast \ \forall \, i\leq m
+	 + \mathcal G_i \theta \leq 1 \ \forall\, i\in\mathcal I_0\Biggr\}\\
+	=&\{\mathcal F_i\Psi x + (\mathcal G_i + v_{0,i}^\ast)\theta \leq 1 - v_{0,1}^\ast \ \forall \, i\in\mathcal I_0
 	\}
@@
 	D_k = \biggl\{\mathcal F_i\Psi^{k+1}x+ \biggl(\mathcal G_i +\sum_{0\leq l\leq k} v_{l,i}^\ast\biggr)\theta \leq 1 
-	- \sum_{0\leq l\leq k} v_{l,i}^\ast\, i\leq m\biggr\}
+	- \sum_{0\leq l\leq k} v_{l,i}^\ast\, i\in\mathcal I_0\biggr\}
 \end{equation}
@@
 The iteration terminates when $Z_k\subseteq Z_{k+1}$. As in section~\ref{sec:state:dep:MRPI}
-we will require $\mathcal Z\vert_{\hat\theta}$ to be contained in an observable band: $\mathcal Z\vert_{\hat\theta}=\{x:\mathcal Fx \leq {\bf{1}}-\mathcal G\hat\theta\}\subseteq
-\mathcal B=\{x:\Gamma x\leq {\bf{1}}\wedge -\Gamma x\leq {\bf{1}}\}$ for all $\hat\theta>-1$. We have the following result.
+we will require $\mathcal Z\vert_{\hat\theta}$ to be contained in an observable band: $\mathcal Z\vert_{\hat\theta}
+=\{x:\mathcal Fx \leq {\bf{1}}-\mathcal G\hat\theta\}\subseteq \mathcal B=\{x:\Gamma x\leq {\bf{1}}\wedge -\Gamma 
+x\leq {\bf{1}}\}$ for all $\hat\theta>-1$. We have the following result:
 %
@@
 \end{thm}
-%\note{You wrote to highlight $\mathcal V(0)$ being bounded was an assumption. It is necessary so I don't know what to do with this.}
 %
@@
 
-The iterative process described above allows uniform scaling of the disturbance set.
-As mentioned earlier, the algorithm can be extended to the case of non-uniformly scaled input constraints to accommodate more degrees of freedom for
+The iterative process described above allows uniform scaling of the disturbance set. As mentioned earlier, the 
+algorithm can be extended to the case of non-uniformly scaled input constraints to accommodate more degrees of freedom for 
 system analysis simply by using 
+%
 \[
@@
 \]
+%
 This does not affect the algorithm since at each step of the iteration 
 the elements of $\mathcal H$ remain unchanged. 
-%In the next section we will illustrate the algorithm.
 %
@@
 In this section we compute MRPI sets for the levitating ball system presented in 
-section~\ref{sec:first:example} and for a purely numerical model.
-These examples illustrate the effectiveness of the proposed approach for state dependent disturbances and the use of parametrised MRPI sets as a system analysis tool.
+section~\ref{sec:first:example} and for a purely numerical model. These examples illustrate the effectiveness 
+of the proposed approach for state dependent disturbances and the use of parametrised MRPI sets as a system analysis tool.
 
@@
 in~\eqref{eq:definition:element:wise:constraints:on:nonlinearities} for all $(x,u)\in\mathcal X\times\mathcal U$. 
-%Using the same constraint set $\mathcal X \times \mathcal U$ to determine 
 This yields a constant set $\mathcal V$ which is non-symmetric around the origin due to nonlinearity. We also introduce
@@
 constraints with the parametrised set $\mathcal Z^\infty$. To do this we compute the scaling parameter 
-$\alpha_{\min}$ such that $\mathcal X^\infty\subseteq\mathcal Z^\infty\vert_{(\alpha=\alpha_{\min},\theta=0)}$
+$\alpha_{\min}$ such that $\mathcal X^\infty\subseteq\mathcal Z^\infty\vert_{(\theta=0,\alpha=\alpha_{\min})}$
 by solving $m_\infty$ linear programs
@@
 Caution is advised when interpreting $\alpha>0$, since the system is nonlinear.
-extrapolations reveal little insight, however $\alpha_{\min} > 1$ indicates that the current set of inputs $\mathcal U(0)=\mathcal U$ 
+extrapolations reveal little insight, however $\alpha_{\min} > 0$ indicates that the current set of inputs $\mathcal U(0)=\mathcal U$ 
 is not large enough to cope with the perturbation set given by upper bounds of the nonlinear effects.
@@
 \lbl[l]{93,32;$\longleftarrow\mathcal X^\infty$}
-\lbl[r]{68,43;$\mathcal Z^\infty\vert_{(\alpha_{\min},0)}\longrightarrow$}
+\lbl[r]{68,43;$\mathcal Z^\infty\vert_{(0,\alpha_{\min})}\longrightarrow$}
 \end{lpic}
@@
 compute which $\alpha_i$ will change the MRPI set the most. This can be done elementwise by calculating
+%
 $$
@@
 $$
+%
 For this example the greatest sensitivity corresponds to $\alpha_3$ with a numerical value of $2.6458\times 10^9$, 
 i.e. the third input constraint.
-Similarly to the first example we might also want to know how much disturbance the closed loop system can tolerate such that a given set is contained in the MRPI set $\mathcal C\subseteq\mathcal Z^\infty\vert_{(0,\theta)}$.
+\note{I actually have no idea what the numerical value means. It sort of tells us that at least one constraint depending on $\alpha_3$
+is highly sensitive. The actual numerical value could also imply that it is a constraint on $\alpha_3$ which has some residual dependence on
+$\alpha_3$ and is blown up by normalising.}
+Similarly to the first example we might also want to know how much disturbance the closed loop system can tolerate 
+such that a given set is contained in the MRPI set $\mathcal C\subseteq\mathcal Z^\infty\vert_{(\theta,0)}$.
 Although non-positivity of $\mathcal H$ implies non-positivity of $\Lambda^\alpha$, a similar argument cannot be applied to $\Lambda^\theta$.
-% , in fact it is easy to see that both signs are likely to be 
-% present in $\Lambda^\theta$. The condition $\theta>-1$ implies that $\Lambda^\theta$ has at least one negative
-% element, on the other hand the elements of $\Lambda^\theta$ are given by $\mathcal G_i + \sum_{l\leq k}v_{l,i}^\ast$.
-% We know $\mathcal G$ and hence we know that most entries are zero, so that $\Lambda^\theta$ has positive entries.
 Let $(\Lambda^1,\lambda^1)$ and $(\Lambda^2,\lambda^2)$ denote all rows of $\Lambda^\theta$ such that $\Lambda^{1,\theta}>0$ and
 $\Lambda^{2,\theta}\leq0$. This implies that for any fixed $\hat\alpha$ the set $\mathcal Z^\infty\vert_{\hat\alpha}$
-is compact, and since $\mathcal Z^\infty\vert_{(\hat\alpha,\hat\theta)}$
+is compact, and since $\mathcal Z^\infty\vert_{(\hat\theta,\hat\alpha)}$
 is compact, there exist a maximal $\theta_{\max}$ and likewise a minimal $\theta_{\min}$
 such that $\Lambda^{1,x}x+\Lambda^{1,\alpha}\hat\alpha+\Lambda^{1,\theta}\theta\leq\lambda^1$ can be satisfied. We can solve the optimisation programs
+%
 $$
 	\gamma_i = \begin{array}[t]{rl}
-	\displaystyle\max_x& \Lambda^{1,x}x\\
+	\displaystyle\max_x& \Lambda^{1,x}_ix\\
 	\text{s.t.}& x\in\mathcal C
@@
 	\delta_i = \begin{array}[t]{rl}
-	\displaystyle\max_x& \Lambda^{2,x}x\\
+	\displaystyle\max_x& \Lambda^{2,x}_ix\\
 	\text{s.t.}& x\in\mathcal C
@@
 $$
+%
 The extremal values for which $\mathcal C$ is contained in the MRPI set are given by
@@
 \centerline{\includegraphics[scale=0.6]{twoDimensional}}
-\caption{The extremal MRPI sets $\mathcal Z^\infty\vert_{(0,\theta_{min})}$ and $\mathcal Z^\infty
-\vert_{(0,\theta_{\max})}$ containing the unit box.}
+\caption{The extremal MRPI sets $\mathcal Z^\infty\vert_{(\theta_{min},0)}$ and $\mathcal Z^\infty
+\vert_{(\theta_{\max},0)}$ containing the unit box.}
 \label{fig:two:dim:example}
@@
 %
-In this paper we discussed extensions to existing computational methods to determine MRPI sets for linear systems subject to additive disturbance for two descriptions of the sets bounding unknown additive disturbances.
-The case of state dependent disturbances was considered, and applied to the problem of determining approximations to MRPI sets for linearised nonlinear systems.
-This was illustrated using the example of a magnetic levitation system.
-Secondly the computation of MRPI sets for systems with disturbance and control inputs bounded by scaled sets was considered.
-This enables system analyses based on uniform scaling applied to disturbance sets and non-uniform scaling of input constraints.
-A comparison of the two approaches shows the effectiveness of the method based on state dependent disturbance sets.
+In this paper we discussed extensions to existing computational methods to determine MRPI sets for linear systems subject 
+to additive disturbance for two descriptions of the sets bounding unknown additive disturbances. The case of state dependent 
+disturbances was considered, and applied to the problem of determining approximations to MRPI sets for linearised nonlinear 
+systems. This was illustrated using the example of a magnetic levitation system. Secondly the computation of MRPI sets for 
+systems with disturbance and control inputs bounded by scaled sets was considered. This enables system analyses based on 
+uniform scaling applied to disturbance sets and non-uniform scaling of input constraints. A comparison of the two approaches 
+shows the effectiveness of the method based on state dependent disturbance sets.
 

### 2015-03-23 draft.tex
Corrected typo in referencing.
Labled pictures in tex for consistency.
checked changes and added notes

@@
 $v\in\mathcal V(x)$ where $\mathcal V(x)$ is a parametrically convex point-to-set map defined 
-by~\eqref{eq:PWA:distrubance:set} with a convex piecewise affine $H(x)$.
+by~\eqref{eq:PWA:disturbance:set} with a convex piecewise affine $H(x)$.
 Notice that the set $\mathcal V(x)$ is pointwise polytopic set~\eqref{eq:definition:MRPI:set:state:dependent} 
@@
 in this closed form representation but it merely denotes the preimage of $\mathcal X_k$ because that is all we need that the preimages
-keep growing. It might be confusing with the notation but that is only to emphasise that it behaves like the inverse..}
+keep growing. It might be confusing with the notation but that is only
+to emphasise that it behaves like the inverse [change notation, e.g.
+$\Psi^\dagger$?]}
 %
@@
 (\Gamma\Psi^{n-1})^T\end{bmatrix}) = n$.
-\note{This looks very MATLAB.. I don't like it.}
+\note{This looks very MATLAB.. I don't like it [saves space]}
 But  this implies that the set 
@@
 $\dot{y}=0$ and $u=\sqrt{\frac{gm}{c}} y$ for any positive position $y>0$. Linearising the nonlinear differential 
-equation $\dot x = f(x,u)$ around an equilibrium point $(\hat x, \hat u)$ gives the approximate model 
+equation $\dot x = f(x,u)$ around an equilibrium point $(\hat x, \hat
+u)$ gives the approximate linear model 
 %
 \begin{equation}
-	 \dot{\tilde{x}} \approx \underbrace{\left(\begin{array}{cc}
+	 \Delta\dot{x} = \underbrace{\left(\begin{array}{cc}
 	0 & 1 \\ \frac{2c\hat u^2}{m\hat x_1^3} & 0
 	\end{array}\right)}_{\frac{\partial f}{\partial x}(\hat x,\hat
-      u)}\tilde x 
+      u)}\Delta x 
 + \underbrace{\left(\begin{array}{c}
@@
 	\end{array}\right)}_{\frac{\partial f}{\partial u}(\hat x,\hat
-      u)}\tilde u
+      u)}\Delta u
 \end{equation}
 %
-\note{I find the $x^+\approx Ax+Bu$ notation very misleading! I prefer $=$ since we 
-will take it as an equality after all not handling discretisation errors at all..}
-where $\tilde{x} = x-\hat{x}$, $\tilde{u} = u -\hat{u}$.
+\note{I find the $x^+\approx Ax+Bu$ notation very misleading! I prefer
+  $=$ since we will take it as an equality after all not handling
+  discretisation errors at all.. [OK - agreed]}
+where $\Delta u = u -\hat{u}$ and $\Delta x \approx x-\hat{x}$.
 We derive the discrete time dynamics with sampling rate $T_s$ using
@@
 \[
-\tilde{x}^+ \approx A \tilde{x} + B \tilde{u}, \quad
+\Delta x^+ = A \Delta x + B \Delta u , \quad
 \Biggl\{\begin{aligned} A &= I+T_s\frac{\partial f}{\partial  x}(\hat
@@
 for a minimum  $\gamma^2$, see e.g.~\cite{Boyd:94}.
+\note{What is $w$ here?}
 A representation of disturbances acting on the linearised
@@
 Using the Mean Value Theorem
-and the linearisation around $(\hat{x},\hat{u})$, we obtain the successor state:
+and the linearisation around $(\hat{x},\hat{u})$, and defining 
+$\tilde{x} = x - \hat{x}$, $\tilde{u} = u - \hat{u}$ we obtain the successor state:
 %
@@
 &\quad + \int_0^1\frac{\partial\tilde f}{\partial u}(\hat x + t\tilde x,\hat u+
-t\tilde u) dt\cdot \tilde u \\
+t\tilde{u}) dt\cdot \tilde{u} \\
 \Leftrightarrow 
@@
 \int_0^1\frac{\partial\tilde f}{\partial x}(\hat x + t\tilde x,\hat u
-             + t\tilde u)dt - A \Bigr)\tilde x 
+             + t\tilde{u})dt - A \Bigr)\tilde x 
 \\ 
-&\quad +\Bigl(\int_0^1\frac{\partial\tilde f}{\partial u}(\hat x + t\tilde x,\hat u + t\tilde u)dt - B\Bigr)\tilde u
+&\quad +\Bigl(\int_0^1\frac{\partial\tilde f}{\partial u}(\hat x +
+  t\tilde x,\hat u + t\tilde{u})dt - B\Bigr)\tilde{u}
 \end{align*}
@@
 \[
-\tilde x^+ = A\tilde x+B\tilde u + H^x\tilde x + H^u \tilde u, 
+\tilde x^+ = A\tilde x+B\tilde{u} + H^x\tilde{x} + H^u \tilde{u}, 
 \]
@@
 where $H^x$ and $H^u$ can be determined by integration. 
-Suppose that for all $x\in\mathcal X$ and $u\in\mathcal U$, where $\mathcal X$ and $\mathcal U$ are compact sets,
-we can bound the values of $H^x x+ H^u u$ by a finite convex combination of extremal values, i.e. 
-$H^x x+H^u u\in\conv_k\{H^x_k x + H^u_k u\}$.
+Suppose that for all $x\in\mathcal X$ and $u\in\mathcal U$, where
+$\mathcal X$ and $\mathcal U$ are compact sets, $f(x,u)$ is
+continuously differentiable. Then
+we can bound the values of $H^x \tilde{x}+ H^u \tilde{u}$ by a finite convex combination of extremal values, i.e. 
+$H^x \tilde{x}+H^u \tilde{u}\in\conv_k\{H^x_k \tilde{x} + H^u_k \tilde{u}\}$.
 \note{I did't like this passage. It made it seem obvious that the nonlinearities are contained in a polytope spanned by
-extremal values.. That's obviously not the case..}
+extremal values.. That's obviously not the case.. [We can assume this
+if $f$ is continuously differentiable]}
 Clearly, we can then introduce the element\-wise disturbance bound 
@@
 \begin{multline}\label{eq:definition:element:wise:constraints:on:nonlinearities}
-\mathcal V(x,u)=\biggl\{v:\min_k\{
-H^x_{k,i}x+H^u_{k,i}u\}\leq v_i\,\wedge 
+\mathcal V(\tilde{x},\tilde{u})=\biggl\{v:\min_k\{
+H^x_{k,i}\tilde{x}+H^u_{k,i}\tilde{u}\}\leq v_i\,\wedge 
 \\ 
-v_i \leq \max_k\{H^x_{k,i}x+H^u_{k,i}u\}, \, i =1,\dots,n\biggr\}.
+v_i \leq \max_k\{H^x_{k,i}\tilde{x}+H^u_{k,i}\tilde{u}\}, \, i =1,\dots,n\biggr\}.
 \end{multline}
@@
 levitating ball: $Ts=30ms, C=1, m=100g, \hat x_1 = 50mm$ and $\mathcal X=\{x:
-\abs{\hat x_1-x_1}\leq 1mm\wedge \abs{x_2}\leq 105\frac{mm}{s}\}$, $\mathcal U=\{u:\abs{\hat u-u}\leq10mA\}$.
+\abs{x_1- \hat x_1}\leq 1mm\wedge \abs{x_2}\leq 105\frac{mm}{s}\}$, $\mathcal U=\{u:\abs{ u-\hat u}\leq10mA\}$.
 Using a total of 25 samples for the computation of $(H^x,H^u)$ we obtain the invariant set shown in figure~\ref{fig:MRPI:set:levitating:ball},
-which is less conservative than using fixed bounds on the nonlinearities as we will see in the next example.
+which is less conservative than using fixed bounds on the
+nonlinearities as we will see in Section~\ref{sec:second:example}.
 The algorithm for computing the MRPI set terminates after 3 iterations.
@@
 is highly sensitive. The actual numerical value could also imply that it is a constraint on $\alpha_3$ which has some residual dependence on
-$\alpha_3$ and is blown up by normalising.}
+$\alpha_3$ and is blown up by normalising. [some comment is needed in
+the text]}
 Similarly to the first example we might also want to know how much disturbance the closed loop system can tolerate 
@@
 \begin{figure}
-\centerline{\includegraphics[scale=0.6]{twoDimensional}}
+\centering
+\begin{lpic}{twoDimensional(.6,)}
+{\tiny
+\lbl[r]{4,9;$-3$}
+\lbl[r]{4,22;$-2$}
+\lbl[r]{4,35;$-1$}
+\lbl[r]{4,49;$0$}
+\lbl[r]{4,62;$1$}
+\lbl[r]{4,76;$2$}
+\lbl[r]{4,89;$3$}
+\lbl[t]{6,3;$-10$}
+\lbl[t]{17,3;$-8$}
+\lbl[t]{28,3;$-6$}
+\lbl[t]{39,3;$-4$}
+\lbl[t]{50,3;$-2$}
+\lbl[t]{63,3;$0$}
+\lbl[t]{74,3;$2$}
+\lbl[t]{85,3;$4$}
+\lbl[t]{96,3;$6$}
+\lbl[t]{107,3;$8$}
+\lbl[t]{118,3;$10$}
+}
+{\footnotesize
+\lbl[r]{0,52,90;$x_2$}
+\lbl[t]{63,0;$x_1$}
+}
+\end{lpic}
 \caption{The extremal MRPI sets $\mathcal Z^\infty\vert_{(\theta_{min},0)}$ and $\mathcal Z^\infty
@@
 \begin{figure}
-\centerline{\includegraphics[scale=0.6]{threeDimensional}}
+\centering
+\begin{lpic}{threeDimensional(.6,)}
+{\tiny
+\lbl[r]{4,69;$6$}
+\lbl[r]{4,61;$5$}
+\lbl[r]{4,53;$4$}
+\lbl[r]{4,45;$3$}
+\lbl[r]{4,37;$2$}
+\lbl[r]{4,29;$1$}
+\lbl[r]{4,21;$0$}
+\lbl[r]{4,13;$-1$}
+\lbl{9,5;$6$}
+\lbl{24,5;$4$}
+\lbl{40,4;$2$}
+\lbl{55,4;$0$}
+\lbl{69,3;$-2$}
+\lbl{83,3;$-4$}
+\lbl{99,3;$-6$}
+\lbl{116,8;$-10$}
+\lbl{120,16;$0$}
+\lbl{126,23;$10$}
+}
+{\footnotesize
+\lbl{125,15;$x_1$}
+\lbl{50,2;$x_2$}
+\lbl[r]{-1,40,90;$\theta$}
+}
+\end{lpic}
 \caption{The parametrised MRPI set for $\alpha=0$. Containing the unit box in the 

### 2015-03-23 draft.tex
Made my changes.

@@
 In closed form the iterates can be expressed as
-\note{We actually do NOT assume that $\Psi$ is invertible! We don't need its inverse at any point! $\Psi^{-1}$ appears only
-in this closed form representation but it merely denotes the preimage of $\mathcal X_k$ because that is all we need that the preimages
-keep growing. It might be confusing with the notation but that is only
-to emphasise that it behaves like the inverse [change notation, e.g.
-$\Psi^\dagger$?]}
 %
@@
 %
+Notice that we do not require $\Psi$ to be invertible, in~\eqref{eq:set:iteration:state:dependent:constraints} $\Psi^{-1}\mathcal X_k$
+merely denotes the preimage of $\mathcal X_k$ under the linear map $\Psi$.
 We will use~\eqref{eq:set:iteration:state:dependent:constraints} to prove the finite determinability of
@@
 (\Gamma\Psi^{n-1})^T\end{bmatrix}) = n$.
-\note{This looks very MATLAB.. I don't like it [saves space]}
 But  this implies that the set 
@@
 %
-\note{I find the $x^+\approx Ax+Bu$ notation very misleading! I prefer
-  $=$ since we will take it as an equality after all not handling
-  discretisation errors at all.. [OK - agreed]}
 where $\Delta u = u -\hat{u}$ and $\Delta x \approx x-\hat{x}$.
@@
 MRPI set is applicable since we consider the closed loop system under
-linear feedback  $u=Kx$, where $K$ satisfies the robust Lyapunov condition $V(x)-V((A+BK)x+Dw)\leq \gamma^2w^Tw$ 
-with $V(x)=x^T P x\geq0$, i.e. $x^TPx - ((A+BK)x+Dw)^TP((A+BK)x+Dw)\geq x^T(Q+K^TRK)x -\gamma^2 w^Tw$
+linear feedback  $u=Kx$, where $K$ satisfies the robust Lyapunov condition $V(x)-V((A+BK)x+v)\leq \gamma^2v^Tv$ 
+with $V(x)=x^T P x\geq0$, i.e. $x^TPx - ((A+BK)x+v)^TP((A+BK)x+v)\geq x^T(Q+K^TRK)x -\gamma^2 v^Tv$
 for a minimum  $\gamma^2$, see e.g.~\cite{Boyd:94}.
 \note{What is $w$ here?}
-A representation of disturbances acting on the linearised
-model due to linearisation errors can be obtained using the
+A representation of additive disturbances acting on the linearised
+model due to linearisation errors, i.e. a system representation $x^+=Ax + Bu + v$ with an additive disturbance $v$, can be obtained using the
 Mean Value Theorem for vector-valued functions (e.g.~\cite{Apostol:1974}).

### 2015-03-23 draft.tex
Added index terms.

@@
 \begin{keywords}
+constrained control, positively invariant sets, robust control
 \vskip-\baselineskip
@@
 for a minimum  $\gamma^2$, see e.g.~\cite{Boyd:94}.
-\note{What is $w$ here?}
 A representation of additive disturbances acting on the linearised
@@
 $H^x \tilde{x}+H^u \tilde{u}\in\conv_k\{H^x_k \tilde{x} + H^u_k \tilde{u}\}$.
-\note{I did't like this passage. It made it seem obvious that the nonlinearities are contained in a polytope spanned by
-extremal values.. That's obviously not the case.. [We can assume this
-if $f$ is continuously differentiable]}
 Clearly, we can then introduce the element\-wise disturbance bound 
@@
 To obtain values for $(H^x_k,H^u_k)$ we sample $\mathcal X\times\mathcal U$ and evaluate the integral 
-expressions defining $(H^x_k,H^u_k)$ pointwise. For this we use the numerical values for the example of the 
+expressions defining $(H^x_k,H^u_k)$ pointwise.
+This leads to an inner approximation of the linearisation error set, however we can make it as tight as necessary
+by increasing the number of samples.
+For this we use the numerical values for the example of the 
 levitating ball: $Ts=30ms, C=1, m=100g, \hat x_1 = 50mm$ and $\mathcal X=\{x:
@@
 %
-For this example the greatest sensitivity corresponds to $\alpha_3$ with a numerical value of $2.6458\times 10^9$, 
+For this example the greatest sensitivity corresponds to $\alpha_3$, 
 i.e. the third input constraint.
-\note{I actually have no idea what the numerical value means. It sort of tells us that at least one constraint depending on $\alpha_3$
-is highly sensitive. The actual numerical value could also imply that it is a constraint on $\alpha_3$ which has some residual dependence on
-$\alpha_3$ and is blown up by normalising. [some comment is needed in
-the text]}
 Similarly to the first example we might also want to know how much disturbance the closed loop system can tolerate 

### 2015-08-02 postreview.tex
Added file to accommodate reviews.
Made changes according to review 16643

--- 2015-03-23 draft.tex
@@
 \[
-	\mathcal X_{k+1} = \mathcal X_k\cap \{x:\genmat_{0,i}\Psi^k x + \sum_{l=0}^{k-1}v_{l,i}^\ast(x)
+	\mathcal X_{k+1} = \mathcal X_k\cap \{x:\genmat_{0,i}\Psi^k x + \sum_{l=1}^{k-1}v_{l,i}^\ast(x)
 	\leq\genvec_{0,i}\,\forall i\in\mathcal I_0\},
@@
 	=\mathcal X_k\cap D_k \\
-	=& \bigcap_{0\leq l\leq k+1}\left( \Psi^{-l} \mathcal X_0 \underset{0 \leq i\leq l-1}{\bigominus} 
+	=& \bigcap_{0\leq l\leq k+1}\left( \Psi^{-l} \mathcal X_0 \underset{1 \leq i\leq l-1}{\bigominus} 
   \Psi^i \mathcal V(\mathcal X_{l-1})\right).
@@
 $\mathcal X^\infty$ is non-empty. For this we require that $\bigcup_{s\in\mathcal S}\mathcal V(s)$ is 
-compact on any compact set $\mathcal S\subset\mathbb R^n$.
+bounded on any bounded set $\mathcal S\subset\mathbb R^n$.
 
-The proof has two main steps: First we prove that $\mathcal X_p$ is compact for $p\leq n$
+The proof has two main steps: First we prove that $\mathcal X_p$ is bounded for $p\leq n$
 where $n$ is the dimension of the state $x$. The second step is to prove that in~\eqref{eq:set:iteration:state:dependent:constraints}
-the set $D_k$ grows exponentially, i.e. that for any given compact set $\mathcal C$ there exists
+the set $D_k$ grows exponentially, i.e. that for any given bounded set $\mathcal C$ there exists
 finite $N$ such that $\mathcal C\subseteq D_{N}$. The proof is concluded by setting 
@@
 is bounded, and since $\mathcal X_k\subseteq \mathcal P_k$ for all $k$, 
-the set $\mathcal X_{n}$ is also bounded. To show that $D_k$ grows exponentially we use the compactness 
+the set $\mathcal X_{n}$ is also bounded. To show that $D_k$ grows exponentially we use the boundedness 
 of $\mathcal V(\mathcal X_{n})$. Let $K_1$ denote the smallest ball that contains $\mathcal V(\mathcal X_{n})$ and let
@@
 \begin{equation}
-D_k = \underbrace{\Psi^{-k}\mathcal X_0}_{=\mathcal S_1} \ominus \underbrace{\biggl(\bigoplus_{i\leq k-1} 
+D_k = \underbrace{\Psi^{-k}\mathcal X_0}_{=\mathcal S_1} \ominus \underbrace{\biggl(\bigoplus_{1\leq i\leq k-1} 
 \Psi^i\mathcal V(\mathcal X_k)\biggr)}_{=\mathcal S_2}.
@@
 is bounded. To bound $\mathcal S_2$ we note that for $k\geq n$ we have $\mathcal S_2\subseteq 
-\bigoplus_{0\leq i\leq k-1} \rho^i K_2 \subseteq \frac{1}{1-\rho} K_2$. Thus $D_k$ grows exponentially, whereas 
+\bigoplus_{1\leq i\leq k-1} \rho^i K_2 \subseteq \frac{1}{1-\rho} K_2$. Thus $D_k$ grows exponentially, whereas 
 $\mathcal X_k$ is contained in a ball of finite radius, and hence we conclude from~\eqref{eq:set:iteration:state:dependent:constraints} that 
@@
 %
-We have seen that we can compute a the maximal robust positively invariant set $\mathcal X^\infty$ for linear 
+We have seen that we can compute the maximal robust positively invariant set $\mathcal X^\infty$ for linear 
 systems with state dependent constraints. In the next section we will illustrate the concept with an 
@@
 \put(30,5){$m g$}
-\put(30,41){$c\frac{i^2}{x^2}$}
+\put(30,41){$c\frac{i^2}{y^2}$}
 \put(78,28){$y$}
@@
 %
-In this section we discuss the calculation of the MRPI set for a linearised simplified model of the magnetic 
+In this section we discuss the calculation of the MRPI set for a linearised and simplified model of the magnetic 
 levitation system depict in figure~\ref{fig:levitating:ball}. The system dynamics for the ball are given
@@
 For this we use the numerical values for the example of the 
-levitating ball: $Ts=30ms, C=1, m=100g, \hat x_1 = 50mm$ and $\mathcal X=\{x:
+levitating ball: $T_s=30ms, C=1, m=100g, \hat x_1 = 50mm$ and $\mathcal X=\{x:
 \abs{x_1- \hat x_1}\leq 1mm\wedge \abs{x_2}\leq 105\frac{mm}{s}\}$, $\mathcal U=\{u:\abs{ u-\hat u}\leq10mA\}$.

### 2015-08-03 postreview.tex
Added remark about classification.

@@
 \end{align*}
+%
+\begin{rem}
+Determining the map $v_{l,i}(x)$ for all admissible $x\in \mathcal X_0$ in general poses a great classification
+challenge. 
+%
+Notice that in our calculations we can avoid determining the particular vertex $v_{l,i}(x)$ explicitly, it
+suffices to determine the vertex determining a supporting hyperplane of $\mathcal X_{k+1}$, i.e.~$v_{l,i}^\ast(x)$. 
+%
+This can be done by adding all possible inequalities and applying a inequality reduction algorithm.
+\end{rem}
 %

### 2015-08-04 postreview.tex
checked and reduced to 6 pages

@@
 \subset\mathbb R^n$, the Minkowski set addition is denoted $\mathcal A\oplus\mathcal B = \{c : c = a + 
-b\; \forall\,a\in\mathcal A,\, b\in\mathcal B\}$. We use ${\bf{1}}$ to denote the column vector of ones 
-in appropriate dimensions, and $\wedge$ is the logical AND operator, index sets are denoted by $\mathcal I
+b\; \forall\,a\in\mathcal A,\, b\in\mathcal B\}$. We denote the column vector of ones 
+in appropriate dimensions as ${\bf{1}}$, the logical AND operator as $\wedge$, and index sets as  $\mathcal I
 \subset\mathbb N$. 
@@
   \subseteq &\lambda\underbrace{(\{z_1\}\oplus T(z_1))}_{\subseteq S}\oplus
-  (1-\lambda)\underbrace{(\{z_2\}\oplus T(z_2))}_{\subseteq S}\\
-  \subseteq& Z
+  (1-\lambda)\underbrace{(\{z_2\}\oplus T(z_2))}_{\subseteq S}
+  \subseteq Z
 \end{aligned}\]
@@
 for each $i\in \mathcal I_0$.
-Notice that $v_{0,i}^\ast(x)$ is not necessarily given by a unique maximiser, 
-but is the solution of a multi-parametric linear program and hence will be given 
+Here $v_{0,i}^\ast(x)$ is not necessarily given by a unique maximiser, 
+but is the solution of a multi-parametric linear program and hence is given 
 by a vertex $v_i(x)$ of $\mathcal V(x)$ for each $x$ on that facet.
-Since each vertex is a piece-wise affine function of $x$, the maximum $v_{0,i}^\ast(x)$ will also
-be piece-wise affine
-and therefore the set $\mathcal X_1=\mathcal X_0 \cap \{x:\genmat_{0,i}\Psi x + v_{0,i}^\ast(x) \leq 
+Since each vertex is a piece-wise affine function of $x$, the maximum $v_{0,i}^\ast(x)$ is also piece-wise affine
+so the set $\mathcal X_1=\mathcal X_0 \cap \{x:\genmat_{0,i}\Psi x + v_{0,i}^\ast(x) \leq 
 \genvec_{0,i}\forall i\in\mathcal I_0\}$
-has the representation $\mathcal X_1 = \{x:\genmat_{1,i}x\leq\genvec_{1,i}\,\forall i\in\mathcal I_1\}$.
+has representation $\mathcal X_1 = \{x:\genmat_{1,i}x\leq\genvec_{1,i}\,\forall i\in\mathcal I_1\}$.
 The next iterate is defined by
@@
 %
-\begin{align*}
-	v_{l,i}^\ast(x)&=\max_j \ \genmat_{0,i}\Psi^{l-1}v_j(x)
-	 = \begin{array}[t]{rl} \displaystyle\max_v & \genmat_{0,i}\Psi^{l-1}v \\ \text{s.t.}& v\in\mathcal V(x)
-   \end{array} \\ 
-   &= \begin{array}[t]{rl} \displaystyle\max_{\tilde v} & \genmat_{0,i}\tilde v\\ \text{s.t.}& \tilde v\in 
+\[
+	v_{l,i}^\ast(x)=\max_j \ \genmat_{0,i}\Psi^{l-1}v_j(x)
+   = \begin{array}[t]{rl} \displaystyle\max_{\tilde v} & \genmat_{0,i}\tilde v\\ \text{s.t.}& \tilde v\in 
    \Psi^{l-1}\mathcal V(x) \end{array}
-\end{align*}
+\]
+% \begin{align*}
+% 	v_{l,i}^\ast(x)&=\max_j \ \genmat_{0,i}\Psi^{l-1}v_j(x)
+% 	 = \begin{array}[t]{rl} \displaystyle\max_v & \genmat_{0,i}\Psi^{l-1}v \\ \text{s.t.}& v\in\mathcal V(x)
+%    \end{array} \\ 
+%    &= \begin{array}[t]{rl} \displaystyle\max_{\tilde v} & \genmat_{0,i}\tilde v\\ \text{s.t.}& \tilde v\in 
+%    \Psi^{l-1}\mathcal V(x) \end{array}
+% \end{align*}
 %
@@
 \bigoplus_{1\leq i\leq k-1} \rho^i K_2 \subseteq \frac{1}{1-\rho} K_2$. Thus $D_k$ grows exponentially, whereas 
-$\mathcal X_k$ is contained in a ball of finite radius, and hence we conclude from~\eqref{eq:set:iteration:state:dependent:constraints} that 
-$\mathcal X_{k+1} = \mathcal X _k$ for all $k\geq N$ and therefore $\mathcal X _N = \mathcal X^\infty$ for finite $N$.
+$\mathcal X_k$ is contained in a ball of finite radius, and we conclude from~\eqref{eq:set:iteration:state:dependent:constraints} that 
+$\mathcal X_{k+1} = \mathcal X _k$ for all $k\geq N$ and hence $\mathcal X _N = \mathcal X^\infty$ for finite $N$.
 \end{proof}
@@
 \label{fig:levitating:ball}
-\end{figure}
+\vspace{-2mm}\end{figure}
 %
@@
 %
-In this section we discuss the calculation of the MRPI set for a linearised and simplified model of the magnetic 
-levitation system depict in figure~\ref{fig:levitating:ball}. The system dynamics for the ball are given
+This section discusses the calculation of the MRPI set for a linearised, simplified model of the magnetic 
+levitation system depicted in figure~\ref{fig:levitating:ball}. The system dynamics for the ball are given
 by $m \ddot y = m g - c\frac{i^2}{y^2}$, where $m,g,c,i$ and $y$ denote the mass of the ball, the gravitational
 constant, a constant factor, the current and the distance between the coil and the centre of the ball respectively.
-For illustration purposes we neglect inductive dynamics and use the current $u=i$ as an input and the position
-$y$ and its first derivative $\dot y$ as the states, i.e. $x = (y,\dot y)^T$. We find that any equilibrium has 
+For illustration purposes we neglect inductive dynamics, using the current $u=i$ as the control input and the position
+$y$ and its first derivative $\dot y$ as the states: $x = (y,\dot y)^T$. We find that any equilibrium has 
 $\dot{y}=0$ and $u=\sqrt{\frac{gm}{c}} y$ for any positive position $y>0$. Linearising the nonlinear differential 
@@
 We derive the discrete time dynamics with sampling rate $T_s$ using
-the Euler formula $x^+=x+T_s f(x,u) =:\tilde f(x,u)$ giving
+the Euler formula $x^+=x+T_s f(x,u) =:\tilde f(x,u)$ giving $\Delta x^+ = A \Delta x + B \Delta u$,
 \[
-\Delta x^+ = A \Delta x + B \Delta u , \quad
-\Biggl\{\begin{aligned} A &= I+T_s\frac{\partial f}{\partial  x}(\hat
-  x,\hat u) \\
-B &= T_s \frac{\partial f}{\partial u}(\hat x,\hat u)
-\end{aligned}
+A = I+T_s\frac{\partial f}{\partial  x}(\hat
+  x,\hat u) , \quad
+B = T_s \frac{\partial f}{\partial u}(\hat x,\hat u)
 \]
+% \[
+% \Delta x^+ = A \Delta x + B \Delta u , \quad
+% \Biggl\{\begin{aligned} A &= I+T_s\frac{\partial f}{\partial  x}(\hat
+%   x,\hat u) \\
+% B &= T_s \frac{\partial f}{\partial u}(\hat x,\hat u)
+% \end{aligned}
+% \]
 Although this system has a control input, the algorithm for computing the
@@
 model due to linearisation errors, i.e. a system representation $x^+=Ax + Bu + v$ with an additive disturbance $v$, can be obtained using the
-Mean Value Theorem for vector-valued functions (e.g.~\cite{Apostol:1974}).
+Mean Value Theorem 
+(e.g.~\cite{Apostol:1974}).
 %
@@
 and the linearisation around $(\hat{x},\hat{u})$, and defining 
-$\tilde{x} = x - \hat{x}$, $\tilde{u} = u - \hat{u}$ we obtain the successor state:
+$\tilde{x} = x - \hat{x}$, $\tilde{u} = u - \hat{u}$, we obtain the successor state $x^+ = \tilde{f}(\hat{x} + \tilde{x},\hat{u} + \tilde{u})$ as
 %
-\begin{align*}
-x^+ &= \tilde{f}(\hat{x} + \tilde{x},\hat{u} + \tilde{u}) 
-\\
-&= \tilde f(\hat x, \hat u) 
+\begin{multline*}
+%x^+ &= \tilde{f}(\hat{x} + \tilde{x},\hat{u} + \tilde{u}) 
+%\\
+x^+= \tilde f(\hat x, \hat u) 
 + \int_0^1\frac{\partial\tilde f}{\partial x}(\hat x + t\tilde x,
 \hat u + t\tilde u) dt \cdot \tilde x  \\
-&\quad + \int_0^1\frac{\partial\tilde f}{\partial u}(\hat x + t\tilde x,\hat u+
-t\tilde{u}) dt\cdot \tilde{u} \\
-\Leftrightarrow 
-\tilde x^+ &= A\tilde{x} + B \tilde{u} +\Bigl(
++ \int_0^1\frac{\partial\tilde f}{\partial u}(\hat x + t\tilde x,\hat u+
+t\tilde{u}) dt\cdot \tilde{u}
+\end{multline*}
+and hence
+\begin{multline*}
+\tilde x^+ = A\tilde{x} + B \tilde{u} +\Bigl(
 \int_0^1\frac{\partial\tilde f}{\partial x}(\hat x + t\tilde x,\hat u
@@
 \\ 
-&\quad +\Bigl(\int_0^1\frac{\partial\tilde f}{\partial u}(\hat x +
++\Bigl(\int_0^1\frac{\partial\tilde f}{\partial u}(\hat x +
   t\tilde x,\hat u + t\tilde{u})dt - B\Bigr)\tilde{u}
-\end{align*}
+\end{multline*}
+% \begin{align*}
+% %x^+ &= \tilde{f}(\hat{x} + \tilde{x},\hat{u} + \tilde{u}) 
+% %\\
+% x^+&= \tilde f(\hat x, \hat u) 
+% + \int_0^1\frac{\partial\tilde f}{\partial x}(\hat x + t\tilde x,
+% \hat u + t\tilde u) dt \cdot \tilde x  \\
+% &\quad + \int_0^1\frac{\partial\tilde f}{\partial u}(\hat x + t\tilde x,\hat u+
+% t\tilde{u}) dt\cdot \tilde{u} \\
+% \Leftrightarrow 
+% \tilde x^+ &= A\tilde{x} + B \tilde{u} +\Bigl(
+% \int_0^1\frac{\partial\tilde f}{\partial x}(\hat x + t\tilde x,\hat u
+%              + t\tilde{u})dt - A \Bigr)\tilde x 
+% \\ 
+% &\quad +\Bigl(\int_0^1\frac{\partial\tilde f}{\partial u}(\hat x +
+%   t\tilde x,\hat u + t\tilde{u})dt - B\Bigr)\tilde{u}
+% \end{align*}
 %
@@
 where $H^x$ and $H^u$ can be determined by integration. 
-Suppose that for all $x\in\mathcal X$ and $u\in\mathcal U$, where
-$\mathcal X$ and $\mathcal U$ are compact sets, $f(x,u)$ is
-continuously differentiable. Then
+If $f(x,u)$ is
+continuously differentiable for all $x\in\mathcal X$ and $u\in\mathcal U$, where
+$\mathcal X$, $\mathcal U$ are compact sets, then
 we can bound the values of $H^x \tilde{x}+ H^u \tilde{u}$ by a finite convex combination of extremal values, i.e. 
 $H^x \tilde{x}+H^u \tilde{u}\in\conv_k\{H^x_k \tilde{x} + H^u_k \tilde{u}\}$.
-Clearly, we can then introduce the element\-wise disturbance bound 
+Thus we can introduce the element\-wise disturbance bound 
 %
@@
 %
-With this set we can
-guarantee that $\tilde x^+ = A\tilde x + B\tilde u + v$ accounts for all nonlinearities within $\mathcal X
-\times\mathcal U$ if we constrain $v\in\mathcal V(\tilde x,\tilde u)$. For general nonlinear systems
-finding the extremal values of $(H^x,H^u)$ cannot be done easily.
+Therefore $\tilde x^+ = A\tilde x + B\tilde u + v$ accounts for all nonlinearities within $\mathcal X
+\times\mathcal U$ if $v\in\mathcal V(\tilde x,\tilde u)$. For general nonlinear systems
+finding the extremal values of $(H^x,H^u)$ is non-trivial.
 To obtain values for $(H^x_k,H^u_k)$ we sample $\mathcal X\times\mathcal U$ and evaluate the integral 
@@
 For this we use the numerical values for the example of the 
-levitating ball: $T_s=30ms, C=1, m=100g, \hat x_1 = 50mm$ and $\mathcal X=\{x:
-\abs{x_1- \hat x_1}\leq 1mm\wedge \abs{x_2}\leq 105\frac{mm}{s}\}$, $\mathcal U=\{u:\abs{ u-\hat u}\leq10mA\}$.
+levitating ball: $T_s=30\,\text{ms}$, $C=1$, $m=100\,\text{g}$, $\hat x_1 = 50\,\text{mm}$ and $\mathcal X=\{x:
+\abs{x_1- \hat x_1}\leq 1\,\text{mm}\wedge \abs{x_2}\leq 105\,\text{mm}/\text{s}\}$, $\mathcal U=\{u:\abs{ u-\hat u}\leq10\,\text{mA}\}$.
 Using a total of 25 samples for the computation of $(H^x,H^u)$ we obtain the invariant set shown in figure~\ref{fig:MRPI:set:levitating:ball},
 which is less conservative than using fixed bounds on the
-nonlinearities as we will see in Section~\ref{sec:second:example}.
+nonlinearities (this will be shown in Section~\ref{sec:second:example}).
 The algorithm for computing the MRPI set terminates after 3 iterations.
@@
 \end{lpic}
-\caption{The maximal robust positively invariant set for the levitating ball system.}
+\caption{The maximal robust positively invariant set for the levitating ball.}
 \label{fig:MRPI:set:levitating:ball}
-\end{figure}
+\vspace{-2mm}\end{figure}
 %
@@
 %
+% \[
+% \begin{array}[t]{@{}rl@{}}
+% \max_v&\mathcal F_i \Psi^l v \\
+% \text{s.t.}&v\in\bar{\mathcal{V}}
+% \end{array}
+% =
+% \begin{array}[t]{@{}rl@{}}
+% \max_{\tilde v}&\mathcal F_i \tilde  v \\
+% \text{s.t.}&\Psi^{-l} \tilde v\in\bar{\mathcal{V}}
+% \end{array}
+% =
+% \begin{array}[t]{@{}rl@{}}
+% \max_{\tilde v}&\mathcal F_i \tilde v \\ 
+% \text{s.t.}& \tilde v\in\Psi^l\bar{\mathcal{V}}
+% \end{array}
+% \]
 \[
-\small
-\begin{array}{rlcrlcrl}
+\begin{array}{@{}rl@{\hspace{0.7em}}c@{\hspace{0.7em}}rl@{\hspace{0.7em}}c@{\hspace{0.7em}}rl@{}}
 \max_v&\mathcal F_i \Psi^l v &=& \max_{\tilde v}&\mathcal F_i \tilde  v &=& \max_{\tilde v}&\mathcal F_i \tilde v \\ 
@@
 observability argument as in Lemma~\ref{thm:finite:MRPI:set:state:dependable}.
-We then use the representation~\eqref{eq:closed:form:parametrised:iterates} to argue that $D_k$ as
-in~\eqref{eq:parametrised:Dk} grows exponentially and therefore contains any compact set after a finite number
+We then use the representation~\eqref{eq:closed:form:parametrised:iterates} to argue that $D_k$ 
+in~\eqref{eq:parametrised:Dk} grows exponentially and hence contains any compact set after a finite number
 of iterations. Fixing $\theta=\hat\theta$ does not affect the result since
 our argument is constructed for a fixed matrix $\Gamma$ with rows scaled by 
-$\frac{1}{1-\mathcal G_i\hat\theta}$; clearly we can re-scale the rows to accommodate any other choice of $\hat\theta>-1$.
+$(1-\mathcal G_i\hat\theta)^{-1}$; clearly we can re-scale the rows to accommodate any other choice of $\hat\theta>-1$.
 \end{proof}
@@
 set for the levitating ball. To obtain results comparable to those in Section~\ref{sec:first:example} we derive fixed bounds
-on the effect of nonlinearities on each state by finding a fixed set containing the set $\mathcal V(x,u)$ 
+on the effect of nonlinearities on each state by finding a set $\mathcal V$ that contains $\mathcal V(x,u)$ 
 in~\eqref{eq:definition:element:wise:constraints:on:nonlinearities} for all $(x,u)\in\mathcal X\times\mathcal U$. 
-This yields a constant set $\mathcal V$ which is non-symmetric around the origin due to nonlinearity. We also introduce
-a scaling parameter $\alpha$ such that $\mathcal U(0)=\mathcal U$ for $\alpha=0$. For this setup we obtain the MRPI
-set $\mathcal Z^\infty=\{(x,\theta,\alpha): \Lambda_i^x x + \Lambda_i^\theta \theta + \Lambda_i^\alpha \alpha\leq
-\lambda_i\,\forall i\leq m_\infty\}$. Notice that since $\alpha$ was introduced as a scaling parameter
-for $\mathcal U(\alpha)=\{u: Fu\leq (1+\alpha){\bf{1}}\}$ all entries in $\mathcal H$ are non positive and
-remain unchanged throughout the computation of $\mathcal Z^\infty$ so that $\Lambda^\alpha$ has only non
-positive entries, i.e. increasing $\alpha$ will enlarge the parametrised MRPI set $\mathcal Z^\infty\vert_{\alpha_1}
+%This yields a fixed set $\mathcal V$ which is non-symmetric around the origin due to nonlinearity.
+We also introduce
+a scaling parameter $\alpha$ such that $\mathcal U(0)=\mathcal U$ for $\alpha=0$.
+The MRPI set then has the form $\mathcal Z^\infty=\{(x,\theta,\alpha): \Lambda_i^x x + \Lambda_i^\theta \theta + \Lambda_i^\alpha \alpha\leq
+\lambda_i\,\forall i\leq m_\infty\}$. Since $\alpha$ was introduced as a scaling parameter
+for $\mathcal U(\alpha)=\{u: Fu\leq (1+\alpha){\bf{1}}\}$, all entries in $\mathcal H$ are non positive and
+remain unchanged throughout the computation of $\mathcal Z^\infty$; hence $\Lambda^\alpha$ has only non
+positive entries, and increasing $\alpha$ enlarges the parametrised MRPI set $\mathcal Z^\infty\vert_{\alpha_1}
 \subseteq\mathcal Z^\infty\vert_{\alpha_2}$ for $\alpha_1\leq\alpha_2$.
 
-First we compare the MRPI set $\mathcal X^\infty$ obtained with state dependent disturbance 
-constraints with the parametrised set $\mathcal Z^\infty$. To do this we compute the scaling parameter 
+To compare the MRPI set $\mathcal X^\infty$ for state dependent disturbance 
+constraints with the parametrised set $\mathcal Z^\infty$, we determine
 $\alpha_{\min}$ such that $\mathcal X^\infty\subseteq\mathcal Z^\infty\vert_{(\theta=0,\alpha=\alpha_{\min})}$
-by solving $m_\infty$ linear programs
+by solving $m_\infty$ linear programs:
 %
@@
 \[
+	% \gamma_i^\ast = 
+	% \max_x \ \Lambda_i^x x \ \ 
+	% \text{s.t.} \ x\in\mathcal X^\infty
 	\gamma_i^\ast = \begin{aligned}[t]
@@
 The minimal value for $\alpha_{\min}$ is then given by the maximal $\alpha$ satisfying $\gamma_i^\ast + 
-\Lambda_i^\theta\cdot 0 + \Lambda_i^\alpha \alpha \leq \lambda_i$. Solving this we obtain the 
-minimal value $\alpha_{\min} = 1.7555$ and the MRPI sets shown in Figure~\ref{fig:minimal:scaling:comparison:MRPIs}.
+\Lambda_i^\theta\cdot 0 + \Lambda_i^\alpha \alpha \leq \lambda_i$. This gives the 
+minimal value of $\alpha_{\min} = 1.7555$ and the MRPI sets shown in Figure~\ref{fig:minimal:scaling:comparison:MRPIs}.
 The computation terminates after seven iterations and produces a polyhedron $\mathcal Z^\infty$ supported by $m_\infty=10$
 planes.
-Caution is advised when interpreting $\alpha>0$, since the system is nonlinear.
-extrapolations reveal little insight, however $\alpha_{\min} > 0$ indicates that the current set of inputs $\mathcal U(0)=\mathcal U$ 
-is not large enough to cope with the perturbation set given by upper bounds of the nonlinear effects.
+Caution is advised when interpreting $\alpha>0$, since the system is nonlinear,
+%extrapolations reveal little insight, however 
+however $\alpha_{\min} > 0$ indicates that the input constraint set $\mathcal U(0)=\mathcal U$ 
+is too small to cope with a fixed disturbance set bounding the linearisation errors.
 %
@@
 \end{lpic}
-\caption{The minimal scaling of the constant disturbance set such that the associated MRPI set contains
-the MRPI set for piecewise affine disturbances is $\alpha_{\min}=1.7555$. Note that since the nonlinearities of the system
- dynamics are not symmetrical around the equilibrium the MRPI set with fixed constraints on the disturbance
- is non-symmetric.}
+\caption{MRPI sets for the minimally scaled fixed disturbance set and for the piecewise affine disturbance set.
+The MRPI set for fixed disturbance bounds is non-symmetric because the nonlinearities of the system dynamics are not symmetrical about the equilibrium.}
+%The minimal scaling of the constant disturbance set such that the associated MRPI set contains %the MRPI set for piecewise affine disturbances is $\alpha_{\min}=1.7555$. 
+%Note that since the nonlinearities of the system dynamics are not symmetrical around the equilibrium the MRPI set with fixed constraints on the disturbance
+% is non-symmetric.}
 \label{fig:minimal:scaling:comparison:MRPIs}
-\end{figure}
+\vspace{-2mm}\end{figure}
 
@@
 (\theta)\wedge \alpha,\theta>-{\bf{1}}\right\}$, for $K$ and $K_w$ satisfying the robust Lyapunov condition
-$x^TPx - ((A+BK)x+Dw)^TP((A+BK)x+Dw)\geq x^T(Q+K^TRK)x -\gamma^2 w^Tw$, i.e. $K_w = (\gamma^2-D^TPD)D^TP(A+BK)$.
-We use $Q = \text{diag}(2,1)$ and $R = I$. Using these numerical values we determine the MRPI set 
+$x^TPx - ((A+BK)x+Dw)^TP((A+BK)x+Dw)\geq x^T(Q+K^TRK)x -\gamma^2 w^Tw$, i.e. $K_w = (\gamma^2-D^TPD)D^TP(A+BK)$
+for $Q = \text{diag}(2,1)$ and $R = I$. Using these numerical values we determine the MRPI set 
 $\mathcal Z^\infty$. After 22 iterations the algorithm terminates producing a total of 61 facets. 
@@
 For this example the greatest sensitivity corresponds to $\alpha_3$, 
-i.e. the third input constraint.
-Similarly to the first example we might also want to know how much disturbance the closed loop system can tolerate 
+i.e.~the third input constraint.
+As for the first example we might also want to know how much disturbance the closed loop system can tolerate 
 such that a given set is contained in the MRPI set $\mathcal C\subseteq\mathcal Z^\infty\vert_{(\theta,0)}$.
@@
 \label{fig:two:dim:example}
-\end{figure}
+\vspace{-2mm}\end{figure}
 \begin{figure}
@@
 \label{fig:three:dim:example}
-\end{figure}
+\vspace{-4mm}\end{figure}
 %
@@
 %
-In this paper we discussed extensions to existing computational methods to determine MRPI sets for linear systems subject 
+This paper discusses extensions to existing computational methods for determining MRPI sets for linear systems subject 
 to additive disturbance for two descriptions of the sets bounding unknown additive disturbances. The case of state dependent 

### 2015-09-23 correction.tex
irredundancy correction

\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
\usepackage{amsmath}
%\define\vv{\vskip\baselineskip}

\begin{document}

The error in the paper comes from a mistake in Lemma 2.4. (There is a typo in Lemma~2.3: $Z$ should be $S$ in the second-last line, but otherwise Lemma 2.3 is OK.)

\vskip\baselineskip
The mistake in the proof of Lemma 2.4 is in the line
\[%\begin{align*}
\{v : G v \leq \lambda H(x_1) + (1-\lambda)H(x_2)\} 
= \{v : Gv \leq \lambda H(x_1)\} \oplus \{v : Gv <= (1-\lambda)H(x_2)\}.
\]%\end{align*}
I think equality only holds here if $\{v : Gv \leq H(x_i)\}$ is irredundant for $i = 1$ and $i = 2$; in the general case the LHS will contain (but not be equal to) the RHS. To correct this we need to assume that $\{v : Gv \leq H(x)\}$ is an irredundant representation (i.e.\ one that contains no redundant constraints) for all $x$ in $\mathcal{X}$. Although this sounds not too bad, it's actually quite a restrictive assumption because it rules out the possibility (as we discussed this morning) of the number of vertices of $V(x)$ changing.

\vskip\baselineskip
To see why we need $V(x)$ to be irredundant in order that Lemma~2.4 can hold consider the following 1-dimensional example. For scalar $v$ and $x$, let $\mathcal{X} = [0,2]$ and
\begin{gather*}
V(x) =  \{v : Gv \leq H(x)\}, \\
G = \begin{bmatrix} 1 \\ 1 \\ -1\end{bmatrix}, \ \ H(x) = \begin{bmatrix} 1\\  (x+1)/2 \\ 1 \end{bmatrix}.
\end{gather*}
Then 
\[
V(x) = \begin{cases}
\{ v : -1 \leq v \leq (x+1)/2\} & x \in [0,1] \\
\{ v : -1 \leq v \leq 1\} & x \in [1,2] 
\end{cases}
\]
so the upper limit of $V(x)$ is clearly a concave (rather than convex) function of $x$ even though $H(x)$ is linear and hence is necessarily elementwise convex.

\vskip\baselineskip
In particular, taking $x_1 = 2$ and $x_2 = 0$ we get
\begin{align*}
V\bigl( \lambda x_1 + (1-\lambda) x_2 \bigr) 
&= \left\{ v: \begin{bmatrix} 1 \\ 1 \\ -1 \end{bmatrix} v \leq \lambda \begin{bmatrix} 1 \\ 1.5 \\ 1 \end{bmatrix} + (1-\lambda)  \begin{bmatrix} 1 \\ 0.5 \\ 1 \end{bmatrix} \right\}  
\\
& \supseteq 
\left\{ v_1 + v_2 : \begin{bmatrix} 1 \\ 1 \\ -1 \end{bmatrix} v_1 \leq \lambda \begin{bmatrix} 1 \\ 1.5 \\ 1 \end{bmatrix} , \ 
\begin{bmatrix} 1 \\ 1 \\ -1 \end{bmatrix} v_2 \leq  (1-\lambda)\begin{bmatrix} 1 \\ 0.5 \\ 1 \end{bmatrix} \right\} \\
&= \lambda V(x_1) \oplus (1-\lambda) V(x_2),
\end{align*}
where $\supseteq$ appears in the 2nd line because the RHS is equal to 
\[
\left\{v_1 + v_2 :  \begin{bmatrix} 1 \\ -1 \end{bmatrix} v_1 \leq \lambda \begin{bmatrix} 1 \\ 1 \end{bmatrix} , \ 
\begin{bmatrix} 1 \\ -1 \end{bmatrix} v_2 \leq (1-\lambda) \begin{bmatrix} 0.5 \\ 1 \end{bmatrix}\right\}
= 
\{ v :  -1 \leq v \leq 0.5 + 0.5\lambda\} .
\]
In general equality will only hold in this step if and only if the same linear inequalities are active in the conditions on $v_1$ and $v_2$, and this will be the case if and only $Gv \leq H(x_i)$ is irredundant for  $i=1$ and $i=2$.

\end{document}

\begin{align*}
\left\{ v: \begin{bmatrix} 1 \\ -1 \end{bmatrix} v \leq \begin{bmatrix} 0.5 \\ 1 \end{bmatrix}\right\} \oplus \{0 \} \\ 
%\begin{bmatrix} 1 \\ -1 \end{bmatrix} \leq  \begin{bmatrix} 0 \\ 0 \end{bmatrix} \right\} \\
& = \{v : -1 \leq v \leq 0.5 \} \neq V(\lambda x_1) \oplus V\bigl( (1-\lambda) x_2 \bigr)
\end{align*}
However if we use an irredundant representation (piecewise in $x$ or $\lambda$) we get an 
\[
V(2\lambda) = 
\begin{cases} 
\left\{v : \begin{bmatrix} 1 \\ -1 \end{bmatrix} v \leq \begin{bmatrix} 0.5+\lambda \\ 1 \end{bmatrix}\right\} 
& \text{for } 0 \leq \lambda \leq 0.5 \\
\left\{v : \begin{bmatrix} 1 \\ -1 \end{bmatrix} v \leq \begin{bmatrix} 1 \\ 1 \end{bmatrix}\right\} 
& \text{for } 0.5 \leq \lambda \leq 1
\end{cases} 
\]

### 2015-11-23 postreview.tex
corrected K_1 and K_2

@@
 This paper considers sets of disturbances that depend on
-parameters. First we consider state-dependent sets,
+parameters. First we consider state-dependent sets with the irredundant representation
 \begin{equation}\label{eq:PWA:disturbance:set}
@@
   (1-\lambda)\underbrace{(\{z_2\}\oplus T(z_2))}_{\subseteq S}
-  \subseteq Z
+  \subseteq S
 \end{aligned}\]
@@
   The point-to-set map $\mathcal V (x)$ defined by~\eqref{eq:PWA:disturbance:set} is parametrically 
-  convex for all $x\in \mathcal X$ if $H(x)$ is elementwise convex in $x\in \mathcal X\subset 
-  \mathbb R^n$ (i.e.~if each element $H_i(x)$ of $H(x)$ satisfies $H_i(\lambda x_1+(1-\lambda)x_2)\leq 
-  \lambda H_i(x_1)+(1-\lambda)H_i(x_2)$ for all    $\lambda\in[0,1]$ and $x_1, x_2\in\mathcal X$).
+  convex for all $x\in \mathcal X$ if $H(x)$ is elementwise convex (i.e.~if each element $H_i(x)$ of $H(x)$ satisfies $H_i(\lambda x_1+(1-\lambda)x_2)\leq 
+  \lambda H_i(x_1)+(1-\lambda)H_i(x_2)$ for all    $\lambda\in[0,1]$ and $x_1, x_2\in\mathcal X$) and
+  irredundant for all $x\in \mathcal X$.
 \end{thm}
@@
 %
-Since $\Psi$ is asymptotically stable we have $\rho<1$ and therefore $\rho^{-l}K_1\subseteq\Psi^{-l} K_1 
-\subseteq \Psi^{-l}\mathcal X_0 = \mathcal S_1$, implying exponential growth of $D_k$ provided $\mathcal S_2$ 
+Since $\Psi$ is asymptotically stable we have $\rho<1$ and therefore $\rho^{-k}K_2\subseteq\Psi^{-k} K_2 
+\subseteq \Psi^{-k}\mathcal X_0 = \mathcal S_1$, implying exponential growth of $D_k$ provided $\mathcal S_2$ 
 is bounded. To bound $\mathcal S_2$ we note that for $k\geq n$ we have $\mathcal S_2\subseteq 
-\bigoplus_{1\leq i\leq k-1} \rho^i K_2 \subseteq \frac{1}{1-\rho} K_2$. Thus $D_k$ grows exponentially, whereas 
+\bigoplus_{1\leq i\leq k-1} \rho^i K_1 \subseteq \frac{1}{1-\rho} K_1$. Thus $D_k$ grows exponentially, whereas 
 $\mathcal X_k$ is contained in a ball of finite radius, and we conclude from~\eqref{eq:set:iteration:state:dependent:constraints} that 
